\section{GMS - General Massive Systems}

 GMS - GENERAL MASSIVE SYSTEMS  

    “From Cradle to the Stars, General Massive Systems did it first and did it best. GMS:  
                         reliable quality, universal licensing, total coverage.”   

General Massive Systems, GMS for short, is the galactic standard for non-civilian mechs.  
Reliable, sturdy, and solidly built, with universal components, full radiation and environmental  
shielding, and tens of thousands of pre-loaded languages, a pilot in their GMS mech will have all  
they need to get the job done in a hostile galaxy.
 

GMS is one of the oldest galactic entities, getting their start as an early player in the colonization  
rush of the 2400’s after constructing the first Blink Gates. GMS hails from Cradle, the home  
systems of Union and all humanity, and their designs reflect the aesthetics and intentions of  
those first pioneers to seek the stars. They developed the first mech cores in 4500, followed  
shortly by the pre-contemporary Harrison Armory. 
 

All GMS FRAMEs, gear, core bonuses, and licenses are available to all pilots from license  
level 0. The GMS core is the all-rounder standardized EVEREST core. Variants of this core exist,  
such as the ANNAPURNA, the LHOTSE, the DENALI, and the MASSIF mechs.

\subsection{BASIC PILOT GEAR}
                                         BASIC PILOT GEAR  
This is a list of basic pilot gear available at level 0. All gear listed here is rarity 0. More  
advanced pilot gear can be found in each of the manufacturer’s sections of the compendium.  
Pilots can take armor, one or two weapons, and any reasonable amount of gear with them on a  
mission as long as the gear’s total rarity is less than their pilot level. All pilot weapons are ‘pilot’  
sized.
 

                                        Basic Pilot Melee Weapons  

 Name                      Tags                                       Range             Damage 

 Primitive Melee           Primitive                                  Threat            1 kinetic 

 Alloy/Composite           -                                          -                 - 
 Weapon 

                    Light  Sidearm                                    Threat            1 kinetic 

                 Combat    -                                          Threat            2 kinetic 

                  Heavy    Inaccurate                                 Threat            3 kinetic 

*See Entry
 

                                                                                                             


If you want to generate an appearance or history for any of the melee weapons above, you can roll on the  
table
 

                                                      Notable Feature
 

 D6      Result 

  1      This weapon is ancient in design - it may have been dug up or excavated from pre-collapse ruins 

 2       This weapon is ornate or ceremonial, perhaps a badge of office 

 3       This weapon is well known or was wielded by a famous warrior 

 4       This weapon is plain in design or mass produced, but has a recognizable reputation and history -- positive  
         OR negative 

 5       This weapon was passed down to you and is a family heirloom 

 6       This weapon was custom-forged for you and bears your mark (or you made it yourself) 

Primitive melee weapon  

This category of weapons describes weaponry made by methods pre-dating modern alloy technology, and  
can describe anything from an industrial era steel sword to a stone axe. Though they are widely used in  
some worlds, most of these weapons used by pilots are relics, heirlooms, or serve ceremonial purposes.  

Primitive weapons are too simple to harm mechs.
 

Alloy/Composite weapon  

This catch-all category describes melee weapons forged with advanced and non-reactive alloys and or  
composite materials, allowing for durable and reliable weaponry in survival or close combat situations  
where kinetic shielding reduces the effectiveness of ballistics. 
 

Light: Knives, bayonets, arm blades, punching daggers, short swords.
 
Combat: Straight swords, war hammers, officer’s sabres, trench axes
 

Heavy: Mallets, rams, pikes, assault swords
 

                                             Basic Pilot Ranged Weapons  

  Name                        Tags                                             Range               Damage 

 Primitive Ranged              Primitive                                       5                   1 kinetic 

 Signature Weapon             -                                                -                   - 

                  Sidearm     Sidearm                                          3                   1* 

                   Combat     -                                                5                   2* 

                     Heavy    Ordnance, Limited (3)                            10                  4* 

If you like, you can roll on the tables below for a feature.
 

                                                      Notable Feature
 

                                                                                                                          


 D6      Result 

 1       This weapon is archaic or outdated by modern standards, but still reliable. 

 2       This weapon is prone to jamming and very finicky. You’re the only one that can use it effectively. 

 3       This weapon is sleek, foldable, and easily concealable 

 4       This weapon makes an amazing show, giving off an enormous amount of noise, smoke, light, etc when it  
         fires. 

 5       This weapon has been custom tooled for you by an omninet miltec enthusiast and has a couple extra  
         features such as foldable stands, grips, range-finders, motion detectors, omni-net hookups, chat programs,  
         and text games built in. 

 6       This weapon was given by or taken from someone else, willingly or otherwise. 

Primitive Ranged  

This weapon category describes primitive, pre-modern tech weapons such as black powder weapons,  
muskets, or bows, all commonly used in some societies. Primitive weapons are too simple to harm mechs.
 

Signature weapon  
Pilots carry a diverse array of weaponry with them into the battlefield, everything from heirloom weapons,  

to custom-tooled sidearms, or anonymous military-issued assault rifles. 
 

Choose the damage type when you acquire it (from explosive, energy, or kinetic). You can use this entry to  

represent the weapon that your pilot typically carries or uses. 
 

Sidearm: An oversized revolver, a brace of pistols, a sub-machine gun.
 

Combat: An assault rifle, a shotgun, a pack-fed laser, a disruption gun
 
Heavy: A missile tube, a heavy laser, a light machine gun, an exotic-caliber rifle
 

                                             Basic Clothing and Armor
 

    Name                Tags                Bonuses                              Armor        Evasion/         Speed 
                                                                                              E-defense 

    Plain clothes       Clothing            -                                    0            10/10            4 

    Light Hardsuit      Armor               +3 HP                                0            10/10            4 

    Assault             Armor               +3 HP                                1            8/8              4 
    Hardsuit 

                                                     Plain Clothes
 
This catch-all entry describes pilots when they’re not wearing armor specifically designed for  
combat. Pilots can be found sporting all kinds of fashion depending on their employment, rank,  
and role - from civilian street clothing, to smart-jackets, to oil-stained overalls, to military  
fatigues.
 

                                                                                                                        


                                                         Hardsuit  

There are tens of thousands of licensed hard suit makers — the Big Five notwithstanding — that an attempt  
to attribute a galactic standard make and model to any one manufacturer is impossible. That said, the GMS  
Model One would be the closest to a galactic standard, if one must choose.   

Hardsuits are, generally speaking, any suit that provides the following protections and features: protection  
from hard vacuum, protection from radiation, neural and data interface ports that interact with galactic- 

standard connections, full omninet communication compatibility, some measure of kinetic and energy  
protection in the form of plate armor over vital areas, some measure of environmental sealing, and some  
measure of rescue capability should a pilot be forced to eject.   

A pilot’s hard suit often provides an advanced interface and neurological shielding between themselves and  
the mech chassis they pilot. Piloting a mech without some kind of shielding (from a suit or otherwise,  

colloquially referred to as ‘riding naked’) is fully possible but typically only employed by old fashioned or  

daredevil pilots.   

If you like, you can roll on the tables below for a feature.
 

                                                       Notable Feature
 

  D6     Result 

  1      This hard suit was custom-tooled by an artisan manufacturer - it’s nearly one-of-a-kind, and its quality shows 

  2      This hard suit is an outdated or old model but remains incredible sturdy. You might be the only one who can  
         fit in it. People might have great affection for it’s model and its reputation is well deserved - though it lacks  
         many features of modern suits. 

  3      This hard suit is partially retractable - components of it can slide in or out of place without requiring it to be  
         taken off and it can be activated by detecting pre-set micro-muscular twitches, ready to activate at a  
         moment’s notice 

  4      This hard suit has self-healing or sealing components, possibly biocomponents, and feeds and charges  
         partly off the body’s own electromagnetism 

  5      This hard suit has been heavily customized by either you or someone else, with features and notable  
         cosmetic changes, such as etchings, trophies, badges or emblems 

  6      This hard suit has strong cultural or background ties to your pilot, and has a signature or recognizable look -  
         perhaps it is worn as part of a particular mercenary company, perhaps it is custom armor of the imperial  
         guard, or perhaps it’s manufactured only on your home world 

Light Hardsuit: Light hard suits are usually made of reactive, cloth like weaves, with plating and  
powered components kept to a minimum to maximize mobility. Often, they resemble light body  
armor or military fatigues and they may or may not have a closed helm by default, depending on  
environmental expectations. 
 

                                                                                                                           


Assault Hardsuit: Standard hardsuits have heavier plating than light hardsuits, restricting  
movement but providing greater protection from damage -- the heaviest versions will have vital  
plating comparable to mech armor. They are often environmentally sealed and powered, and  
typically have a faceplate, visor, or closed helm.
 

                                              Deployables and medical  

    Name                   Tags        Description                                                            Uses 

    Concussion             Gear        Grenades that detonate for a burst of concussive energy               2 
    Grenades                           and a bright flash on impact. A pilot can throw a  
                                       concussion grenade at any point in range 5 as an action.  
                                       It detonates on impact in a blast 1 area. Make an attack  
                                       roll against each target caught in the area, on hit, the  
                                       target is stunned until the start of your next turn. Does not  
                                       affect mechs or targets larger than human-sized. 

    Corrective             Gear       This clear, plastic-sheet like medical deployable can be                1 
                                       attached to severely wounded pilot, where it instantly  
                                       begins stabilizing them, injecting medicine, and deploying  
                                       nanites to stitch shut wounds. A corrective can be applied  
                                       to any pilot that’s Down and Out to instantly bring them  
                                       back to consciousness at 1/2 HP as if they had taken a  
                                       rest. 

   Fragmentation           Gear       A pilot can throw a frag grenade at any point in range 5 as            2 
    Grenade                            an action. It detonates on impact in a blast 1 area. Make  
                                       an attack roll against each target caught in the area, on  
                                       hit, it deals 2 explosive damage. 

   Nanite Spray            Gear       This spray paint can be sprayed on any surface. It is                   Unlimited 
                                       invisible to the naked eye but can be used to transmit a  
                                       simple message or limited data packets when scanned 

   Patch                   Gear        ‘Patch’ is a catch all term for sprayable medi-gel, instant-           1 
                                       acting medical patches, or other first aid gear. Using a  
                                       patch takes a full action and restores 1/2 your pilot’s HP  
                                       (round up). It can be used on another adjacent pilot for the  
                                       same effects, and although it can heal a down and out  
                                       pilot, it won’t bring them back to consciousness. Has no  
                                       effect on mechs. 

                                                                                                                          


  Stims                   Gear       These chemical stimulants are sometimes administered                   3 
                                     automatically by built-in injectors in a pilot’s suit, or even  
                                     their body. 
 
                                     Choose one when you take a stim:
 
                                     Kick: Keeps a pilot awake and alert for up to 30 hours. 
 
                                     Freeze: Keeps a pilot calm and emotionally stable,  
                                     deadens fear or other strong reactions.
 
                                     Juice: Heightens senses, alertness, dispels fatigue, and  
                                     shortens reaction times. Known to occasionally provoke  
                                     rage in some users.
 

                                     Uncontrolled use of any stims can be addictive and  
                                     dangerous to health in the long term and is a problem for  
                                     some pilots.  

  Thermal Charge          Gear       This charge can be planted on any free space for a full                1 
                                     action, and detonated remotely as an action. Once  
                                     detonated, it explodes in a blast 1 area. Attack all targets  
                                     in the area, aim vs evasion, for 3 AP energy damage. This  
                                     deals double damage to objects such as doors, walls, and  
                                     automatically hits them. 

                                                Miscellaneous Gear  

          Name                   Tags                                       Description 

Ambrosia Reservoir            Upgrade        Typically collar-mounted, an Ambrosia Reservoir carries a two- 
                                             week complement of flavored or unflavored Ambrosia, a fuel- 
                                             paste that can keep pilots fed and hydrated in emergency  
                                             situation.  

Antiphoton Visor              Upgrade        Flash/light protection, commonly found among breach teams,  
                                             solar-forward operators. Effective against flash weapons, intense  
                                             UV light, and incidental charge from energy weapons.  

Camo Cloth                    Gear           A 5x5 square of reactive material that slowly shifts to reflect the  
                                             environment around it. The effect takes about 10 seconds to  
                                             complete, and makes anything hidden underneath very hard to  
                                             spot. 

Extra Rations                 Upgrade        Pilot rations are typically no better than their nautical antecedents  
                                             - hard tack and nutritious paste. It’s not uncommon for pilots to  
                                             store extra food or luxuries such as chocolate, coffee, alcohol, or  
                                             canned or dried goods from their home world 

Handheld Printer              Gear           A miniaturized version of the much larger Union printers, can  
                                             make simple objects out of a flexible and durable plastic as long  
                                             as you have the pattern chip for them. 

Mag-clamps                    Upgrade        These clamps attach easily onto any metal surface, giving good  
                                             maneuverability in zero-g or when repairing mechs. Can be fitted  
                                             to boots. 

                                                                                                                        


Omnihook                      Gear           A bulky, miniaturized, portable field omninet terminal that allows  
                                             for communication, data transfer, and limited hotspotting. Very  
                                             valuable. Most mech teams have at least one of these, mounted  
                                             or carried by a designated operator. Tuning an omnihook requires  
                                             a high degree of skill. 

Personal Drone                Gear           A small, non-combat drone. Fairly noisy, but can fly with good  
                                             maneuverability up to half a mile without losing signal and can  
                                             relay audio and visual information. 

Smart Scope                   Gear           A powerful electronic scope that can give good vision up to two  
                                             miles away, automatically adjusts its reticle for wind, gravity, and  
                                             pressure. Can be paired with other thermal, optical, or simulated- 
                                             vision devices to allow for more precise targeting. Can project its  
                                             FoV and all data to a user or networked user’s HUD.   

Sleeping Bag                  Upgrade        Folds out from a hardsuit, compact enough to fit in a mech  
                                             cockpit, highly resistant to changes in temperature. Some mech  
                                             pilots swear by them as emergency fire protection 

Sound System                  Upgrade        Though not strictly necessary, many mech pilots hook up internal  
                                             speakers to give them a clear line to their compatriots during  
                                             combat, or simply play music 

Tertiary Arm                  Upgrade        A powered third arm, mounted on a bracket on the hardsuit. Can  
                                             be equipped with a manipulator to allow for fine motor control,  
                                             fitted with a weapon to allow for greater combat efficacy, or a  
                                             specialty tool. It is powered, and controlled via the same  
                                             neurological bridge processes that lets hardsuits respond to user  
                                             input.  

Wilderness Survival           Gear           Contains many of the essentials for surviving in a hostile  
Kit                                          environment - rebreather, water filter, backup environmental suit,  
                                             bivouac kit, etc 

                                                                                                                         

\subsection{GMS Core Bonuses}
                                      GMS CORE BONUSES  

When you choose a core bonus every 3 license levels, you can always choose a bonus from this  
list. These bonuses apply to any mech you create each time you create it, and each can be  
chosen only once.
 

Auto-Stabilizing Hardpoints  
Choose 1 mount on your mech. Attacks from this mount can be made with +1 Accuracy.
 

BURNOUT Insulation  
Choose 1 weapon on your mech. It deals +1d6 bonus damage on hit.
 

Improved Armament
 
If your mech has less than 3 mounts, gain an additional Flex Mount
 

Integrated Weapon  
Choose 1 mount on your mech. It gains capacity for an additional auxiliary weapon.
 

Mount Retrofitting  
Replace one of your mech’s mounts with one of the following:
 
	       - Flex Mount
 
	       - Aux/Aux mount
 
	       - Main/Aux mount
 

Reserve Capacitors
 
When you spend core power to activate a CORE system, you can also repair your mech’s HP to  
full and cool all heat as a Free Action, then roll a 1d20. On a 20, regain 1 core power.
 

                                                                                                          
\subsection{GMS Standard Pattern I (“Everest”)}

                                GMS Standard Pattern I (“Everest”)  

Most humans don’t think to ask about the history of the water they drink, the earth they walk, or the air they  

breathe. And yet without water, earth, and air, there would be no place for Humanity to make their home.   

The Everest -- officially, the General Massive Systems Standard Pattern I -- is a plainly designed chassis.  

Simple lines. Functional grace. Sturdy bulk. Its use-name, “Everest”, comes from one of the names of the  
tallest mountain on Cradle. Of the surveyed, named mountains in known space, Mount Everest -- or  
Sagarmatha, or Chomolungma, as it has been called in Old Human tongues -- is neither the most  

prominent peak, nor the even the tallest in Cradle’s local star system; and yet, pilots the galaxy over learned  
to call their GMS-SPi’s by that ancient name. Why?    

The sentimental answer is that the Everest is called the Everest because it is a reminder of what was once  
the limit of human endurance, of what once was the peak of human achievement. To summit Everest was  
to stand atop the world, the culmination of months -- maybe years -- of training, investment, and effort,  

defying death and injury upon your quest to summit.   

The real answer is probably much less intentional. Somewhere along the line, GMS’s plain naming  

convention coupled with Union’s anthropocentric emphasis lead a cadet, having graduated to a full pilot, to  
paint EVEREST across their GMS-SPi’s flank. Maybe it was meant to be their callsign, or maybe it was  
meant to represent their success following grueling training, but either way the name stuck in the insular  

pilot culture. Other pilots adopted the name, and over five centuries it has grown to become the official- 
unofficial designation for all GMS-SPi chassis.   

Veteran pilots may never return to crew an Everest after they’ve moved on to other chassis, but they’ll  
always remember when they reached that first summit, when they proved they were worthy of planting their  
own flag on at the peak of the world.   

The Everest may not be the most specialized chassis in the galaxy, but it is the backbone of the galaxy, and  

humanity steps to the stars from its shoulders. 
 

                                                      EVEREST 

  HP: 10          Evasion: 8                                Speed: 4             Heat Cap: 6          Sensors: 10 

 Armor: 0         E-Defense: 8                              Size: 1              Repair Cap: 4        Tech Attack:  
                                                                                                      +0 

                                                        TRAITS: 

  Initiative: The very first turn the Everest takes in any combat, it can take an extra Quick Action as a free  
 action 

                                                 SYSTEM POINTS: 6 

                                                                                                                       


                                                 MOUNTS: 

Flex Mount                        Main Mount                            Heavy Mount 

                                              CORE system 

                                      GMS Hyperspec Fuel Injector  
Active (requires 1 core power): Power up
 
Protocol
 
This turn only, you can make an additional Full Action as a free action or 2 Quick actions as free  
actions. 
\subsection{GMS Mech Weapons List}
                                   GMS Mech Weapons List  

Name                 Designation        Size/Type        Tags                Range          Damage 

Anti-Material        MC-AMR             Heavy Rifle       Loading,            20            2d6 kinetic 
Rifle                                                     Ordnance,  
                                                        Accurate 

Assault Rifle         MC-AR              Main Rifle        Reliable 2          10             1d6 kinetic 

Charged Blade        MC-CB              Main Melee      AP                  Threat 1        1d3+3 energy 

Drone Nexus          MC-DLA             Auxiliary        Smart               10             1d3 kinetic 
(Light)                                 Nexus 

Drone Nexus          MC-DHK             Main Nexus       Smart               10             1d6 kinetic 
(Hunter-Killer) 

Heavy Machine        MC-MG              Heavy            Inaccurate          10            2d6+2 kinetic 
Gun                                     Cannon 

Heavy Melee          MC-HB              Heavy Melee      -                  Threat 1       2d6+1 kinetic 
Weapon 

Heavy Charged        MC-EB              Heavy Melee     AP                  Threat 1        1d6+3 energy 
Blade 

Howitzer             MC-HW              Heavy           Arcing,              20, Blast 2   2d6 explosive 
                                        Cannon           Inaccurate,  
                                                         Loading,  
                                                         Ordnance 

Missile Rack         MC-MR              Auxiliary        Loading             10, Blast 1    1d3+1 explosive 
                                        Launcher 

Mortar               MC-M               Main            Arcing,              10, Blast 1    1d6 explosive 
                                        Launcher         Inaccurate 

Pistol               MC-P               Auxiliary CQB    -                   5, Threat 3    1d3 kinetic 

                                                                                                           


 Cyclone Pulse        MC-Cyclone         Superheavy       Reliable 5,         15             3d6+3 kinetic 
 Rifle                                    Rifle             Accurate,  
                                                          Loading 

 RPG                  MC-RPG             Main             Loading,            10, Blast 2    1d6+1 explosive 
                                         Launcher         Ordnance 

 Shotgun              MC-SG              Main CQB         -                   5, Threat 3    1d6 kinetic 

 Tactical Melee       MC-TB              Main Melee       -                   Threat 1       1d6+2 kinetic 

 Tactical Knife       MC-TK              Auxiliary        Thrown 5            Threat 1       1d3+1 kinetic 
                                         Melee 

 Thermal Pistol       MC-TP              Auxiliary CQB    -                   Line 5         2 energy 

 Thermal Rifle         MC-TL              Main Rifle        AP                  5              1d3+2 energy 

 Thermal Lance        MC-EL              Heavy            2 heat (self)       Line 10        1d6+2 energy 
                                         Cannon 

GMS weapons, much like their premier mech line, are reliable, galactic standards, made from  
interchangeable parts and built to withstand almost any conditions imaginable.
 

The Type I line includes powerful and reliable weapons that rely on conventional ammunition  
methods, such as the MC-AR, P, BR or SG as well as powerful thermal weaponry.
 

The Type II line is GMS’ line of proprietary melee weapons, forged from powerful polymers and  
intended to take maximum advantage of a mech’s extreme strength. The Tactical and Heavy  
Blade line, although called as such, also contain a line of mauls, hammers, picks, and other blunt  
weaponry. The charged blades line, new in GMS weapons development, includes weapons with  
an attached generator that sheathes the blade or head of the weapon in superheated plasma for  
shearing through armor. 
 

The Type III line is intended for specialized or siege warfare. It includes weapons like the widely  
feared GMS Type III AMR, a mech-scale sniper weapon infamous for its extremely high kill  
efficiency, and the Type III “Cyclone” superheavy pulse rifle, a weapon known for its enormous  
rate of fire. The Cyclone is so large that its spare magazines have been reported in some  
incidents to have been used as effective anti-infantry blunt weapons in close combat.
 
\subsection{GMS GENERAL MARKET CHASSIS MODS}
                       GMS GENERAL MARKET CHASSIS MODS
 

Custom paint job
 
1 SP, Unique  
This paint job counts as a system that can be destroyed by structure damage
 

Manipulators  

                                                                                                             


Precise interaction with the built or natural environment, soft targets, and sensitive material below rated  
tonnage is part of the daily routine for support-class mechs. Manipulators, haptic-padded multi-digit  
“hands”, allow for such precise manipulation.   

1 SP, Unique  
Gain 2 extra sets of limbs. These limbs cannot be used to make attacks, but can otherwise hold  
and manipulate the environment and items as normal. In addition, these manipulators can  
interact with objects in the environment that a pilot would normally have to interact with (a pilot  
sized touch pad, etc) with no penalty.
 

Personalizations  

1 SP, Unique  
When you take this mod, your mech gains +2 HP and you may establish with your GM 1 minor  
effect or modification you have made to your mech. This mod cannot grant any statistical or  
combat benefit to your mech other than the hp benefit, but could provide other useful effects. If  
your GM agrees that this mod would help you with a particular skill check, they can give you +1  
Accuracy on the check.
 

Stable Structure  
1 SP, Unique  

You make rolls to resist getting knocked prone with +1 Accuracy.
 
\subsection{GMS General Market Deployables}
                               GMS General Market Deployables   

GMS Pattern-A “Apple” High Explosive Grenades  

The GMS Pattern-A HEX Grenade is a pilot’s best friend in a tight spot. Inert until activation by its neuro- 

coded welder, the “Apple” is guaranteed to neutralize any hard or soft target within its effective radius.  
 

1 SP, Limited (1)  

Grenade  
Range 5, Blast 1  
Attacks all targets caught in the blast radius for 1d6 explosive damage on hit.
 

GMS Pattern-A “Jericho”  Deployable Cover  

2 SP  
Deployable, Quick Action  
Using this system creates a Line 2 section of size 1 Heavy Cover adjacent to the user (in any  
orientation, as long as there is free space). Requires a full action to pick up. Reusable. The cover  
has 5 Evasion, 40 HP, and can be targeted and destroyed. A mech can spend 1 repair during a  
rest to repair it to full HP.
 

GMS “Pancake” Anti-Vehicular Mines  

                                                                                                                  


Used primarily for area denial, the GMS AV Mine system has begun to see more offensive employment by  
GMS pilots in combat theaters.   

1 SP, Limited (2)
 
Mine
 
This mine detonates when any target moves adjacent to it for a burst 1 attack, 1d6+3 explosive  
damage. A target can pass an agility check to halve this damage.
 

GMS Pattern-A “Filter” Smoke Grenade  

The Pattern-A/SL is a cheap, reliable, and low-system-cost method of deploying effective cover in a high- 
velocity kinetic scenario. Mixed with a proprietary blend of chaff, particulates, accelerants, and defilade- 

enhancers, Pattern-A/SL smoke is effective at obscuring most all sensor suites.   

1 SP, Limited (1)  
Grenade  
Range 5, Blast 3  
The blast area grants light cover to all within, friend or foe. Lasts until the end of the user’s next  
turn, then disperses.
 
\subsection{GMS General Market Systems List}
                                GMS General Market Systems List  

Companion/Concierge-Class Dummy Plug  

The Companion/Concierge Class Dummy Plug conforms to galaxy wide standards for comp/con units. A  
Com/Con DP will pass even the most rigid Turing-Null classifications and is cleared for operations even  

when the pilot is not present.   

2 SP, Unique  
AI  
Your mech has a basic companion/concierge unit installed in it, gaining the AI tag. It can speak  
to you and has a personality but is not truly capable of independent thought, as a true AI would  
be. It is obedient to you alone. When you hand over the controls, it can take actions and move  
on its own prerogative when not piloted, using its stats, but has no independent initiative (it must  
take and follow commands from you, or else takes no action other than to defend itself).
 

Dummy Plugs are not true AIs and thus cannot be unshackled.
 

GMS Shield Type-I  

The GMS Shield Type-I utilizes a projected, aggressive, anti-ballistic super-positional shield to trap and  

deny incoming solid and wave-based projectiles.   
   

2 SP, Unique
 
Shield, Protocol, 1 heat (self), Unique
 

                                                                                                                       


You can choose to activate this shield protocol at the start of your turn. Nominate an enemy you  
can see. All that enemy’s ranged or melee attacks against you are made at +2 difficulty until the  
start of your next turn, but your ranged or melee attacks against them also suffer the same  
penalty.
\subsection{Flight}

                                                   FLIGHT  

GMS EVA Module  
1 SP, Unique  

Your mech counts as having a propulsion system in low or zero gravity and submarine  
environments (its not Slowed while moving and can fly normally).
 

GMS ‘Burst’ Jump Jet System
 
2 SP, Unique  
When your mech boosts, your mech can fly. However, your mech must end its turn on the  
ground or another surface, or else fall.
 

GMS Type I Flight System  

3 SP, Unique
 
When your mech moves or boosts, it can fly. However, at the end of each turn that you activated  
this module, generate heat equal to the size of your mech +1, rounding up.
 

                                                                                                                
