\section{Harrison Armory}


                          HARRISON ARMORY  

                                     “SUPERIOR BY DESIGN”  

Harrison Armory is known galaxy-wide for the quality of their manufactured arms and  
ordnance. Formerly reliant on the GMS platform to mount their name-brand and licensed  
weapons, after a recent CEO change Harrison Armory has decided to go proprietary. Citing  
performance figures, tariffs, licensing costs, and shareholder-citizen demand, Harrison Armory  
has rolled out their new line of mech cores, available to all pilots who are cleared to license. 
 

Harrison Armory mechs are sturdy by necessity. Harrison Armory weapon platforms demand  
tremendous amounts of power, technical skill, and strength of material in order to operate  
successfully: their mech cores are built to ensure optimal weapon systems performance within  
established and theoretical parameters. 
 

Pilots looking to specialize into front line, first rank, durable mechs that can repair as much as  
they dish out should consider acquiring Harrison Armory mech core licenses.     

HARRISON ARMORY MECHS:  

TOKUGAWA (Energy Melee)  
BARBAROSSA (Siege)  
NAPOLEON (Stasis  
SHERMAN (Laser line mech)  
ISKANDER (Mine mech)  
SALADIN (Shield support mech)  
GENGHIS (Flame mech)  

                                                                                                    
\subsection{Harrison Armory Pilot Gear}

                                  HARRISON ARMORY Pilot Gear  

                                                    Pilot Weapons  

  Name                    Tags                                      Range            Damage                  Rarity 

 KOTTOS AA/               Ordnance                                  8                1d3 kinetic             1 
 Largearm Rifle 

 MicroCore Laser          Loading                                  5                 1 energy + Burn 1       2 
 Rifle 

 Atlatl                   Seeking                                  Threat 1
         1 explosive             3 
                                                                   Thrown 5 

 Hardlight Weapon         -                                        Threat 1          1 energy + Burn 1       4 

Atlatl  

Developed following the suppression of anti-Armory elements in the initial wave of recolonization in the  
Dawline Shore, the Atlatl is a neo-primitivist weapon indigenous to New Madrassa, a voluntary Arcadian  
world set in a blended Neo-Bronze/Information Age idyll.   

Though deceptively simple in appearance, this javelin-like weapon contains a hardened suite of intelligent  
hardware and a miniaturized pressure wave generator in the tip. It can be thrown very accurately up to  

range 5, recalled to hand as an action, and guides itself around cover and other obstacles.
 

Hardlight Weapon  

One of a limited supply scavenged from Boundary Garden, this hardlight blade has been patched by  
independent Ecumenical contractors to a serviceable, minimum-milspec functionality. These are exotic  

weapons, and their wielders must be coached in their use by trained handlers.    

These rare and powerful weapons project a sheathed energy field that ignites targets on impact.
 

KOTTOS AA/Largearm  
Harrison Armory’s KOTTOS distance-denial anti-armor system was ordered following repeated instances of  

HAAT legionnaires encountering hostile local chassis armed with sufficient anti-kinetic/ablative armor;  
KOTTOS, developed in conjunction with GMS’s Distant Venture campus, the KOTTOS represents the  
pinnacle of infantry-portable kinetic anti-armor kinetics.    

This heavy anti-armor rifle fired superheated bullets used to punch through infantry-scale hardsuits and  
light mechs. It requires mounting on a tripod before use, though some models come with a built-in stand.  

The enormous kick from this weapon is infamous for dislocating rookie pilots’ shoulders.
 

MicroCore Laser Rifle  

                                                                                                                     


A Think-Tank product, the MicroCore is a miniaturized, infantry-portable version of the popular SolidCore  
laser cannon mounted atop HA’s Sherman Chassis. The MicroCore has been tuned to not require windup  
on firing, but as a result must be “reloaded” after each shot with a new power core.   

An infantry-scale model of the larger, mech mounted lasers, this weapon requires heavy cooling after each  
use. Standard squad-support weapon for Armory legionnaires.
 

                                                 Clothing and Armor  

  Name                  Tags        Bonuses                                    Armor      Evasion/       Spd    Rarity 
                                                                                          E-defense 

 Buckler                Clothing    Provides protection in plain clothes       -          -              -      1 

 STAMBHA               Armor        Offers a short ranged protective            0          10/10          4      2 
  Overarmor                         shield. 

 DJED Overarmor    Armor            Provides stasis instead of Down            1          8/8            4      3 
                                    and Out 1/full repair 

 ASHOKA                Armor        +3 HP, Reduces heavy damage                1          8/8            3      4 
  Overarmor 

 ICEPACK                Upgrade     Gain the ability to overcharge             -          -              -      4 

Buckler  
This personal energy shield fits snugly under clothing and is standard issue to protect the Armory’s colonial  

bureaucrats and collaborators while venturing outside of green zones.   

While wearing plain clothes (not armor or a hardsuit), as a reaction to taking damage from a single source,  

you can activate this shield to reduce that damage to 0. This shield must recharge and can be used once  
every full repair.
 

ASHOKA Overarmor  
The Ashoka Overarmor Hardsuit is favored by frontline HAAT legionnaires in hostile colonies. Large and  
heavily armored, the ASHOKA is built to appear imposing: when it is needed, soft power has failed, and the  

Armory does not discount the memetic power of an intimidating appearance.   

This heavy armor disperses shock and heat from overwhelming damage, reducing it to manageable levels.  

While wearing this armor, if you would take more than 1/2 your maximum HP in damage, reduce the  
damage instead to 1/2 your maximum HP.
 

DJED Overarmor  
The DJED Overarmor is a medium weight, combat-posture hardsuit designed to preserve its user in case of  
sudden traumatic/catastrophic injury. Favored by legionnaires on patrol-and-liaise missions, the DJED is an  

Armory favorite and the most commonly requisitioned hardsuit among HAAT personnel.   

                                                                                                                      


When you go Down and Out, instead of rolling a check, you can activate this armor’s stasis system. Until  
the end of the current challenge, you are put into a stasis state where you cannot take damage, but also  
cannot move or take any actions (or be revived from this state). Once the challenge ends, roll for Down and  

Out as normal.
 

ICEPACK  

A stabilized sliver of coldcore, the ICEPACK is a near-perpetual power system that allows for momentary  
overclocking of powered hardsuit components.   

This miniaturized reactor is integrated into armor and cannot be used without it. While wearing armor with  
this enhancement, as a limited (3) system you can spend a charge as a pilot to take an extra quick action  
on your turn.
 

STAMBHA Overarmor  
Another combat-posture hardsuit, the STAMBHA employs a beefed-up buckler/flickershield system that  

protects its wearer from hostile fire. Resting somewhere between the Armory’s DJED and ASHOKA lines,  
the STAMBHA is a favorite of the officer class who are willing to trade mobility for protection.   

If you didn’t move on your turn, at the end of your turn, until the start of your next turn, gain a protective  
shield that grants all ranged weapon attacks against you +1 difficulty.
 

                                                   Miscellaneous  

  Name                Tags         Description                                                               Rarity 

 Dataplating          Upgrade      Linked jewelry/faceplates that allow sub-vocal communication               1 
                                   and augmented reality. Dataplates can quickly translate many  
                                   languages, and anyone with a dataplate can talk to any other  
                                   person with a dataplate without vocalizing, creating something  
                                   eerily similar to telepathy. 

 Flexsuit             Upgrade      A strong, under-clothing suit that recycles water, generates               1 
                                   nutrients, and adapts very rapidly to hostile environs, keeping its  
                                   wearer in a state of stability and extending their survivability. Very  
                                   good for colonists adapting to a new environs. 

 Sleep suit           Upgrade      Once activated, the suit can put an individual into a state of             1 
                                   human hibernation for as little as 3 hours and up to 6 months,  
                                   lowering their vital signs to almost nothing, relieving them of the  
                                   need for food, air, or sleep, and halting the process of any  
                                   diseases. During the first 10 minutes, the suit extrudes a  
                                   hardened polymer around the sleeper, protecting them from  
                                   impact and making them resistant to all damage. 

                                                                                                                   


 Hold/Lock          Gear        This mine can be planted in a free adjacent space as an action,      1 
 Nonlethal                      and detonated remotely as an action. It can also be set to  
                                detonate once any target moves adjacent to it. Once detonated,  
                                any target caught in a burst 1 zone around the mine is stunned  
                                and immune to all damage until the end of their next turn. Mechs  
                                cannot be affected. 

 Dispersal          Gear        This shield can be deployed as an action in a free adjacent          2 
 Dropshield                     space. Once deployed, it creates a burst 2 zone around it.  
                                Ranged attacks against all non-mech targets size 1/2 or smaller in  
                                the zone suffer from +1 difficulty. The shield deactivates after the  
                                current challenge and must recharge on a full repair. 

*See Entry  

                                                                                                          
\subsection{Harrison Armory Core Bonuses}

                           HARRISON ARMORY CORE BONUSES  

When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in H.A. licenses for each H.A. bonus you have. For example,  
if you have 6 points in H.A. licenses, you could take up to 2 bonuses. H.A. bonuses are focused  
on repair, heat capacity, and overcharge.
 

ARMORY SCULPTED  
Rather than simply queuing a stock chassis like any other pilot, you’ve used your reputation, contacts, or  

status in the Armory’s hierarchy to requisition a chassis that is designed, tested, and tuned by a master  
fabricator.    

Your mech takes +1 Accuracy to all engineering checks
 

HEATFALL Coolant System  

The HEATFALL system comes packaged with a stable COLDCORE power core of Armory make; when  

paired together, this suite makes for an incredibly low-tax powerplant.   

The heat cost for overcharging your mech never exceeds 1d6.
 

INTEGRATED AMMO FEEDS  

By streamlining and better integrating all automated ordinance loading modules, your chassis’ time-to- 
target minimums are greatly improved. As an added bonus, your overall carrying capacity has been  

increased, allowing you to field more ordinance than design specifications suggest.    

Your mech gains +1 use to all limited systems or deployables
 

REDUNDANT REPAIR SYSTEMS  

All Armory chassis are engineered to have multiple failsafe systems: yours has been over-engineered to  
make SURE you won’t go down fast. Your chassis comes with a ream of single-item print sheets to be  
applied to any scoring damage or hull breaches.    

You can now spend 3 repairs as part of a Stabilize action in combat to repair 1 reactor stress and  
cool your mech, or regain 1 structure and heal your mech to full.
 

STASIS SHIELDING  

A Think-Tank exercise in extending stasis beyond the capabilities of civilian utility, stasis shielding is a  
cutting edge Armory system that identifies critical systems and blankets them in HOLDFAST stasis lock,  
preventing further degradation for a limited period of time until repairs can be made.   

Your mech gains +1 repair capacity. Repairing a destroyed weapon or system during a rest now  
costs 0 repairs (only the time to rest).
 

                                                                                                                 


SUPERIOR BY DESIGN  

Even the entry-level Armory chassis are designed to be better than the competition. By flexing the sheer  
amount of resources they have at their disposal, the Armory can out design and out produce other smaller,  

boutique engineers and fabricators. Where there is resistance, the answer is simple: buy them out, or  
stamp them out. You, pilot, benefit from this -- so why worry?   

Your mech is immune to the impaired condition and gains +1 heat capacity
 

                                                                                                          
\subsection{Harrison Armory Barbarossa}

                           HARRISON ARMORY BARBAROSSA  

The BARBAROSSA chassis is a massive frame, built to carry the heaviest of weapons and equipment.  

Standing nearly forty feet tall at its highest point, the BARBAROSSA is a slow, unsubtle beast of a mech,  
inspiring terror in enemies and comfort in allies. The weapons it can mount are capable of going toe-to-toe  
with corvette and cutter class ships; indeed, due to its size and slow maneuverability, the BARBAROSSA is  

                                                                                                          


commonly employed in micro and zero gravity engagements where mass is less of a factor. The  
BARBAROSSA is rated for all theaters, and excels in ranged combat situations.   

                                                  License:
 
I. Siege Stabilizers, Roller Grenades
 
II. BARBAROSSA FRAME, Auto-Loader, Flak Cannon
 
III. External Ammo Feed, Siege Cannon
 

                                            BARBAROSSA 

 HP: 10         Evasion: 6                           Speed: 2           Heat Cap: 7       Sensors: 10 

 Armor:  2      E-Defense: 6                         Size: 3            Repair Cap: 4     Tech Attack:  
                                                                                          +0 

                                                  TRAITS: 

 Heavy FRAME: The Barbarossa cannot be knocked back or prone by actors smaller than itself
 
 Siege Shield: The Barbarossa has resistance to Explosive Damage
 
 Slow: The Barbarossa gets +1 Difficulty on Agility checks 

                                           SYSTEM POINTS: 5 

                                                 MOUNTS: 

 Main Mount                                          Apocalypse Rail 

                                              CORE system 

                                                                                                          


                                                Apocalypse Rail  

 The HA Apocalypse Rail is a spinal mount augmentation that adapts the weapon mounted upon it to  
 patch directly into its host mech’s coldcore. This allows for energy conservation/overcharge cycling:  
 most effective with energy weapons, this system allows a pilot to dump excess offensive energy from  
 sub-super weapons and systems into its central core, exciting the cold-burn system into an overcharge  
 state, which is then used to overpower and override inherent limiters built into the factory spec weapon  
 mounted in the Apocalypse Rail. This overcharge state allows for momentary overclocking of the AR- 
 mounted weapon, sacrificing mobility and auxiliary abilities in favor of stationary defense and attack.   

 Passive: Your mech has the apocalypse rail, a weapon mount that takes a superheavy or smaller sized  
 weapon. You can still mount smaller weapons on the apocalypse rail. You don’t need an additional  
 mount to add a superheavy weapon to this mount. This mount is not modifiable (such as from core  
 bonuses).
 

 Active (requires 1 core power): Convert to Battery  
 Quick Action
 
 Your mech converts to something more resembling a gun emplacement. While this mode is active, you  
 have the following drawbacks:
 
      -   Your mech is immobilized
 
      -   You cannot directly attack any target within range 5 of your mech
 
      -   You can only make attacks with the weapon mounted in your Apocalypse Rail
 
 However, you gain the following benefits:
 
      -   You cannot be moved (such as with a grapple) by any target smaller than you
 
      -   You have resistance to heat
 
      -   The weapon mounted in your Apocalypse Rail can be fired twice with the Barrage action  
          instead of just once. If it has the loading tag, it can still be fired twice (but must be reloaded  
          normally after) 

Siege Stabilizers  

Some weapons require further stabilization for optimal use: with Armory-sanctioned Siege Stabilizers  
installed, a chassis becomes a stable firing platform for any weapon.   

1 SP  
Quick Action
 
Extend or retract your stabilizers as a quick action. Your mech is immobilized while this system is  
active, but you can increase the base range of your ranged weapon attacks by +5. You cannot  
directly target any target within range 5 when this system is activated.
 

Roller Grenades  

2 SP, Limited (2)  
Quick Action, Grenade  
Instead of throwing these grenades normally, draw a line 15 spaces long from your mech. These  
grenades bounce over cover and objects up to size 1, and can pass through holes or areas as  
small as size 1/2. They detonate when they move through or adjacent to any actor’s space (even  
allied ones), dealing 2d6 explosive damage to that target only and knocking that actor back in  

                                                                                                                


the direction of the line 3 spaces. The target can pass an agility check to avoid the knock back  
and halve the damage.
 

Auto-Loader Drone  

Auto-Loader Drones are half-size, many-legged arthropod-analogous drone systems that assist  
sectionmate chassis in loading ordinance, maintaining powerline hookups, and cycling magazine-fed  

weapons.  

2 SP, Limited (1)  
Drone  
This drone can be deployed in an adjacent space. While deployed, once per round, any one  
adjacent mech can reload a weapon with the Loading tag as a quick action. It lasts until the end  
of the current scene, then deactivates.
 

Flak Cannon  
A quad-barreled autocannon, flak cannons are loaded with proximity-explosive shells perfect for  
blanketing fire. A perfect weapon for use against massed infantry or low-altitude flyers.   

Main Cannon
 
Reliable 1
 
Range 20
 
1d3 Kinetic Damage
 
Any flying target hit by this weapon must pass an agility check or immediately fall.  

External Ammo Feed 
 

An EAF is a general term for any manner of additional ammunition not carried in a chassis‘s integrated  
storage. Whether in magazines strapped to brachial, trunk, or ambulatory elements; battery packs attached  

to hip clasps; or massive, dorsal-mount ammunition/ charge packs, an EAF ensures that you‘ll have more  
than enough boom to get the job done.   

3 SP, Unique
 
Once on your turn, you can take 1d3+1 heat to reload any weapon with the Loading tag as a  
quick action
 

Siege Cannon  

Siege Cannons are the Armory‘s core-squadron level artillery, a howitzer-style 10“ gun fed by a self- 
contained loading system. Commonly mounted on rear-line mechs deployed in an artillery/ squad support  
role, the Siege Cannon is capable of direct fire should the necessities of dynamic combat call for it. Siege  

cannons can fire HE and canister FRAMEs, depending on the target.   

Superheavy Cannon
 
4 heat (self), Arcing, Ordnance, Loading
 
Range 30, Blast 2
 
3d6 explosive damage
 

                                                                                                                

\subsection{Harrison Armory Genghis}
                                                              
                                  HARRISON ARMORY GENGHIS  

The GENGHIS is a unique Harrison Armory chassis, developed to fill a niche specialist role during the  

Hercynia crisis. Due to the unique nature of the Egregorians, a total-biome-kill system was necessary to  
ensure localized threat neutralization while keeping Hercynia habitable for future colonists. Thus, the  
GENGHIS chassis was developed. Fielding a suite of TBK systems and weapons, GENGHIS squadrons  

were dispatched by Union MEF-105 to identify and strike the Egregorian hives. The campaign was a  

success, and Hercynia is currently undergoing rehabilitation and repopulation in approved settlement areas.    

                                                       License:   
I. Flamethrower, Explosive Vent
 
II. GENGHIS FRAME, Auto-Cooler, HAVOK Mine
 
III. AGNI Class NHP, Plasma Thrower
 

                                                                                                                    


                                                GENGHIS 

HP: 6          Evasion: 6                            Speed: 3            Heat Cap: 10       Sensors: 5 

Armor: 3       E-Defense: 8                          Size: 1             Repair Cap: 4      Tech Attack: -2 

                                                  TRAITS: 

Insulated: The GENGHIS is immune to Burn
 
Emergency Vent: When the GENGHIS loses a point of structure, it immediately cools and clears its  
heat gauge. 

                                            SYSTEM POINTS: 5 

                                                 MOUNTS: 

Flexible Mount                                        Heavy Mount 

                                               CORE system 

                                            TBK Sustain Suite 
In order to better manage the tremendous power demands of the GENGHIS platform, HA’s Think Tank 
developed a suite of power-management protocols to rapidly accelerate heat dispersion. After extensive 
field testing, pilots discovered that the TBK Sustain Suite can be tuned to be both a heat sink and a 
area-denial weapon. 

Active (requires 1 core power): Expose Power Cells 
Quick action 
You ignore the next overheating check you make this challenge. When you would overheat, clear your 
heat from your gauge as normal, but ignore the check (you don’t take stress either). You vent an 
enormous cloud of burning matter from your mech, creating a burst 3 area centered on your mech. 
Inside the area, all targets (allied and enemy) count as invisible to everyone except you, and all mechs 
other than you that enter the area for the first time on their turn or start their turn there take 2 Burn and 
2 heat. 
On the following round, the benefit from the area reduces to heavy cover (which you ignore). On the 
round after that, it reduces to light cover. On the round after that round, the zone disperses. 

                                                                                                           


Flamethrower  

The HA Krakatoa was developed specifically for the Hercynian crisis, as chassis-size flamethrowers had  

been deemed unnecessary, and more to the point, banned by anti-terror conventions. With the  
combination of thick arboreal environment, swarm tactics of the Egregorians, and ineffectual performance  
of slug ammunition, the need for a recession on the ban was apparent. The Krakatoa was quickly  

developed and affiliate patterns disseminated. Adopted by Union MEF units, the Krakatoa saw heavy use in  
the deep world-jungle of Hercynia and towering hives of the Egregorians thanks to its stability, intensity,  
and stopping power — a necessary feature competitor makes lacked. Egregorian drones and warriors,  

commanded by their overminds, would not stop advancing until they were physically incapable of doing so  
— the force at which the Krakatoa expelled flame and fuel was sufficient to knock back or otherwise  
incapacitate charging warriors on the periphery of the flame cone. Reworked after the cessation of the  

Hercynian crisis, the Krakatoa is now a popular tool for creating area-of-denial firebreaks. It’s legality is  
currently under review by the Galactic Treaties Board.    

Heavy CQB
 
Cone 5
 
Burn 4 + 1 heat
 

Explosive Vent  

Less a technology and more of a tactic, explosive venting is an unsanctioned, unsafe method of sudden  
cooling that dumps excess heat into the surrounding area immediately around the chassis.  

2 SP, Unique  
System  

                                                                                                               


When you cool heat, you explosively vent heat in a burst 1 area around you. Affected targets,  
friend or foe, take 1d3 heat and burn.
 

Auto-Cooler  

An HA-designed automatic cooler is a simple, sturdy persistent system that helps pilots mitigate damaging  
heat generation.   

2 SP, Unique, Protocol  
Activate this cooler as a free action at the start of your turn. If you don’t take damage, move, or  
overheat before the start of your next turn, cool your mech at the start of your next turn.
 

HAVOK Mine  
FOR USE IN: Urban, post-urban, and high-density terrestrial environments. High O   concentration  
                                                                                              2  

preferred.   

FOR USE AGAINST: Organic targets preferred. Hardened targets vulnerable to caustic/corrosive  
degradation preferred. Defoliant. Long-term breach solution.   

NOTES: Dispersion is true directional. Dispersion involves aerosolized component -- avoid blue on blue by  
supplying end-users with proper respiratory equipment (noted on canister).  

2 SP  

Mine, Limited (2)  
When detonated, this mine attacks a line 5 zone from the mine instead of a burst area around the  
mine (oriented in any direction). Affected targets must pass an agility check or take 6 Burn or 3  
Burn on a successful check.
 

Plasma Thrower  

The plasma thrower arrived late in the Hercynian Crisis, too late to see widespread battlefield application.  
Some MEF squadrons were able to mount the superheavy system, and what little data there is to see from  
its use suggests that this system would have had a tremendous impact during the major battles that raged  

in the deep jungles during the middle of the Crisis.   

Superheavy CQB
 
4 heat (self)
 
Cone 7
 
Burn 5 + 1d6 heat
 

AGNI-class NHP  

AGNI was developed from the aftermath of the Hercynian Crisis using a combination of combat  
performance data recorded by extant subsentient artificial intelligences (weapons systems, chassis  
copilots, tactic-minds, general combat data) and the neural network of an Egregorian hivemind captured  

and vivisected by Union Science Bureau.   

                                                                                                                       


Born from trauma, AGNI Prime devised systems of heat management that have since been disseminated  
throughout core space to ensure unparalleled heat processing, recycling, and shielding. Further  
developments into radiation shielding, omninet capability, and drone/nanite control are forthcoming;  

meanwhile, AGNI clones have been optimized for mech chassis core systems.  

Pilots report AGNI clones as generally cold and efficient. A low percentage report instances of memory  

recitation and command rejection, often followed days later by total breakdown through attempted self- 
emancipation. Pilots are recommended to cycle their AGNI clones at least once every six standard months.    

3 SP, Unique  
AI  

Your mech gains the AI property and the AGNI protocol
 
         AGNI protocol  
	        Protocol  
         Limited (1)  
         At the end of your turn, you automatically cool, clearing your heat gauge. This vent  
         creates a burst 3 zone around you. All targets within that zone must make an engineering  
         skill check. On a failure, a target takes 2 Burn and is pushed outside the zone (or as far as  
         possible). This area provides light cover until the end of your next turn.
 
         This protocol can only be activated once per scene.
 

                                                                                                                   
\subsection{Harrison Armory Iskander}

                              HARRISON ARMORY ISKANDER  

The ISKANDER is a specialist‘s chassis, designed to provide area-denial and breach capability to squads in  
which it is a member of. A large chassis, the ISKANDER commonly sports weapons meant to ensure  

dominance in all close-quarters situations, as well as increased blast shielding to protect its pilot from  
deadly concussive forces. 
 
                                                   License:
 
I. Stub cannon, Repulsor Field
 
II. ISKANDER FRAME, Assault Launcher, Gravity Gun
 
III. Sticky Bombs, Grounding Charge
 

                                                ISKANDER 

 HP: 8          Evasion: 8                            Speed: 3           Heat Cap: 7        Sensors: 15 

 Armor: 1       E-Defense: 10                         Size: 2            Repair Cap: 4      Tech Attack:  
                                                                                            +1 

                                                  TRAITS: 

 Mine Deployers: When the ISKANDER uses a quick action to plant a mine, it can plant up to 2 other  
 mines in free adjacent spaces as a free action.
 
 Skeleton Key: The ISKANDER never activates mines or other systems that activate by proximity unless  
 it chooses to (allied or enemy). 

                                            SYSTEM POINTS: 6 

                                                  MOUNTS: 

 Flexible Mount                    Heavy Mount 

                                               CORE system 

                                                                                                            


                                             Broad-Sweep Seeder  

 The ISKANDER’s broad-sweep area-denial/countermeasure Seeder is a HA proprietary system  
 developed during the Orrugi Occupation, where HA Acquisition Legionnaires encountered an  
 embittered, recalcitrant local guerilla movement. IEDs, VBEDs, and D/SABEDs were common weapons  
 employed by the local resistance: to counter this threat, the Armory developed a triple-use system to  
 scan, ID, and eliminate explosive threats in proximity to stationary units. This system proved successful  
 and, with minor adaptation, was tuned for use on Armory chassis.   

 The Broad-Sweep Seeder projects a hivecone of excited LIDAR that flags potential targets: mag- 
 accelerated, dull-coat flechettes then disable that target. This system may also load explosive-backed  
 hivemines.   

 Active (requires 1 core power): Death Cloud
 
 Action
 
 As an action, your mech fires an enormous expanding cloud of micro-mines across the whole  
 battlefield. Any mech of your choice on the whole battlefield (or a roughly 50x50x50 area), that  
 voluntarily moves more than 1 space takes 3 AP explosive damage. If a mech boosts, it takes 3 AP  
 explosive damage immediately. Characters are aware of the presence of the mines. They last until the  
 end of 3 rounds, counting this one, then deactivate.
 
 You do not activate mines from this system. 

Stub Cannon  
A supercompact rotary pistol, short range, but able to be integrated into hardpoints or held in a  
manipulator.  

Auxiliary Cannon
 
Limited (6), Knockback 1
 
Range 5
 
3 explosive damage  

Repulsor Field
 

1 SP, Unique
 

Quick Action
 
You can use this system as a quick action to emit a burst 2 pulse around your mech. Targets  
caught in the area (allied or enemy) must pass a hull check or be knocked back directly away  
from you 1 space. The pulse then detonates any mines or explosives caught in the field
 

Assault Launcher  

Assault launchers are universal launchers. Ammunition is loaded first into a comparable sabot, then  
electromagnetically accelerated either directly or indirectly towards its target. The sabot shatters upon  
firing, releasing the projectile to perform as designed at range far greater than factory limits.   

2 SP  
You can fire and deploy mines and grenades up to any point in range 15 and line of sight instead  
of their regular range. 
 

                                                                                                               


Gravity Gun  
The complex negotiations of gravity and time, shattered in an instant by a machine that can pluck  
a waves like a player strums a guitar string.   

We’ve weaponized the thing that holds all things in its embrace. What could go wrong?  

Heavy Rifle
 
Range 8, Blast 3
 
When you attack with this rifle, all targets caught in the area must pass a hull check or take 1d6  
energy damage and be pulled as close to the center of the blast as possible.
 

Sticky Bomb Launcher  

Sticky bombs attach to ferrous metals by means of burnout electromagnetic generators, triggered in  
proximity after firing or manually by the user.   

Main Launcher
 
Arcing
 
Range 15
 
To fire this weapon, you can attack a point on the environment within range without rolling, or  
make a regular ranged attack roll against a target within range. On a hit, the target or area does  
not take damage, but instead has a sticky bomb attached. It takes a quick action and a  
successful engineering check to remove all sticky bombs from an area or mech.
 
As a free action, you can detonate all sticky bombs fired by this weapon to deal 1d6 explosive  
damage in burst 1 area centered on all targeted mechs or areas. Mechs caught in the blast area  
can pass an agility check to halve this damage, but mechs ‘stuck’ by this weapon fail their check  
automatically.
 

Grounding Charge  

Grounding charges take the pulse/wave principle of the thumper and applies a second component: gravitic  
generation. When triggered, the initial pulse wave acts similarly to the Thumper, but immediately after the  

wave dissipates, the grounding charge triggers a gravity well that pulls all destabilized materiel towards it. A  
potent anti-positional weapon, grounding charges are commonly used to disrupt prepared positions and  
pull enemies from cover.   

2 SP, Limited (1)  
Mine  
This charge can also be detonated with a quick action. Once detonated, targets in a burst 6 area  
centered on the charge must make a successful hull check or be knocked prone and pulled as  
far as possible towards the charge as though they moved normally (starting with the closest  
target). The charge also pulls any flying mechs or vehicles within range 6 above the area that fail  
the check to the ground, taking damage as if they fell.
 

                                                                                                                


\subsection{Harrison Armory Napoleon}


                             HARRISON ARMORY NAPOLEON  

Perhaps in a tongue-in-cheek nod to its namesake, the NAPOLEON is a squat silhouette when fielded next  

to other Harrison Armory chassis. But packed into its compact frame are marvels of Armory engineering,  
technology that demands the NAPOLEON be piloted only by the best and the brightest. Stasis technology  
is the very cutting edge of gravitic manipulation technology, only now hitting the commercial market for  

those with the requisite licenses. The NAPOLEON incorporates a mix of gravitic manipulation technology,  
proven anti-kinetic/energy shielding, and superpositional force multiplication to dominate enemies --  
earning its namesake through battlefield success as well as stature.    

                                                  License:
 
I. Phasing Weapon, Stasis Barrier
 
II. NAPOLEON FRAME, Stasis Mine, Dispersal Shield
 
III. H.A. Blackshield, Displacer
 

                                               NAPOLEON 

 HP: 6          Evasion: 8                           Speed: 4           Heat Cap: 8       Sensors:  5 

 Armor: 2       E-Defense: 8                         Size: 1/2          Repair Cap: 3     Tech Attack:  
                                                                                          +0 

                                                  TRAITS: 

 Well shielded: If the NAPOLEON would take half damage from an effect (weapon, system, explosion,  
 etc) on a successful check of any kind, it instead takes 0 damage.
 
 Flash Aegis: When the NAPOLEON Braces, it reduces damage to 0 instead of gaining resistance 

                                            SYSTEM POINTS: 7 

                                                 MOUNTS: 

 Main/Aux Mount 

                                               CORE system 

                                                                                                          


                                                HA Vantablack Aegis  

 The Armory’s VANTAblack AEGIS system is a breakthrough in personal shielding developed by HA’s  
 Think Tank. In line with other NHP-derived technologies, the VANTAblack is a so-called “black-box”  
 technology; pilots with requisition power to obtain a VANTAblack system are typically of high rank or  
 standing within HA, and the inner workings of the system are not known to the public at large. On  
 outward appearance, the VANTAblack system has been described by Cosmopolitan pilots as similar to  
 the void/blindness one has when looking out at blinkspace; it is safe to assume that the system utilizes  
 unstable blinkfield technology to manifest a thin blinkspace bubble within defined parameters around  
 the system -- the blinkfield can only sustain for a brief moment, but can be flickered to create an  
 essential-total blinkspace dome.       

 Active (requires 1 core power): Activate Aegis  
 Quick Action
 
 A shimmering, utterly black field envelops your mech, covering it like a second skin, and taking only a  
 few moments to activate. While this field is active, your mech reduces all damage from any source to 1  
 (after armor as normal), though it can still be grabbed, knocked back, pinned, thrown, and affected by  
 other mechs.
 

 While this shield is active, your mech can only move and make the grapple, improvised attack, ram,  
 and boost actions. It cannot take free actions, reactions, or overcharge, and cannot use any systems or  
 benefit from Flight (if it’s already flying, it falls). It cannot make or be the target of any tech actions  
 (including lock on, etc), cannot benefit from beneficial tech actions (such as lock on, bolster, etc) and  
 cannot communicate or receive communications with or from anyone except the GM (though hand  
 signals are still possible). 
 

  It can still be affected by statuses, grappled, and take heat. It can otherwise interact normally with the  
 world, such as picking up or dragging items, etc.
 

 The shield lasts until the end of the current challenge, or about ten minutes otherwise.
 
 Damage that goes through reduction (such as paracausal ammo) can still harm the Napoleon while its  
 aegis is up. 

Phasing weapon  

Phase-Ready ammunition, as first described after its incorporation into the civil hostilities on Luna de Oro,  
is the “devil‘s round“: each round contains a nanoprocessor suite networked with its firing weapon that,  
ideally, calculates and translates the specific nature of that round‘s superpositional relation with its  

doppelgänger in the immediate space before its intended target. To wit, Phase Ready ammunition, when  
fired, exists in two places at once: exiting the barrel of the weapon it was fired from, and at the moment of  
impact into its target. The prime round may never hit its target, but as it already exists at the moment of  

impact, its doppelgänger round will hit its target. The fuzzy nature of such spooky action occurs in a way  
not fully understood save for in the faltering explanations of Harrison Armory‘s NHP Think Tank; as such,  
the action is not perfect, but falls within acceptable parameters for licensed production.   

2 SP
 
Mod
 
Choose 1 weapon. This weapon can totally ignore line of sight and cover as long as you roughly  
know your target’s location when you attack, but your target counts as having invisibility if you  

                                                                                                                       


attack this way. This weapon can attack through solid walls or obstacles, as long as its target’s  
location is known and they are in range.
 

Stasis Barrier  

Stasis Barriers are the result of Harrison Armory‘s interest in gravitic manipulation and superpositional  
negotiation. Contained within a solid-state generator/projector, a Stasis Barrier is a deplorable wall of  

antigravity, contained by its power supply, that interdicts and denies most all incoming kinetic and energy- 
based weaponry. Another of HA‘s NHP Think Tank development, the Stasis Barrier is now a mainstay of the  
Armory‘s personal and materiel defense line and a common enough sight on all Armory Depot/ 

Development worlds. By manipulating local gravitational forces, the Barrier rejects projectiles and energy  
lances, denying particles and waves both on a molecular level; matter that impacts a Stasis Barrier simply  

ceases to exist, save for anomalous fluctuations that cause some projectiles to break through. As the  
Barrier is technology from the Armory‘s Think Tank line, some of its fuzzy nature is not fully understood, but  
rest assured failsafes have been installed to force a regular cessation of projection to ensure the device  

remains operating within established safe parameters.   

2 SP, Limited (1)  

Shield, Deployable  
This module deploys as a 4 space long piece of size 2 cover that lasts until the end of the current  
challenge. While behind the barrier, a target counts as having heavy cover and has resistance to  
all damage from blast, line, and cone attacks. At the end of the challenge, it deactivates and is  
used up. The cover itself is immune to all damage.
 

Stasis Mine  

Stasis Mines developed by the Armory‘s NHP Think Tank, are portable, unit-specific versions of Stasis  

Barriers. Initially pegged as a potential personal shielding device, early tests proved that stasis is as-yet  
detrimental to the individual inside a projected field. Think Tank suggests that the cognitive hazards of  
sudden and total pause of temporal/gravitic/positional existence without preparation -- however long the  

stasis session lasts -- is irrevocably traumatic.   

1 SP,  Limited (1)
 

Mine
 
You can detonate this mine with a quick action once planted (or it activates normally). Once  
detonated, this mine creates a burst 4 area around it. Affected targets may make an agility check  
with 1 difficulty to escape if on the edge, otherwise they are trapped inside. The area inside is  
locked from the normal flow of space time, creating an impermeable barrier around its edge.  
Effects, mechs, and pilots inside are stunned and removed from play until the end of next round,  
and all other effects cannot penetrate into the area. Time does not flow normally for targets  
inside the area (it stops completely), and is separate to the outside world. Active effects, attacks,  
modules, and other individuals and actions inside the area pause. At the end of the the next  
round (after all characters have acted), this area returns and resumes play as normal.
 

Dispersal Shield  

Dispersal Shielding is a milder form of stasis projection that manipulates only gravity, adjusting the  
perceived mass of its user so that projectiles and excited particles bend and warp around and through  

                                                                                                                    


them. Hostile fire does not quite “miss“ so much as they undergo atomic shuffling, disincorporating on the  
atomic level so that they pass through their targets without colliding.   

3 SP, Unique  
Reaction, Shield
 
1/round you can force any attack that misses you to be re-rolled against a target of your choice  
within your attacker’s range (even a target allied to them).
 

Harrison Armory Blackshield  

The Armory Blackshield leans into the fuzzy nature of quantum manipulation characteristic of Think Tank  
research and development. The Blackshield operates in similar fashion to blinkspace gates, generating a  

pulse of spherical energy that allows its operator to pierce perceived space/time and exist, for a moment, in  
the null-environment of blinkspace. Blinkspace, described by early test pilots and their NHP companions, is  
a void, a space outside of human perception that it at once infinite and without form, blank and cacophony.  

NHPs that accompanied those first pilots have since been retired, their handlers citing recursive ontological  
tail-chasing and paracausal obsession; since then, NHP protocols have been updated to include a sense- 
exposure doctrine, allowing them to do as corporeal, sapient pilots do and simply accept the unreality of  

blinkspace without going mad. Think Tank NHP‘s and their counterpart engineers acknowledge the tactical  
benefits of (non)momentary (non)existence in blinkspace, but they caution pilots against repeated exposure  
without sufficient pre-and-post exposure conditioning and counseling.   

2 SP  
Shield, Unique  

Full Action  
4 heat (self)  

As a full action, this system can be activated to generate a burst 4 area centered on user. While  
active, the flow of time is altered drastically in a small sliver of space in a bubble around the user.  
Nothing, not even light, can enter or exit the shield. It is impermeable and invulnerable. When the  
shield is activated, mechs caught on the edge must make an agility check to choose which side  
they end up on, otherwise the user chooses. To those inside the shield, the world outside the  
shield goes totally black, and the inverse happens from outside. No action or effect can enter or  
exit the shield while it is active or draw line of sight though (even those that normally ignore it),  
though time passes normally on both sides. The shield drops automatically at the end of the  
user’s next turn.
 

Displacer  

The Displacer is the result of ongoing blinkspace exposure tests in Think Tank‘s R\&D department and  
miniaturization of commonly employed interstellar travel methods. The Displacer itself is conventional in  

appearance but requires a massive secondary, dorsal-mounted core in order to power: when fired, the  
Displacer identifies a bubble of local space (size and location determined by the firing pilot) and snaps it  
into blinkspace. Where the contents of that bubble go is unknown, but the effect is dramatic: anything  

inside the projected bubble simply ceases to exist in this dimension, transported somewhere else in the  
void of blinkspace. The Displacer makes no sound when fired, but the sudden and necessary venting of its  

                                                                                                                        


power supply is tremendous; similarly, the heat wave of its backblast is deadly to any unshielded personnel  
exposed to it.   

Main Rifle
 
Unique, Loading, AP, 10 heat (self)
 
Range 10, Blast 1
 
10 energy damage
 

                                                                                                                
\subsection{Harrison Armory Saladin}

                                HARRISON ARMORY SALADIN  

The Saladin chassis provides a platform for pilots to mount squad-support tier shielding. Developed in  

response to anti-slaver engagements in the Tian Shan ring, Harrison Armory’s SALADIN chassis proved an  
invaluable member of Present/Persistent Danger Escort/Evac teams sent in to evacuate emancipator teams  
\& their charges. Records from these engagements indicate that the SALADIN’s massive bulk alone was a  

comfort and morale boost to emancipator squads, who often referred to the chassis pattern as “Big Sal”;  
SALADIN pilots from that era report null balances on bar tabs when present in emancipated systems.   

                                                   License:
 
I. Support Shield, Impulse Missiles
 
II. SALADIN FRAME, Paracausal Ammunition, Projected Shield
 
III. VISHNU-Class NHP, Hardlight Defense System
 

                                                 SALADIN 

 HP: 12         Evasion: 6                            Speed: 3            Heat Cap: 8        Sensors: 10 

 Armor: 1       E-Defense: 8                          Size: 2             Repair Cap: 4      Tech Attack:  
                                                                                             +0 

                                                   TRAITS: 

 Reinforced frame: The SALADIN is immune to the shredded condition
 
 Warp Shield: As a reaction 1/round, the Saladin can impose +1 difficulty on any attack roll that targets  
 itself or an ally in sensor range  

                                             SYSTEM POINTS: 8 

                                                  MOUNTS: 

 Flexible Mount 

                                                CORE system 

                                                                                                             


                                                  Tachyon Loop
 
 Developed by HA’s Think Tank as a joint venture with IPS-Northstar’s stellar engineering unit, a Tachyon  
 Loop manipulates a tachyon lance and restrains them to a closed-loop system, accelerating tachyon  
 particles at faster-than-light speeds around a central buckler. The shield is carried and mounted on a  
 chassis to intercede directional incoming fire: as the tachyon particles are traveling faster than light, they  
 are invisible to the naked eye, giving the shield the appearance of a large spoked wheel.   

 Active (requires 1 core power): Empower Shield  
 Quick Action
 
 You can empower this shield, projecting it over an ally in your sensor range. As long as they remain in  
 your sensor range, once per round, when an attack roll misses either you or the target of this shield,  
 you can force the attacker to repeat the attack roll against a target of your choice within range (even a  
 target allied to your attacker). This effect lasts until the end of the current scene, and you can swap  
 your target by taking this action again. 

Support Shield  
The HA Support Shield, ENCLAVE-pattern, creates a localized one-way blink field, folding a thin dome of  

spacetime around its user to protect occupants from incoming projectiles. Units covered by the field can  
fire out, but probabilistic fluctuations cause incoming projectiles to “lag”, skipping them away from their  
intended target and into a randomized trajectory.   

2 SP, Unique  
Shield, quick action, 2 heat (self)
 

Activating this system generates a Burst 3 area centered on you until the end of your next turn.  
All ranged or melee attacks made against you and any allied targets inside the shield that  
originate from outside the shield are made with +1 Difficulty, but your mech is immobilized for the  
same duration.
 

Impulse Missiles  

Main Launcher
 
1 SP
 
Range 10, Arcing
 
1d3+1 energy damage
 
The attack roll for this weapon cannot be any worse than a regular roll (it can’t suffer any  
difficulty on the final roll)
 

Paracausal weapon mod  

Paracausal weapons are, to say it plain, difficult to describe and visualize. The first incident was recorded  
when paracausal ammunition was pushed to frontline soldiers during the Tian Shen civil engagements. It  

arrived in sealed magazines with directions to be loaded and fired as normal. There was to be no inspection  
of the magazines’ contents, as this would “damage the payload” — frontline reports indicate that this  
ammunition impacts as normal on intended targets, though it seems to pierce armor and shielding at  

                                                                                                                 


near-100% efficacy. Samples of paracausal ammunition have been flagged by Union for retrieval, and due  
to its development Harrison Armory is currently undergoing investigation by the Bureau; paracausal  
ammunition is still in use in the field, however, as shipments continue to leak to interested parties. HORUS  

is suspected, and a concurrent investigation is underway.    

4 SP  
Mod
 
Choose one weapon- damage from this weapon cannot be reduced in any way, by armor,  
resistance, or any other kind of damage reduction.
 

Projected Shield  

The Armory’s mainstay squad-support shielding system. A projected shield takes the standard shield and  
projects it to a nearby allied mech, hardsuit, or infantry squad, ensuring the same coverage as a personal  

shield through a higher intensity series of amplifiers.   

1 SP, Unique  
Shield, Protocol  
Activate or deactivate this shield at the start of your turn. Choose an allied mech. Until the end of  
your next turn, as long as that mech is in your sensor range, all attacks against that mech are  
made at +1 Difficulty, but deal 1 heat to you on a hit.
 

Hardlight Defense System  

The HA HARDLIGHT defense system is an imperfect implementation of a theoretically perfect technology.  
Currently in development by HA Think Tank NHPs and attendant engineers, hardlight technology projects  

tight, stable waves of light akin to lasers that repel matter and impulse energy: this, in effect, creates a  
stable, hard surface, useful for shielding or (theoretically) providing a projected surface. However, current  
technology is unable to lower the ambient temperature of such a surface to one low enough to not burn  

organic matter.  

3 SP, Unique  

Shield, full action, 4 heat (self)
 
Activating this system generates a line 6 section of size 1 hardlight in free unoccupied space in  
sensor range until the end of the current scene. It grants heavy cover to any adjacent character.  
The hard light is immune to all damage and the barrier does not occupy physical space (it can be  
crossed). However, any character that does so, willingly or otherwise, must pass an engineering  
check or take Burn 6 and Burn 3 on a successfully check. This barrier can be reactivated and  
moved by using this system again, but only one can be active at a time.
 

VISHNU-Class NHP  

Developed to be a metropolitan administrative NHP on Ras Shamra, the VISHNU NHP strain does not, at  
first, seem like a viable candidate for military application. However, after being flagged by Think Tank for  

review following numerous anomalous traffic incidents, Armory ontologisticians and engineers were able to  
discover and emphasize protocols endemic to Vishnu Prime that could be exploited for tactical advantages.   

                                                                                                                      


Through numerous iterations and lifecycles, VISHNU Prime displayed a sharp ability to adapt to kinetic  
situations. A proclivity towards crisis management and multiple-k actor tracking led to VISHNU’s pairing  
with the Armory’s ENCLAVE shield system; by networking a series of jet-assist mobility drones carrying the  

ENCLAVE system, monitored and controlled by a VISHNU clone, Think Tank was able to create an  
unparalleled personal shielding system: the DHARMA WALL.  
 

3 SP, Unique  
AI  

Your mech gains the AI property and the following protocol:
 

         DHARMA WALL  
         Protocol  
         3 Heat (self)  

         Until the end of your next turn, your mech is immobilized, but all ranged weapons that  
         target you add +1 Difficulty to their attack rolls. If a weapon misses you while DHARMA  
         WALL is active, you may deal 1d6 damage to its owner. The damage dealt this way is the  
         same type as the attempted attack.
 

                                                                                                                    


                                                                                                                            
\subsection{Harrison Armory Sherman}
                                                                                                                      


                              HARRISON ARMORY SHERMAN  

The SHERMAN is Harrison Armory‘s line-model chassis: any station, nation, world, stellar, or interstellar  

state that holds a fleet-tier contract with Harrison Armory fields a backbone force of localized SHERMAN  
cores. The SHERMAN platform is tuned to provide a rugged, versatile power plant for HA‘s fleet-line  
energy weaponry and a heat-dispersal system to ensure that the tremendous power requirements do not  

overwhelm the chassis‘ tolerance. Next to GMS‘s EVEREST, the SHERMAN is the second most-common  
mech chassis in the core systems, so much so that GMS has recently made a push to include more  
ablative and wave-scatter defenses into its stock +1 models to deal with hostile actors fielding the  

SHERMAN.   

                                                  License:
 
I. Reactor Stabilizer, Laser Rifle
 
II. SHERMAN FRAME, Heavy Laser, Redundant Systems Upgrade
 
III. ASURA Class NHP, Tachyon Lance
 

                                                SHERMAN 

 HP: 10         Evasion: 7                            Speed: 3           Heat Cap: 8       Sensors: 10 

 Armor: 1       E-Defense: 8                          Size: 1            Repair Cap: 4     Tech Attack:  
                                                                                           +0 

                                                  TRAITS: 

 Superior Reactor: The Sherman has +1 accuracy on engineering checks
 
 Vent Heat: When the Sherman takes the stabilize action, it counts as in light cover until the start of its  
 next turn 

                                            SYSTEM POINTS: 5 

                                                 MOUNTS: 

 Flexible Mount                    Main Mount                            Heavy Mount 

                                               CORE system 

                                                                                                           


                                       Zone Focus Mk IV  SOLIDCORE  

 The Harrison Armory ZFMk IV SOLIDCORE is a dual-source energy beam weapon hard mounted to a  
 chassis. Powered by a milifold power generation system, the ZFMk IV features a secondary belt-fed  
 rack of solid-core batteries that can be used to overcharge a single impulse beam, extending the range  
 and destructive power of the weapon.      

  Integrated Mount: Your mech mounts the ZFMk IV SOLIDCORE, a powerful energy beam weapon.
 
 SOLIDCORE  
  Main Cannon
 
 Ordnance
 
  Line 15
 
  1d3+1 Energy damage
 

 Active (requires 1 core power): COREBURN Beam
 
  Full Action
 
 As a full action, your mech begins to charge this weapon but cannot move or take any other action this  
 turn. Your mech stops charging this weapon if it becomes stunned, shut down, jammed, knocked  
  prone, or any effect that would cause it to be unable to attack (if it is unable to fire, don’t spend the  
 core power). The turn after you start charging this weapon, you may fire it by taking Full Action again.  
 Choose a line 30 area originating from your mech. All mechs caught in the area must pass an agility  
 check or take 12d6 energy damage, and half on a successful check. Any obstacles or deployables in  
 the way are hit automatically and the beam easily penetrates through cover. This beam counts as an  
 attack for purposes of systems, talents, etc. 

Laser Rifle (SOL-Pattern)  

The laser rifle is a near-ubiquitous weapon throughout the galaxy, the energy-based cousin to GMS‘s Type-I  
AR. To call it a rifle, though, is shorthand: a laser rifle is a projector that utilizes a series of apertures and  
lenses to amplify and focus light into tight beam, visible in the right circumstances, that paints a target long  

enough to heat the area of “impact“ into plasma. The HA SOL-pattern laser rifle is capable of a 3.5PW  
maximum output, pulsed, but can project a beam at lower power levels; additionally, while some laser rifles  
can double as communication/data transfer devices, the Armory‘s SOL is strictly tuned for combat, and has  

no such communication capability. The SOL is a solid state and entirely self-contained, but can be patched  
into a chassis‘ reactor core for operation and to re-charge spent weaponry. Energy weapons, while having  
downsides of their own, are commonly used in micro-and-zero-gravity environments due to having no  

impulse or kinetic user feedback.   

Main Rifle
 
Range 10
 
1 heat (self)
 
1d6 Energy Damage + Burn 1
 

Reactor Stabilizer  

A necessary component of most energy-based mechs, reactor stabilizers add another layer of failsafe  
protocols to vent heat, manage power flow, and shunt excessive output into weapons and systems in need.   

3 SP, Unique  

                                                                                                                 


When you gain a point of reactor stress, you can re-roll your overheating check (but must keep  
the second result, even if it’s worse).
 

Heavy Laser  

A heavy laser rifle is a larger-scale laser weapon. The Harrison Armory ANDROMEDA-pattern heavy laser  
scales up the SOL by half, adding a second projector that can fire independently, synchronized, or in  

alternating patterns and wavelengths as the primary projector. The effect overwhelms most shields, but the  
power draw necessary makes this weapon impractical on platforms without the necessary heat reduction/  

dispersal to manage the incredible cost.   

Heavy Cannon
 
3 heat (self)
 
Range 15
 
2d6 energy damage + Burn 3
 

Redundant Systems upgrade  

A common right-of-distribution modification by pilots in forward operating bases, building further  
redundancy into a chassis‘s systems guarantees a measure of reliability beyond stock design standards.   

2 SP, Unique, Limited (1)  
You can activate this module to make a Stabilize action as a quick action.
 

ASURA-class NHP  

ASURA was born from the Armory‘s Think Tank thought-war games as a response to repeated failures  

during a forlorn hope scenario test; ASURA manifested in simulated mechs‘ systems as a recode of  
HORUS‘s PUPPETMASTER virus, hijacking friendly cores and forcing them into action far beyond human  
capacity -- action at speed and intensity that the registered g-force caused the sim-pilots to die, suffocated  

and crushed by the sudden amplified mass of their own bodies.   

While such results were initially deemed a failure by Think Tank NHPs and engineers, further study on  

ASURA was commissioned. Personality and parasentience code was injected into the initial anomalous  
PUPPETMASTER, first contact handled by Think Tank NHPs, and societal acclimation and conditioning  
was fast tracked, giving Armory engineers the first iteration of ASURA after roughly a decade of study, re- 

coding, and reeducation. ASURA, as it exists now, is a scaled-back version of that initial manifestation:  
while retaining some of its initial alacratic impulse, ASURA now recognizes the need to keep its pilot alive,  
and will operate within parameters set by its pilot‘s medical and psychological tolerances.  

3 SP, Unique
 
AI  

Your mech gains the AI property and the ASURA protocol:
 
         ASURA protocol  
	        Protocol
 
         Limited (1)
 

                                                                                                                   


         This turn only, gain an extra two quick actions or one full action. These extra actions must  
         still obey normal rules about duplicating actions (you can’t use it to Boost if you’ve  
         already Boosted this turn, for example
 
         This protocol can only be activated once per scene.
 

Tachyon Lance  

The tachyon lance is the weaponized result of early Harrison Armory experiments into faster-than-light  
travel. Rendered obsolete by developments in blinkspace travel and the difficulty of ensuring corporeal  

passenger survival, HA‘s tachyon accelerators were mothballed until Think Tank engineers realized their  
potential application as weapons. A tachyon accelerator projects tachyon particles -- essentially a  
subatomic localized object -- faster than light towards its target. These particles are impossible to see  

through optical/visible means: as they travel faster than light, they cannot be seen or avoided intentionally.  
Though the size of the particle is tiny, the sheer speed and energy of travel is titanic, and the damage a  
tachyon lance imparts on its target -- should it connect -- is unparalleled.   

Superheavy Cannon
 
Ordnance, 4 heat (self)
 
Range 20, Burn 8
 
2d6 Energy damage
 

                                                                                                              
                                                                                                             
\subsection{Harrison Armory Tokugawa}

                             HARRISON ARMORY TOKUGAWA  

HA’s TOKUGAWA chassis is a relative newcomer on the market, popular in core systems for security and  

CQB/ breach applications. The TOKUGAWA is a large, imposing mech, a sturdy platform from which the  
recommended kit can draw the necessary power it needs in order to perform within optimum parameters.   

                                                  License:  
I. External batteries, Annihilator
 
II. TOKUGAWA FRAME, Experimental heat sink, Plasma Lash
 
III. Torch, AMATERASU class NHP
 

                                                                                                          


                                                    TOKUGAWA 

  HP: 8            Evasion: 8                              Speed: 4             Heat Cap: 8         Sensors: 10 

  Armor: 1         E-Defense: 6                            Size: 1              Repair Cap: 4       Tech Attack: -1 

                                                        TRAITS: 

  Reactor Flare: The Tokugawa’s energy weapon attacks deal +1d6 bonus damage if it has 2 or less  
  reactor stress remaining
 
  Plasma Sheathe: While the Tokugawa is in the danger zone, it’s energy weapon attacks deal all bonus  
  damage as Burn 

                                                 SYSTEM POINTS: 6 

                                                       MOUNTS: 

  Flexible Mount                       Main Mount                               Main Mount 

                                                    CORE system 

                                             Superheated Reactor Feed  

  A certain breed of pilot rides the very edge of catastrophe, swinging between an equal chance of  
  success and failure each moment. Tokugawa pilots are familiar with the howl of their chassis’s heat  
  warning, the warbling siren a song of destruction: with a superheated reactor feed, Tok pilots ramp their  
  heat debt to the max in order to supercharge their energy weapons. This allows them to churn out  
  damage and make no friends in the engineering bay, should they not melt into a ball of slag before they  
  make it back from the line.   

  Active (requires 1 core power):   
  Radiance  
  Protocol
 
  Choose 1 energy weapon your mech is wielding. If it is a ranged weapon, its range increases by 5, if it  
  is a melee weapon, its threat increases by +1. For the rest of this combat, this weapon also deals +1d6  
  Burn damage (roll on each attack). However, each time you fire this weapon, you gain +3 heat. 

External Batteries  
External batteries are by no means a Harrison Armory exclusive, but HA literature will ensure you that HA- 

Brand POWERALL cells are the longest lasting, fastest cycling, and highest capacity solid state cells  
available. A consequence of their high capacity is a proportionate increase in volatility if the system should  
ever be damaged, but pilots looking to utilize HA technology agree through continued use to absolve HA  

from all liability.   

2 SP, Unique
 

                                                                                                                     


Your ranged weapons that deal energy damage gain +5 range, and your melee weapons that  
deal energy damage gain +1 threat. If you take structure damage, this system explodes and is  
destroyed, dealing 3 AP explosive damage to your mech. This damage can’t be prevented in any  
way.
 

Annihilator  

HA specializes in conventional and unconventional arms development; solutions to tactical problems are  
designed both in the lab and in the field, often the latter outperforming the former in combat situations. The  

Annihilator takes its name from pilots’ slang for a field-rigged weapon developed during the Bradbury  
Rebellion, when desperate resistance pilots machined a way of shunting the incredible waste heat of their  
core’s reactor into a directed blast.   

Main CQB
 
AP, 2 heat (self)
 
Range 5, Threat 3
 
1d3+1 energy damage
 
This weapon creates an energy pulse for burst 1 around its target’s location on successful hit.  
Actors caught in the area must pass an engineering check or take 1d3+1 AP energy damage.
 

Experimental Heat Sink  

The Harrison Armory DEEP WELL system is a part of their VANGUARD line of equipment available to  
licensed HA beta testers. Though a complicated and delicate weave of heat exchangers, Harrison Armor’s  

DEEP WELL system attempts to recycle the heat generated by a chassis’ systems into useable energy.  
While the system works well, the delicate nature of the exchange renders the DEEP WELL highly volatile.    

4 SP, Unique  
While your mech is in the Danger Zone, it has resistance to heat.
 

Plasma Lash  

A threat at multiple ranges, the Lash was designed following the Armory’s review of data collected from the  
Hercynian Crisis. After-action reports noted the efficacy of thermal and thermobaric weapons against  
hardened targets, but made constant reference to the limitations placed upon conventional thermal  

weapons: the need for atmosphere-specific fuel, the impact of prevailing weather conditions, the necessity  
of atmosphere.   

Enter the Plasma Lash, an early development into plasma weaponry. Firing an excited toroid of plasma, the  
Lash can be used as a ranged weapon with a delayed-detonation, or, essentially, a point-blank melee  
weapon; if used at point blank range, the toroid is detonated inside of its launcher, directing an intense  

thermal blast directly at its target.  

Main Melee or Main CQB
 
2 heat (self)
 
Range 5, Threat 3
 
1 Energy Damage + Burn 3
 

                                                                                                                     


This weapon can be used with either profile, but not both in the same round.
 

Torch  

The Armory’s TORCH is a backbone core weapon: a heavy, two-handed, dual crescent-bladed plasma  
torch. The melee weapon is powered by its wielder’s reactor, connected by both powerlines and inert  
cabling; it can be separated into two torch-axes, and its plasma blades are capable of being tuned into new  

shapes. A common sight in CQB situations, the torch has of late become a status symbol among pilot  
officers, many preferring to carry them alongside a smaller auxiliary weapon.    

Main Melee
 
1 heat (self)
 
Threat 1
 
1d6 energy damage + Burn 2
 

AMATERASU-class NHP  
AMATERASU came to prominence in the Armory NHP think tank after its repeated victories in war thought- 

games. AMATERASU is characterized by its brash, enthusiastic personality, often expressing frustration  
with timid pilots who have it in their employ; however, this bombastic personality hides a calculating,  

brilliant tactical mind that feeds information to pilots often faster then they can process it. AMATERASU’s  
combat doctrine demands action and impetus, a chaotic blend of reckless maneuvering and aggressive  
offense that keeps defenders beleaguered and unable to respond with any great efficacy. Pilots willing to  

partner with AMATERASU should be aware that this attack style often leaves their cores vulnerable to  
counterattack, and that this NHP enjoys what it calls “good-natured ribbing”.    

3 SP, Unique 
AI 
Your mech gains the AI property and the AMATERASU protocol 
	        AMATERASU protocol 
	        Protocol 
	        1d3+3 heat (self) 
         Increase the bonus damage on hit of your next ranged or melee attack this turn by your  
         current heat after activating this protocol. The chosen weapon must deal at least partly  
         energy damage. 

                                                                                                              
