\section{Smith-Shimano Corpro}

 SMITH-SHIMANO CORPRO   

                                        “YOU ONLY NEED ONE”  

Smith-Shimano is the second-oldest Galactic-Tier corporation next to GMS. An early  
contender in the sublight, downwell, and EVA vehicle race, SSC cut its teeth making some of the  
earliest private mech cores for other corporate colonial expeditions. They specialized primarily in  
construction vehicles, long-range scout suits, and hardened EVA units. The transition to military  
came slowly, but when the ruling partners saw there was a need for mechanized, armed, and  
armored cores, they duo-laterally decided to change their business model.
 

Smith-Shimano mechs reflect their rapid, agile business model and pedigree. They’re built not to  
take hits, but avoid them entirely, to stay mobile and low, to land not the hardest hit, but the most  
accurate. Economy is the name of the game for SSC: why fire a thousand rounds when one will  
do just as good?
 

Smith-Shimano mechs are available to pilots with the proper license. They’re a good choice for  
pilots who want to be quick and hit what they’re aiming at, but not recommended for those who  
want to be on the front line. Remember, Smith-Shimano mechs are meant to avoid the hit, not  
get hit.  
 

SSC Mechs:
 

SSC SWALLOWTAIL (Scout)  
SSC MONARCH (Missile)  
SSC MOURNING CLOAK (Assassination)  
SSC DEATH’S HEAD (Marksmanship  
SSC DUSK WING (Rapid Assault)  
SSC METALMARK (Infiltration Line Mech)  
SSC BLACK WITCH (Magnetic/Battlefield control mech)  

                                                                                                         
\subsection{SSC Pilot Gear}

                                                SSC Pilot Gear  

  Name                  Tags                                       Range            Damage                     Rarity 

 Implanted Gun          Sidearm, Upgrade                           2                1 kinetic                  1 

 Arc Blade              Reliable 1                                 Threat 1         2 energy                   2 

 Coldcore Sabot         Accurate, Loading, Ordnance                15               3 energy                   3 
 AA Rifle 

 Micropack              Loading                                    5, Blast 1       2 explosive                3 
 Launcher 

  Variable Sword        AP, Limited 3                              Threat 2         3 kinetic                  4 

                                                    Pilot Weapons  

*See Entry
 

Arc Blade  

This master-forged sword is threaded with fine filaments and powered either by a slim battery in its handle,  
or a long cable with a universal power adaptor that can be attached to any standardized power pack. A  
sturdy, light weapon, the charged filaments can be triggered by the sword’s user or by proximity to lash  

their enemies with an electric arc even if they do not connect.
 

Coldcore Sabot AA Rifle  

This heavy anti-armor rifle is recognisable by its long, minimalist construction and classic Smith-Shimano  
matte-black colorway. A COLDCORE sabot anti-armor rifle is a consumable-sabot energy weapon that  

uses depleted demi-coldcore units to create a superheated, precise, directed blast of plasma on its user’s  
target. After firing, it must be reloaded; COLDCORE Sabot-AA rifles can be breech-fed, box-fed, or belt- 
fed, depending on their receiver.   

Implanted Gun  
This bespoke biological weapon, integrated with its user’s circulatory, respiratory, and nerve systems, can  

be fired by a triggering thought, association, movement, or memory. Commonly installed in the arm or  
hand, it is a quiet, small weapon, a gun in name only -- it launches a spasm-propelled, fin-stabilized needle  
from a keloidal canal grown to be inserted in the bearer’s arm. With a short effective range and untraceable  

profile, it is a popular choice for assassins.  

Whenever you fire a weapon, you can fire this gun at the same or a different target. As an upgrade, this  

gun doesn’t count against weapon limits.
 

Micropack Launcher  

This heavy rifle is a drum-fed micro-rocket launcher capable of single or automatic fire. A popular choice in  
total-combat environments, the Micropack is a squad-tier support weapon usually carried by a single  
trooper or mounted on a hardsuit’s tertiary arm. SSC developed the Micropack as an all-theater weapon,  

capable of being used in vacuum, submerged, or in any atmosphere -- the Micropack uses an electronic  

                                                                                                                      


trigger to catapult its self-propelled ordinance to a minimum safe distance before the projectile ignites,  
allowing for its use in close-quarters; some skilled handlers learn to use this brief ignition period to skip the  
miniature rockets around corners in boarding actions and station combat.   

Variable Sword  
This pilot-scale variant of the popular SSC weapon is a field-sheathed length of mono-molecular wire  

completely invisible to the naked eye. Only the handle and the tip guide are visible. Coiled while not in use,  
the wire itself can be extended up to 20 feet from the handle, creating an incredibly light and extremely  
deadly weapon that cuts through nearly anything. Due to immense power usage, this weapon can only be  

unsheathed for a short period.  

                                                  Clothing and Armor  

 Name                    Tags           Bonuses                                  Armor        Evasion/     Spd     Rarity 
                                                                                              E- 
                                                                                              defense 

  “FallingWater”          Clothing      Smart, omni-net linked coat              -            -            -       1 
 Overcoat 

 Sylph                    Upgrade       Semi-biological undersuit                -            -            -       1 

 Acherontia              Armor          +3 HP, Extremely fast                    0            10/10        6      2 
 Panoply 

 Eloria Panoply          Armor          +3 HP, Flight                            0            10/10        5      3 

 Mythimna Panoply        Armor          Invisibility                             1            10/10        4      4 

 Nerveweave               Upgrade       Gain bonus speed and evasion             -            -            -      4 

*See Entry
 

Acherontia Panoply  
Named for the fine colors of the spring swift migration on Triaara I, a plains-paradise world in the SSC  

Constellation, the Acherontia Panoply is a lightweight hardsuit with minimal paneling over a tailored half- 
brigandine. Visible armored paneling is kept to a minimum, and without its helm, it is hard to tell that a pilot  
is even armored.   

Eloria Panoply  

The Eloria is the heavier cousin of the Acherontia, a plate-forward brigandine with reinforced panels and  
contrast-color ablative cuirass built for rapid aerodynamic/null gravity movement. The Eloria system  
employs a move/arrest system of impulse thrusters to ensure a pilot using the Eloria’s rapid-reposition  

capabilities always lands in the way they want. 
 

A pilot can use the integrated flight systems in this hardsuit to fly when they move or boost.
 

“FallingWater” Overcoat  
The FallingWater is a signature SSC sartorial anti-ballistic personal protective garment. Created with a  

                                                                                                                        


charged magnetorheological hydrofiber and coached by an attendant comp/con, the FallingWater pre- 
adapts to incoming threats moments before they transfer their kinetic/thermal impulse upon its wearer.   

This couture overcoat fits over any armor or clothing and is interwoven with infowebbing. It has full  
ominnet access, can display image, color, or video on its internal or external paneling, and has an  
integrated companion/concierge unit. 
 

Mythimna Panoply  
The Mythimna panoply is another light, minimalist design by SSC, built to support an anti-optic/photon  

platform that blends its user into any background environment.   

This light hardsuit has a reactive weave that allows a wearer to turn invisible. A pilot can become invisible  

as an action. The invisibility breaks if a pilot takes damage or makes an attack roll. Used outside of  
combat, it lasts about 10 minutes before it must be recharged for another 10.
 

Nerveweave  
Nerveweave blends fibers of HORUS-derived, SSC-modified greywash nanites with fibrous Sylph silk into a  
smart fabric capable of augmenting its wearer’s movement. The predictive/kinetic capabilities of the  

greywash and semi-autonomous/symbiotic nature of the Sylph create an expensive, powerful system  
dedicated to reflexively protecting its pilot (within established parameters)  
 

This enhancement can only be taken as a part of armor. While wearing this armor, a pilot gains +2 speed  
and +2 evasion.
 

Sylph  
Discovered on Acrimea IV, an SSC biome cultivar world, the Sylph is an organic lifeform that appears to  

find homeostasis in nearly any and all environments. Working with breeding-analogous methods familiar to  
SSC bioengineering doctrines, SSC developed Sylph Undersuits -- sterile, living sylphs grown as an  
envelope, fitted to its owner. Once fitted, the Sylph bonds, creating a symbiotic relationship -- it sustains  

itself off the waste products of its host, while protecting its host from a number of hostile environmental  
factors. It can be removed and stored when not in use, where it conforms to whatever container it is placed  
in.  

This semi-biological, skin-tight undersuit can be worn for extended periods. In its natural form, it is  
translucent and semi-liquid, and can be stored easily. It cleans the body, aids its natural healing processes,  

and eliminates waste. Parts of it can be made opaque or translucent or change color or texture. It can cowl  
over the head, providing sealant from vacuum, high protection against radiation, and filtering of air or  
liquid, providing the ability to breathe water for a limited time.
 

                                                       Miscellaneous  

  Name           Tags            Description                                                              Rarity 

                                                                                                                           


Infoskin        Upgrade        This reactive, synthetic polymer bonds easily to real skin               1 
                                and hair. It responds to electronic signals and can rapidly  
                                change color, texture, or even contort or distort, allowing a  
                               wearer to make minor changes in their appearance such as  
                               facial features, hair color, or makeup patterns with a linked  
                                program. 

Panacea         Gear           This fast healing injectable derived from the Sylph protects             3 
                                its host from disease and promotes rapid healing. This  
                                gives 1 use. When injected as a full action, heals a pilot to  
                               full HP, but the shock means a pilot is stunned until the end  
                                of their next turn 

                                                                                                                         
\subsection{SSC Core Bonuses}

                                         SSC CORE BONUSES  
When you choose a core bonus every 3 license levels, you can pick a bonus from this list as long  
as you have at least 3 license levels in SSC licenses for each SSC bonus you have. For example,  
if you have 6 points in SSC licenses, you could take up to 2 bonuses. SSC bonuses are focused  
on increasing speed, evasion, and ranged combat.
 

FULL SUBJECTIVITY SYNC  

By creating a strong, stable, and secure biased two-way ontologic bridge, SSC has removed the need for a  
pilot to rely primarily on physical controls to crew their mech. With a full subjectivity sync installed, pilots in  

their chassis perceive the mech to be their own body, and can control it with no input lag. Dissociation  
remains a concern, however, and SSC engineers do not recommend extended periods of sync without  

proper desync and cooldown.   

Your mech gains +2 evasion. You control the mech with no separation between your subjectivity  
and your input; a second set of physical controls are built in to a retractable panel. 
 

GHOSTWEAVE  

A scaling up of the same systems found in SSC’s Mythimna panoply, Ghostweave is the name of a  
proprietary applique that licensed pilots use to better camouflage their mechs to any environment.   

Your mech is invisible during your turn (from the start until the end of your turn). If you do nothing  
on your turn except move, hide, or boost (no other actions), keep this invisibility until the start of  
your next turn. It breaks if you take a reaction.
 

INTEGRATED NERVEWEAVE  

Like the pilot-tier system, integrated nerveweave relies on dual technologies to grant a pilot total battlefield  
alacrity. Mech-tier integrated nerveweave assures a pilot will never be left behind.   

Your mech gains +2 speed when boosting.
 

KAI BIOPLATING  
Adapted from SSC home system-local fauna, Kai Bioplating adds a lamellar layer of insulated, anchored,  

chitinous plating over key brush-points on a mech. Essentially a cheaper, feasible version of living metal,  
bioplating guards sensitive systems from minor impacts that would otherwise lead to maintenance during  

downtime.   

You gain +1 accuracy on all agility checks
 

NEURO-LINKED TARGETING  

To further shrink the information gap between pilots and the machines the crew, SSC developed a stable,  
non-invasive, limited-transfer ontologic bridging system that all pilots of sufficient license could use. Neuro- 
linked targeting is a common “ability” employed by pilots who use this system, a simple protocol that  

brings them closer to feeling rather than thinking -- a more natural expression of pilot ability.     

                                                                                                                  


All ranged weapons your mech mounts gain +3 range.
 

SSC ALL-THEATER MOVEMENT SUITE  

A popular SSC modification, the AT-MS adds a stock system of short-cycle impulse drives that dramatically  
improve a chassis’ mobility.   

Your mech can fly when it moves or boosts. Generate 1 heat at the end of any turn it flies.
 

                                                                                                                     
\subsection{SSC Black Witch}

                                                               
                                            SSC BLACK WITCH  

The BLACK WITCH is the primary designate model in SSC’s newest line of mech cores meant to compete  

with HORUS’s dominance in the field of invasion/control cores. The BLACK WITCH is open to all pilots with  
the necessary SSC licensing and should experience greater overall use, as current SSC licenses outnumber  
the hypothetical maximum of HORUS licenses issued.   

The BLACK WITCH is built to withstand the stresses of combat system invasion and magnetic weaponry: it  
is a primary platform for engagements where the use of kinetic, ferrous projectiles and ordinance is  

expected. Developed primarily as a salvage and scrap repair system, the SSC-BW’s mag field system was  
soon repurposed by the SSC Gendarme as a personal defense system    

                                                                                                                       


                                                  License:
 
I. Ferrous Lash, Mag Cannon
 
II. BLACK WITCH FRAME, ICE-OUT Drone, Mag Deployer
 
III. Black ICE module, Mag Shield
 

                                             BLACK WITCH 

 HP: 6          Evasion: 10                          Speed: 5           Heat Cap: 6        Sensors: 15 

 Armor: 1       E-Defense: 12                        Size: 1            Repair Cap: 3      Tech Attack:  
                                                                                           +1 

                                                  TRAITS: 

 Repulsor field: The Black witch is resistant to kinetic damage
 
 Mag parry: 1/round you can attempt to parry any attack that deals kinetic damage against you or an  
 adjacent ally as a reaction. Roll a d6. On a 5+, the attack is negated and automatically misses. 

                                            SYSTEM POINTS: 8 

                                                 MOUNTS: 

 Aux/Aux                                             Main Mount 

                                               CORE system 

                                                                                                           


                                                     Mag Projector   

 A magnetic field generator takes the same technology as other projected magnetic defenses and makes  
  them portable separate from a mech core. When activated, the mag field generator creates a projected  
 magnetic bubble that traps all incoming ferrous projectiles; the strength of the field is so great that it can  
 even draw mechs to its center. When the field is canceled or the solid-state battery burns out (by  
 design), the field detonates through sudden catastrophic reversal, launching all captured projectiles out  
 from its center.   

 Active (requires 1 core power): Mag Field  
 As a quick action, you may activate the mag field to create a Blast 4 area in any area with at least one  
  square adjacent to you. Inside, ranged weapon attacks that deal kinetic or explosive damage cannot  
  penetrate into or out of the field and will stop at the edge, doing no damage (keep track of them). The  
 field is difficult terrain for all mechs and vehicles made at least partly of metal. Actors at least partly  
  made of metal that start their turn in the Mag Field or enter it for the first time on their turns must make  
  a successful Engineering check with 1 difficulty or be pulled to the center as far as possible and  
  immobilized. They can repeat this check at the start of their subsequent turns while trapped this way  
  and can move normally on a success, otherwise they remain trapped. 
 
 The field lasts until the end of your next turn. At the end of your next turn, any kinetic or explosive  
 weapons fired into this field will resume trajectory towards the center of this zone. The GM performs a  
  single attack roll vs each target still inside the zone with +1 targeting per attack fired into this zone  
  (cumulative, up to a max of +6). Successful hits deal 1d6 Kinetic damage per attack fired into this zone  
  (cumulative, to a maximum of 6d6). Then, the zone deactivates. 

Mag Cannon  

The SSC Magnetic Cannon is a first in Smith-Shimano’s ENERGY line: an aperture-focused magnetic  
projection beam that disrupts and damages hardware using intense pulses of magnetic force. Cores caught  
in the beam of a mag cannon suffer additional damage to their software, as even hardened components  

come under massive systemic stress.   

Main Cannon
 
1 heat (self)
 
Line 8
 
1d3 energy damage +1 heat
 
All targets caught in the area of this weapon must pass a systems check or become impaired  
until the end of their next turn.
 

Ferrous Lash  

Initially developed as a non lethal crowd suppression device, the Ferrous Lash is a far more complex and  
dangerous device in the right pilot’s hands. Fired from a series of integrated launchers, the FL system  
detonates payloads of fast-congeal ferrofluids that restrain their targets; tuned to the correct frequency,  

these proprietary SSC ferrofluid blends form into rudimentary ambulatory segments, pulling their hosts  
back towards the casting unit.   

2 SP  

                                                                                                                          


Quick Action  
A target of your choice in range 10 must pass an agility check with 1 difficulty. On a failure, it is  
knocked back 5 in a direction of your choice. This movement must obey obstructions, terrain,  
etc, but doesn't provoke reactions and ignores engagement. If it collides with an obstacle or  
another mech, it is additionally knocked prone.
 

ICEOUT drone  

SSC’s ICEOUT module is a response to the increasing reliance on system-based scans to ensure accurate  

targeting. By blanketing a core’s systems in layers of digital defilade, mirroring, spoofing, and redirection,  
an ICEOUT module can effectively disappear/disincorporate/legion its user from hostile scans. Note that  
this module only makes its user system-invisible; they will still be visible through optics.    

2 SP, Limited (2)  
Drone, quick action  

You fire an ICEOUT drone at a point within range 10 of you, where it hovers in place. The drone is  
invisible. Once fired, the drone creates a burst 2 zone around itself. Any target at least partially  
covered by the zone, allied or enemy, is immune to all tech actions (even beneficial ones), and  
cannot make or benefit from any tech actions. Any negative statuses caused by tech actions  
immediately end. Targets inside the zone don’t show up on any electronic sensors and are only  
visible to the naked eye or optics. The drone deactivates at the end of the current scene or when  
destroyed, and cannot be re-used. You can move it again to a point in your sensor range as a  
quick action.
 

Mag Deployer  
SSC’s own take on flash-printing is advanced enough to embed magtech burnout cells into raw  
prefab clay. SSC non-mag pilots often disparage Black Witch pilots for “throwing plates” at the  
enemy, but the tactical advantage they provide cannot be denied.   

2 SP  

Quick action.  
You flash-print a heavy metal plate that takes up a 2x2 free space in range 5 of you. It is flat and  
doesn’t obstruct movement. You can set the system to one of two settings when you create it:
 
         Repulse: Any hostile target that enters the space must pass a hull check or be pushed in  
         a direction of your choice 3 spaces. If this causes them to collide with an obstruction  
         (terrain, a mech, etc) it is additionally knocked prone. An allied target that enters the  
         space can fly 3 in any direction as a free action.
 
         Attract: Any target, allied or enemy, that enters the space, must pass a hull check or  
         become immobilized. It can end this status by taking a quick action and repeating this  
         check successfully to free itself.
 
The deployer can be attacked - it has evasion 5, 20 hp, and 2 armor, and it lasts until the end of  
the current challenge or around an hour outside. You can only deploy one at at time. If you create  
a new deployer, the old one disintegrates and is destroyed.
 

Black Ice module
 

                                                                                                                    


3 SP, Unique  
Hostile tech actions or system attacks against your mech or any adjacent ally are made at +1  
Difficulty. Successive attacks in the same combat from any target are made with an additional +1  
Difficulty (cumulative). This difficulty has a maximum of +4, and resets when it would hit +5 back  
to +1 as its definitions roll over.
 

Mag Shield  

SSC’s magnetic shield takes the same technology as their proprietary magnetic buckler and applies it to a  

massive deployable system.  

2 SP, Unique  

Shield, quick action
 
As a quick action, this system creates a line 4 force field 4 spaces high with at least 1 square in  
an adjacent space to you. Any adjacent mech can use this force field for heavy cover from  
attacks on the other side. It additionally gains resistance to kinetic and explosive damage from  
attacks on the other side of this field, but conversely, any of its targets on the other side of the  
forcefield gain resistance to kinetic and explosive damage from its attacks. The shield lasts until  
the end of the current scene, but only 1 shield can be placed at a time.
 

                                                                                                                      
\subsection{SSC Death's Head}

                                         SSC DEATH’S HEAD  

The DEATH’S HEAD is Smith-Shimano’s answer to all other long range, low splash artillery mechs. By  
sacrificing hull strength for stability and alacrity, the DEATH’S HEAD manages to avoid incoming fire while  

holding a near-perfect lock through advanced maneuvers.   

                                                    License:
 
I. Hi Stress Mag Clamps, Tracking Drone
 
II. DEATH’S HEAD FRAME, Core Siphon, Vulture DMR
 
III. Kinetic Compensator, Railgun
 

                                               DEATH’S HEAD 

  HP: 8           Evasion: 10                           Speed: 5            Heat Cap: 6        Sensors: 10 

  Armor: 0        E-Defense: 8                          Size: 1             Repair Cap: 2      Tech Attack:  
                                                                                               +0 

                                                     TRAITS: 

  Neuro-linked: The Death’s Head can re-roll the very first ranged attack it makes per round. It must keep 
  the second result. 
  Perfected Targeting: The Death’s Head gets a bonus +1 to all ranged attacks (a flat +1 to the attack 
  roll) 

                                              SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Main/Aux Mount                     Heavy Mount 

                                                  CORE system 

                                                                                                               


                                                 Precognitive Targeting  
  Precognition is the next step in human/AI interaction. By allowing AI data-dump and REM learning via a  
  neural bridge, a pilot can learn to read situations before they begin to develop. The nature of  
  precognition is as-yet unknown, so SSC recommends limited, monitored use of this protocol.   

  Active (requires 1 core power): Activate Neural Shunt  
   For the rest of this scene, you can take the following action:  

  Mark for Death 
  Full Action 
   Choose a target in range 30 but further away from range 5 of the Death’s Head. You concentrate on that 
  target. While concentrating, your mech cannot move or take reactions. You can stop concentrating at 
  the end of any of your turns as a free action, and can only concentrate on one target at once. 
  While concentrating on a target, as long as that target is not in cover from you or within range 5 of you, 
  your ranged attacks against the target deal +4d6 bonus damage on Critical Hit. 

Hi-stress Mag Clamps  
A simple, reliable system. When installed, it seeds toggleable electromagnets into the locomotive systems  
of a chassis. When turned on, the mag clamps allow a chassis to cling to ferrous surfaces. Of especial use  
in micro and null gravity environments.  

1 SP, Unique  
Your mech treats all vertical and overhanging surfaces as flat ground for the purposes of  
movement. You no longer count as climbing on these surfaces and can move, stand, and run at  
full speed, though if you are knocked prone you fall.
 

Tracking Drone  

A modified version of a tracer round, a tracking drone must hit its target in order to activate. Once a  
successful hit is registered, a tracking drone will feed live, surreptitious data back to its shooter across  

multiple theaters.   

1 SP
 
Quick Tech
 
Gain the following quick tech action:
 
	        Tracking Drone: Make a tech attack against a target in your sensor range. On a hit, you  
know the target’s exact location, HP, Structure, Heat, and speed, and it cannot hide or benefit  
from invisibility from you until the drone is removed from them. It takes a quick action and a  
successful engineering check from the targeted mech to remove a tracking drone.
 

Core Siphon  

By shunting some core waste-heat from dispersal systems to weapon systems, the Death’s Head can  
overclock its weapons’ targeting, catalytic, and processing systems. This comes with a trade-off, however,  

as reliance on overclocking without sufficient cooling can damage systems not built to handle the influx of  
power.   

                                                                                                                        


2 SP  
Unique  
At the beginning of your turn, you can choose to give the first attack roll of your turn +1  
Accuracy. If you do, however, any additional attack rolls until the end of your turn gain +1  
difficulty
 

Vulture DMR  

The SSC VULTURE-BR is Smith-Shimano’s core line battle rifle, chambered for 12.7x108mm HTI rounds.  

Field performance reports of the VULTURE report low TTK rates and satisfactory all-theater capability,  
though some pilots have reported fouled-fire incidents as a result of the high burst rate.   

Main Rifle
 
2 heat (self)
 
Overcharged, Accurate
 
Range 15, 1d6+1 damage
 

Kinetic Compensator
 
Another common modification, a system of electronically modulated gyroscopes and hydraulic  
compensators work in concert to absorb and disperse recoil caused by firing heavy weaponry.   

2 SP, Unique
 
When you miss with any ranged weapon attack roll, your very next ranged attack roll gains +1  
Accuracy.
 

Railgun  
A railgun is a simple, elegant weapon. With no moving parts and a magnetically-accelerated  
projectile, a railgun can be used at peak efficacy in any combat theater and is entirely self- 
contained in a disposable unit. However, power draw is massive, and it is necessary for mechs  
mounting a railgun to be fitted with a core-charged auxiliary power pack.   
   
Heavy Rifle
 
AP, Ordnance
 
Line 20
 
1d6+4 kinetic damage
 

                                                                                                                  
\subsection{SSC Dusk Wing}

                                           SSC DUSK WING  

The SSC DUSK WING is built from a legacy-inspired modification package to hazardous/hardened EVA  
suits; in the early days of deep space exploration, there was a need for mechanized exoskeletons that  

provided not only amplified capacity, but plated kinetic defense. The DUSK WING is the spiritual heir of  
those early deep space suits. Fast and small, the DUSK WING mounts a complement of all-theater  

maneuverability jets that allow for perfect (or near-perfect) flight.    

                                                    License:
 
I. Veil Rifle, SSC neurospike Mk1
 
II. DUSK WING FRAME, Burst Launcher, Flicker Field
 
III. StunCrown, OASIS
 

                                                 DUSK WING 

  HP: 6           Evasion: 12                           Speed: 7            Heat Cap: 5        Sensors: 10 

  Armor: 0        E-Defense: 8                          Size: 1/2           Repair Cap: 2      Tech Attack:  
                                                                                               +1 

                                                     TRAITS: 

  Integrated Hover Flight: The Dusk Wing can hover when it moves or boosts (it can fly, doesn’t need to  
  move, it can move without going in a straight line, and doesn’t need to land). While flying, it generates 1  
  heat at the end of its turn.
 
  Harlequin Cloak: The Dusk wing is invisible during its turn. It re-appears at the end of its turn.
 
  Fragile: This mech has +1 Difficulty on Hull Checks 

                                              SYSTEM POINTS: 6 

                                                    MOUNTS: 

  Aux/Aux Mount                      Flex Mount 

                                                  CORE system 

                                                                                                               


                                                  Hall of Mirrors 
  Active (requires 1 core power): For the rest of the scene, gain the following quick action: 
  Hall of Mirrors 
  Each time your mech takes the boost action or its regular move on its turn, it leaves a holographic 
  imprint of itself behind in the space where it started. This hologram is an illusory projected object the 
  same size as your mech (it can be moved through and doesn’t actually take up any space). The 
  holograms detonate if any non-allied actor moves through or adjacent to their space, dealing 1d6 
  energy damage (an actor can pass an agility check to halve this damage). In addition, any time as a 
  quick action, you can instantly teleport to one of the hologram’s locations. Doing so detonates all 
  holograms for a burst 1 attack centered on their areas for the same effect and prevents you from 
  generating new holograms until the start of your next turn. 

Veil Rifle  
Main Rifle  
Line 10
 
1d3 energy damage
 
Allies caught in the area of this rifle do not take damage but are instead are covered in  
coruscating energy that throws off targeting systems and count as in light cover until the start of  
your next turn.
 

SSC Neurospike Mk1  
Building off SSC’s strain of dormant DHIYED viral code, the Neurospike Mk1 was the first all-theater, single- 
use spike system developed by the Exotic Materials group. N-Mk1 comes pre-packaged with a basic, but  
effective, activated DHIYED virus: when fired or otherwise implanted in a synthetic target, it pumps a  
cocktail of DHIYED virus into the codebase, altering crew outputs and onboard systems’ battlefield  
perception.    

2 SP, Unique
 
Quick Tech
 
Gain the following options for invasion:
 
         Shrike Code: Until the end of your next turn, each time your target makes an attack roll,  
         it first takes 2 heat.
 
         Mirage: Choose yourself or a friendly mech you can see. Your target’s systems relay  
         blurred, illusory images of that mech over its real image that confuse your target’s  
         systems. That friendly mech (or your mech) counts as invisible to your target until the end  
         of your next turn.
 

Burst Launcher  

Typically dorsally mounted, Burst Launchers fire rapid streams of explosive cores. These thermal spheres  

are tuned for an airburst detonation, overwhelming the target zone with rippling chain explosions that  
damage and suppress units in the area.   

Main Launcher
 
Arcing
 
Range 10
 

                                                                                                                


1d3 explosive damage
 
On a Critical Hit, a target struck by this weapon is impaired until the start of your next turn.
 

StunCrown
 

The SSC StunCrown is a simple system, a ring of WHITEOUT flash lamps in hardened mounts that can be  
triggered to fire an overwhelming burst of light. The StunCrown is usually mounted on a short post or in a  

ring around a mech’s cranial suite; due to the intense energies running through the flash bulbs, this system  
only has a limited number of uses before the lights burn out.   

2 SP, Limited (2)  
Quick action  

All hostile targets in a burst 5 area centered on your mech that can see your mech must pass an  
agility check or become Jammed, and a systems check or become Impaired. Both effects last  
until the end of your next turn. Mechs in cover from you when this system is activated are not  
affected. 
 

Flicker Field  

Flicker Fields are generated by holochaff, a blend of photoreactive slivers, mirrorchips, LEDs, and strips of  
flare-out. Fired from launchers at a pilot’s command, holochaff looks at first like a cloud of smoke: within  

moments it adapts to its surroundings and begins to project out a shattered, shifting image of the terrain  
around it, creating a distorted field that confounds both visual and systemic targeting.     

1 SP, Unique
 
When you move or boost, you project a holographic pattern around your mech that leaves  
dazzling afterimages, making it hard to discern your mech’s location. After moving or boosting  
you count as having invisibility against the very next attack roll against you. The field disperses  
after this attack, hit or miss. You can only gain the effect of this field once (you can’t ‘stack’ up  
several instances of it).
 

OASIS  

2 SP, Unique
 
Protocol
 
2 heat (self)
 
Until the start of your next turn when you move or boost you can move only in straight lines, but  
create a holographic trail behind your mech as you move. The trail lingers until the start of your  
next turn, creating a light construct 1 space high and the same length as your movement. It can  
be used for light cover by adjacent allies, and any allies that benefit from this cover also have  
resistance to energy damage.
 

                                                                                                                      

\subsection{SSC Metalmark}
                                                                                                                          
                                             SSC METALMARK  

The METALMARK is SCC’s backbone-class line mech, fully equipped with SSC’s proprietary design and  
engineering hallmarks to ensure that it is just as survivable as it is agile. The METALMARK base model  
reflects SSC’s deep-space and long patrol heritage in its aquiline design, sturdy construction, and multiple  

redundant systems. All METALMARK models come standard with a SMITH CUSTOM LEATHER gimbaled  
pilot seat to ensure comfort on long distance ranging expeditions.   

                                                                                                                     


                                                     License:  
 I. Flash Grenade, Reactive Weave
 
 II. METALMARK FRAME, Shock Wreath, Rail Rifle
 
 III. Active Camo, Shock Knife
 

                                                METALMARK 

  HP: 8          Evasion: 9                             Speed: 5            Heat Cap: 5         Sensors: 10 

 Armor: 1        E-Defense: 8                           Size: 1             Repair Cap: 4       Tech Attack:  
                                                                                                +0 

                                                     TRAITS: 

  Flash Cloak: The metalmark is invisible while moving (regular move, boosting, moves from talents, etc),  
  but reappears after it finishes its movement.
 
  Carapace Adaptation: When the METALMARK would benefit from light cover, it instead benefits from  
  heavy cover 

                                              SYSTEM POINTS: 5 

                                                    MOUNTS: 

 Aux/Aux                             Main                                   Heavy Mount 

                                                 CORE system 

                                                 Tactical Cloak  

 A tight-knit, tight-bind weave of reactive fabric, tactical cloaks are high-license tech, restricted to pilots  
  of METALMARK classification II or higher. The weave covers roughly 80% of a chassis, giving it an  
  overall dull quality when viewed through optics or with the naked eye. It is difficult to target, and when  
 activated it bends light in such a way that makes it nearly impossible to see.   

 Active (Requires 1 core power):  
  Cloaking Protocol
 
  Protocol
 
  Until the end of the current challenge, or when you deactivate this module at the start of your turn, you  
  become invisible. If you take damage, you lose the benefit of this module until the start of your next  
  turn. No other action will deactivate it. 

Reactive Weave  

A woven CSAJ (Critical Systems And Joints) cover, Reactive Weave not only protects sensitive systems and  
joints from fouling and poor weather, but provides a surface for SSC engineers to apply their unique  
loomware technology. This weave is powered, capable of free-flexing to augment a mech’s mobility and  

reduce the stress placed on a chassis’ joints.   

                                                                                                                


1 SP, Unique  
When you brace, your mech can immediately move its speed as a reaction and it also gains  
invisibility until the end of its next turn.
 

Flash Grenade  
2 SP, Limited (2)
 
Grenade
 

This grenade can be thrown to a space in range 5. When this grenade explodes, it creates a  
burst 2 zone that lasts until the end of your next turn. Actors other than you (allied or enemy)  
caught inside can’t trace line of sight out of the zone (they can attack other targets inside  
normally), and actors inside the zone benefit from light cover.
 

Shock Wreath  

An after-fabrication modification popular among melee-oriented pilots, the Shock Wreath applies an  

integrated bundle of conductive filaments to the blade, point, tip, or surface of a close combat weapon.  
Paired with a power source (typically in the hilt or half of a weapon, but sometimes external), the Shock  
Wreath adds a thermal element to the kinetic, and a distinct visual marker: their weapons are picked out in  

fine lines of white-hot light, shrouded in heat shimmer.     
2 SP  
Mod  
Choose 1 melee weapon. It gains Burn depending on its size (Aux: Burn 1, Main: Burn 2, Heavy  
or larger: Burn 3). If it already has Burn, this increases the burn it deals by the same amount.
 

Rail Rifle  

A rail rifle is a popular weapon for pilots in any theater, but the only choice for those operating in  
atmospheres made up of highly combustible gasses. Using a line of cascading electromagnets, a rail rifle  

accelerates a small projectile up to tremendous speeds, launching it without combustion or heat reactions.  
A rail weapon is kinetic and comparatively quiet when fired next to combustion weapons, though its energy  
signature is difficult to mask given the massive power requirements demanded by the weapon system.   

Main Rifle
 
1 heat (self), Line 12
 
1d6 kinetic damage
 

Active Camo  

Active camouflage represents the pinnacle of counter-optic defense systems. By interpreting incoming  
visible-light spectrum data, an active camouflage system can project a light-bending field around its user,  

effectively hiding them in plain sight.    

3 SP, Unique  

2 heat (self), Protocol
 

                                                                                                                   


You can activate or deactivate the light bending properties of this module at the start of your  
turn. It lasts until the end of your next turn. While this module is active you are invisible. If you  
take damage, this module immediately deactivates.
 

Shock Knife
 
The shock knife is a mech-sized blade made to accept and integrate the post-fabrication Shock Wreathe  

system. The knives are custom-fabricated by SSC’s Terashima artisan enclave, each one bearing its stamp.  

Auxiliary Melee
 
1 heat (self)
 
Thrown 5, Threat 1
 
1 energy damage + Burn 2
 

                                                                                                               
\subsection{SSC Monarch}

                                             SSC MONARCH   

The SSC MONARCH platform is Smith-Shimano’s solution for a fast, self-propelled missile/barrage battery.  
Able to mount ground-to-ground, ground-to-air, ground-to-space, and all-theater missile tubes and their  

guidance systems, the MONARCH can be adjusted to deliver any payload at any distance to any target.  
The MONARCH is commonly deployed in a fire-support role, though field tests of a MICROMONARCH  
mid/close range system is underway. 
 
                                                     License:
 
I. Sharanga missiles, Companion Gun
 
II. MONARCH FRAME, Stabilizer weapon mod, Gandiva Missiles
 
III. Pinaka Missiles, TLALOC class NHP
 

                                                    MONARCH 

  HP: 8           Evasion: 8                             Speed: 5            Heat Cap: 6         Sensors: 15 

  Armor: 1        E-Defense: 8                           Size: 2             Repair Cap: 3       Tech Attack:  
                                                                                                 +0 

                                                      TRAITS: 

  Avenger Silos: Once a round, when you score a Critical Hit with a weapon, a target different to your  
  first target in range 10 and line of sight takes 3 explosive damage (no roll required).
 
  Seeking payload: The monarch’s launcher attacks against targets suffering from Lock On gain the  
  seeking tag 

                                               SYSTEM POINTS: 5 

                                                     MOUNTS: 

   Flex Mount                         Main mount                             Heavy Mount 

                                                   CORE system 

                                                   Avenger silos 

  The SSC 30 High-pen missile system is a FRAME mounted micro missile system capable of tremendous 
  output in combat. The MONARCH is fitted to hold upwards of 60 of these deadly miniaturized warheads 
  at once. 

  Active (requires 1 Core Power): Divine Punishment 
   Full Action 
  You unload your Avenger Silos. All targets of your choice on the battlefield (or a burst 50 area from your 
  mech) must pass an agility check with 1 difficulty or take 1d6+3 explosive damage, and half on a suc- 
  cessful save. You do not need line of sight to any targets, and the self-guiding missiles can perfectly 
  seek any target as long as they can trace a path. Once used, you cannot benefit from the Avenger Silos  
  trait until you take a full repair. 

                                                                                                                 


Sharanga Missiles  
Main Launcher
 
Range 15
 
Arcing
 
3 explosive damage
 
When you fire this weapon, you can choose one or two targets in range and line of sight, making  
attack rolls for each.
 

Companion Gun  
2 SP, Unique
 
Once a round, whenever you score a Critical Hit against a target, this shoulder-mounted gun can  
calibrate and rapidly fires a projectile that also deals 3 explosive damage to a different target  
within range 10 and line of sight, no attack required.
 

Stabilizer weapon mod  
A stabilizer modification is a series of modifications to physical mounts and targeting software that ensures  

weapons will remain level, steady, and angled at max-optimum in order to ensure positive target  
engagement at range.   

2 SP  
Mod  
Choose 1 launcher or cannon weapon. Increase its base range by 5, but it gains the ordnance  
tag.
 

Gandiva Missiles  

Gandiva missiles are a reliable mainstay from Smith-Shimano’s EWAR line. Like the Pinaka, the Gandiva  

platform is equipped with jet-assisted mid-flight repositioning systems, allowing the Gandiva to respond to  
changing battlefield environments with a high degree of expected successful navigation to its target. Each  
Gandiva missile platform comes pre-loaded with a hivemind companion/concierge class drone AI, making  

an equipped system capable of learning from each right-of-launch experience.     

Heavy Launcher
 
Smart, Seeking, Accurate
 
1 SP
 
Range 15
 
1d6+3 energy damage
 

Pinaka Missiles  
Pinaka missiles are massive, two-stage missiles mounted along the spine of a mech core or carried  

disassembled, to be affixed and launched from a brachial mount.  Pinaka missiles are adapted from ship-to- 
ship missiles, their second stage intended to be able to re-orient in flight through jet-assisted repositioning.   

Superheavy Launcher
 
Arcing, 2 heat (self)
 

                                                                                                               


Range 30, one or two Blast 1 areas* 
 
2d6+1 explosive damage
 
When this weapon is fired, it chooses one or two Blast 1 areas within range to attack. The areas  
cannot overlap.
 

TLALOC class NHP  

TLALOC-Class NHP systems provide advanced multi-system targeting and co-pilot functions, taking over  
subroutine control to ensure persistent lock-on and engagement. With TLALOC installed and operational, a  

pilot can trust that their back is always covered and every possible advantage will be exploited.   

TLALOC clones are often stereotyped as a hasty, impetuous NHP. They are well known for having a  

superiority complex.  

3 SP, Unique
 

AI
 
Your mech gains the AI property and the TLALOC protocol
 

TLALOC protocol  
Protocol  
2 heat (self)
 
Your mech is capable of rapidly firing and re-targeting your weapons, far faster than you can  
think. When you activate this protocol, your mech is immobilized until the start of your next turn,  
but for the same duration, if you miss any weapon attack, you can immediately re-roll the attack  
as long as you target a different target in range or area of effect (if the attack was blast, line, or  
cone). You can take this re-roll only once for each attack (if the second attack misses you don’t  
get to keep making it), and a target already hit by this attack (from a re-roll or otherwise) cannot  
be targeted again.
 

                                                                                                                     


                                                                                                                            

                                                                                                                      
\subsection{SSC Mourning Cloak}

                                    SSC MOURNING CLOAK  

The SSC MOURNING CLOAK core is intended to provide pilots with a closer-than-CQB tactical option for  
situations where firearms and ordnance weapons are impractical or unavailable. The MOURNING CLOAK  

line specializes in precision melee combat and is commonly outfitted with a complement of variable  
weaponry; shielded microfilament wires designed to attack vulnerable joints and external modules. 
 

                                                  License:
 
I. Variable Knife, Vijaya Rockets
 
II. Mourning Cloak FRAME, Exposed Singularity, Hunter Logic
 
III. Variable Sword, FADE Cloak
 

                                           MOURNING CLOAK 

  HP: 8          Evasion: 12                          Speed: 5           Heat Cap: 4        Sensors: 10 

  Armor: 0       E-Defense: 6                         Size: 1            Repair Cap: 3      Tech Attack:  
                                                                                            +1 

                                                   TRAITS: 

  Hunter: The Mourning Cloak’s melee attacks become AP and deal +1d6 bonus damage if it is the only  
  actor (allied or enemy) in engagement with the target
 
  Bioplating: The Mourning Cloak gets +1 accuracy on agility checks 

                                             SYSTEM POINTS: 6 

                                                  MOUNTS: 

  Main/Aux                                             Flex Mount 

                                                CORE system 

                                                                                                           


                                     Smith-Shimano EX Slipstream Module  
   The EX SLIPSTREAM program is a Smith-Shimano innovation open only to highly licensed pilots. An  
  interesting development in personal travel, the EX SLIPSTREAM module itself is a miniaturized near- 
  lightspeed star drive capable of transporting the user through blinkspace with acceptable accuracy. The  
  program and its technology is temperamental; a mech core is the smallest unit capable of surviving the  
  stress of exposed blink travel, though the experience is still traumatic to the user and those in close  
  proximity to egress.    

   Passive:  
  This dangerous and experimental module is a miniaturized starship nearlight drive. You can use it  
   instead of moving or taking the boost action. When you use it, roll 3d6. You can teleport to a point  
  within that range around you as long as there is space for your mech. You don’t have to be able to see  
  this point, but if you attempt to teleport to an already occupied space (by terrain, another mech, etc),  
  the teleport fails and you take 2d6 kinetic damage.
 

   If you roll triples for this system, your mech disappears and does not re-appear, either indefinitely or  
   until your party rests (up to you).
 

  Active: Requires 1 core power  
  Stabilize singularity
 
   Protocol
 
   Until the end of this scene, when you move or boost, you instead teleport up to the same distance. 

Vijaya Rockets  
Vijaya rockets are miniaturized, close range missiles fired from a portable, drum-fed launcher. Their shaped  

charges are formed in such a way as to project their blast forward, away from the user, and are intended for  
use in close range engagements as a force multiplier.   

Auxiliary Launcher
 
Range 5
 
Accurate
 
1d3 explosive damage
 

Variable Knife  

A variable knife is a shorter version of a variable sword, a shielded length of mono-molecular wire. The  

power drain on a mech’s systems makes mounting these weapons incredible taxing.  

Auxiliary Melee
 
Accurate
 
Threat 1
 
2 kinetic damage
 
The Variable knife deals +1d3 bonus damage on critical hits  

Exposed Singularity  

                                                                                                                   


SSC’s Exotic Materials project worked to develop the Mourning Cloak’s unique gravatic power plant. For the  
second generation of the SSC-MC, the Exotic Materials project devised a system that allows pilots to  
aperture open, for a moment, the gravatic containment system, exposing a slice of naked singularity to  
realspace.   

Naked singularity is difficult for organics and synthetics to perceive, being similar to the core of a black hole.  
The sudden exposure directed at foes (or other targets) essentially “blanks” the Mourning Cloak from real  
time. The Cloak’s pilot, meanwhile, experiences roughly 10 seconds of normal subjective time, allowing  
them a brief window in which they can act independently of local realtime.   

SSC does not recommend abusing this system, as the Exotic Materials group is still testing long-term  
exposure to local sidereal time.  

2 SP, Unique
 
Reaction
 
Once per round, when your mech takes damage, you can immediately teleport up to 1d6 spaces  
as a reaction in a direction of your choosing (though if this teleport would put you inside an  
obstacle or other mech you take damage as normal and the teleport fails).
 

Hunter Logic  
Building from interpreted strands of DHIYED-strain viral code, SSC’s Hunter Logic is an agile computational  
memetic, a dual synthetic/VLS-vector systemic weapon capable of crippling a target’s computer and crew.  

2 SP
 

Quick Tech  
Gain the following options for invasion:  
         - Stalk Prey: Your systems infect the target with a viral logic that wipes your image from  
their sensors. Until you are damaged by that target, they count you as invisible. This system can  
only affect one target at a time (other targets still count you as visible and can see you normally).
 
	        - Terrify: Your systems infect the target with a viral logic that causes your mech to appear  
horrifying to the target. Until the end of its next turn, your target is impaired and also cannot  
willingly make any movement that would take it closer to you.
 

Variable Sword  

The variable sword is a Smith-Shimano hallmark. A length of razor sharp molecular wire attached to a  
handle and caught in a magnetic field, a variable sword is invisible to the naked eye until it makes cuts in an  
enemy. Built in the early days of interstellar travel, the variable sword was meant to allow for precision  

sample gathering in the field, while also reducing the overall payload on a mech core.   

Main melee
 
Accurate
 
Threat 2
 
3 kinetic damage.
 
The Variable Sword deals +1d6 bonus kinetic damage on critical hits
 

FADE Cloak  

                                                                                                                


Representing SSC’s first successful manipulation of what the Aun call the “Firmament”, each Firmament  
Affinity/Directed Entropy Drive must be fabricated to the unique firmament signatures of the pilot cleared to  
requisition it. FADE drives are rough tools, artificial affinity generators that allow operators to “shimmer”, to  

nudge their physical bodies between the causal and paracausal. The drive extrudes a semi-organic  
membrane that accomplishes this effect, wrapping around the mech.  

At present, the long-term effects of this system on organic matter is unknown; pilots who are cleared to  
operate this system agree to check in with their SSC personal concierge on a regular schedule (“check in”  
includes regular deposits of genetic material).  

2 SP  
Quick Action, Unique  
Once this highly experimental drive is activated as an action, it shifts its user partially in and out  
of blinkspace. When activated, you immediately go out of phase with reality. While out of phase,  
you can ignore obstructions such as walls or cover and pass through enemy mechs and solid  
obstacles as if they were not there, but not end your turn there. You cannot interact with the  
physical world, but neither can it affect you (in terms of damage, etc). If for any reason you are  
forced to return while inside of another object, take 2d6 AP kinetic damage and return in the  
nearest available space. 
 

At the start of each of your turns while this system is active, roll a d6. On a 4+, you go or remain  
out of phase, on a 3 or lower, you return to the battlefield until the start of your next turn. This  
drive can’t be activated again if it’s already active. It deactivates if you make an overheating  
check, deactivate as a quick action, or the scene ends.
 

                                                                                                             
\subsection{SSC Swallowtail}

                                                           
                                          SSC SWALLOWTAIL  

The SWALLOWTAIL platform is Smith-Shimano’s primary long range/long term scouting platform,  
built for rapid and sustained ranging across hostile, volatile environments.   

                                                     License:
 

                                                                                                                


I. Markerlight, Scout Drone Nexus
 
II. SWALLOWTAIL FRAME,  Oracle light machine gun, Low Profile
 
III. ATHENA-class NHP, Cloaking Field
 

                                                SWALLOWTAIL 

  HP: 6           Evasion: 10                            Speed: 6            Heat Cap: 6         Sensors: 20 

  Armor: 0        E-Defense: 10                          Size: 1             Repair Cap: 3       Tech Attack:  
                                                                                                 +1 

                                                      TRAITS: 

  Integrated Cloak: If the Swallowtail doesn’t move during its turn, it becomes invisible at the end of its  
  turn. This invisibility immediately breaks if it moves, attacks, takes a reaction, or starts its next turn.
 
  Prophetic Scanners: Targets suffering from Lock On from the swallowtail are also Shredded 

                                               SYSTEM POINTS: 6 

                                                     MOUNTS: 

  Aux/Aux                                                 Flex Mount 

                                                   CORE system 

                                          Cloudscout TACSIM Swarms  

  Cloudscout TACSIM Swarms are packets of networked microsensors, launched in nonlethal mortar  
  canisters that detonate high above the battlefield. Once seeded in such a way, the TACSIM program the  
  cloudscouts create begin to run brevity cycles: tight, contained simulations of tactical possibility.  
  Probability results are then fed to the pilot’s NHP, who in turn feeds it to the pilot and their networked  
  squad members, ensuring high-probability successful outcomes.       

  Active (Requires 1 core power): Prophetic Interjection  
  Until the end of the current challenge, once per round, as a reaction when an allied target you can see  
  is damaged by another target you can see, you can make a systems check. On success, the attack  
  hitting was actually a simulation that your mech predicted. Your ally gains resistance to all the damage  
  from that attack, and your ally can move 3 in any direction to where they ‘actually’ were. This  
  movement does not provoke reactions and ignores engagement. 

Scout Drone Nexus  
The scout drone is a small, active-camouflaged mini-drone launched from a mounted LOTUS projector.  

The LOTUS projector fires scout drones at subsonic speeds in bursts of ten, blanketing a wide area with  
the single-use drones in order to relay information about terrain and targets within.    

2 SP
 
Drone, Quick Action
 

                                                                                                                 


Sensor Range
 
When you use this system, you can deploy your drone to an area in sensor range and line of  
sight. The drone then emits a burst 2 area around it that grants the following benefits:
 
  - Gain perfect vision of that area
 
  - Hostile targets that end their turn in the area immediately lose invisibility or hiding.
 
  - Reveal current HP, Evasion, E-defense, and heat levels of targets in that area
 
The drone can be attacked and targeted as normal, but it is also permanently invisible. It can be  
recalled or redeployed by taking this action again.
 

Markerlight  
Main Rifle
 
1 SP
 
Range 20
 

This weapon deals no damage and cannot deal damage (from talents or otherwise) or take  
weapon mods, but on hit, it inflicts Lock On on your target at the end of your turn.
 

ORACLE Light machine gun  
Auxiliary Rifle
 
1 SP, Arcing, Accurate
 
Range 15
 
1d3 kinetic damage
 

Low Profile  

A hallmark of a well thought out mech platform is the ability for pilots to work with their technicians to  

adapt their stock model to the specifications of the environments they operate in. Lowering a mech’s profile  
removes extraneous protrusions, tunes any broadcast software, and masks heat signatures — all an effort  
to reduce optical and scanner signatures.   

1 SP, Unique  
Protocol  
Your mech can retract its major systems to reduce its profile. You can activate this protocol at  
the start of your turn. While active:
 
     -   Rolls to find your mech while hidden are made at +1 Difficulty
 
     -   All ranged and tech attacks against you are made at +1 Difficulty
 
     -   Your mech is Slowed and cannot make ranged, melee, or tech attacks
 

ATHENA-class NHP  

Smith-Shimano’s ATHENA is the pinnacle of total hyperspectral environmental facsimile. Through a  

combination of unfettered Omninet access, hyperspectral relays fired out from a Cloudscout TACSIM  
projector, sub-networked squadmates, and active/hostile intrusion protocols, ATHENA bootstraps a near- 
flawless reconstruction of the immediate environment around its host core. ATHENA is unparalleled in its  

processing power, and with this reconstructed environment it can provide trustworthy, accurate advising to  
pilots in need of strategic counsel.   
ATHENA clones tend to be patient, cautious, and measured in their relations with their pilots.  

                                                                                                               


   
3 SP, Unique
 
AI  

Your mech gains the AI property and gains the ATHENA protocol:
 

         ATHENA protocol  
          Quick Action
 
          Choose a blast 3 area within 1 mile of you. Your AI constructs a perfect, real-time, 3d  
          model of this are that you can rotate and interact with, including actors that move in and  
          out of that area, and extreme detail. You can re-target or move this area by taking this  
          quick action again. It lasts until the end of the current scene (or about 10 minutes in  
          narrative time).
 

         Your mech gains perfect vision of this area and can relay this to allies, letting any attacks  
         from yourself or allies in the area ignore cover. Hostile targets that end their turn in this  
          area lose invisibility or hiding, and you can see the current heat and HP levels of all  
         targets in the area.
 

Cloaking Field  

SSC’s milspec cloaking field is the result of extensive experimentation in cooling and light-reflecting  
technology. Born from a need to bounce harmful radiation away from ships and EVA modules in deep  

space, the SSC-MILSPEC LIGHTBEND/OVERCLOAK is a system often equipped by ranger and long-patrol  
scout pilots to ensure not only radiation protection, but optical concealment as well. The light and  
radiation-bending properties of the LB/OC conceals anything inside of its projected bubble from sensor  

suites and optical spotting.   

4 SP  

2 heat (self)  
Quick Action
 
You can activate or deactivate the light bending properties of this module as a quick action. It  
lasts until the end your next turn. When you activate this module, your mech and all allied targets  
within a burst 3 area centered on you become invisible while they remain in the area. This area  
moves when you move, and remains centered on you. If you become stunned, shut down, or  
take damage, this module immediately becomes inactive.
 

                                                                                                                        
