\section{Special Classes}
      SPECIAL CLASSES  

The following NPC classes describe special cases, NPCs that are a little more unique or can’t be  
described as a mech.
 
\subsection{Human}
                                                HUMAN  
This entry describes humans or human-scale enemies, such as pilots in the world of lancer. The  
entry is intentionally pretty simple.
 

To make a human enemy:
 
            -   Pick a statistic block from the table below that basically describes the enemy. 
 
            -   Pick a weapon for your enemy if they’re armed, and describe any other gear they  
                have
 
            -   All human enemies are size 1/2 and roll attacks and checks at +2/per tier
 
            -   You can use the Heavily Armored, Elite, and Legend modifiers below to make  
                enemies tougher
 

                                           Starting templates  

 Name                        HP         Evasion/E-defense            Armor                   Speed 

 Civilian                    1          8/8                          0                       3 

 Untrained martial           3          9/9                          0                       3 
 human (gangster, thug,  
 warrior, etc) 

 Martial human (pilot,       5          10/10                        0                       4 
 soldier, guard, etc) 

 Subaltern frame             8          10/8                         1                       4 

 Armored human (pilot        5          8/8                          1                       4 
 in a hard suit, etc) 

 Heavily armored             -          -2 to both                   +1                      -1 

 Elite (apply to any)        +2/tier    +1/tier to both              -                       +1 

 Legend (apply to any)       +3/tier    +2/tier to both              +1                      +2 

                                                Weapons  

 Name                        Tags                          Range                    Damage 

 Assault Weapon               -                            5                        2 

 Melee weapon                 -                            Threat                   2 

                                                                                                         


 Sidearm                      -                             2                       1 

 Heavy Weapon                 Ordnance, Loading             8, Blast 1              4 

Damage: Weapons can be kinetic, energy, or explosive depending on their function
 
Type: All weapons have the pilot type
 
Tags: AP (weapon gets -1 damage, to minimum of 1), Smart, Seeking, Arcing, Ordnance,  
Loading (weapon gets +2 damage), Limited, Accurate (weapon gets -1 damage, to a minimum of  
1), Inaccurate (weapon gets +1 damage)
 

A weapon shouldn’t go above 5 damage after tags.
 

                                            Example enemies:  
These are just a few examples! Feel free to make your own
 

 Name                     Template                              Weapons 

 Assassin                  Elite, Martial Human                 Variable Sword (Melee  
                                                                Weapon, AP), Sniper rifle  
                                                                (Heavy Weapon, Loading,  
                                                                AP) 

 Pirate King               Legend, Armored Human                Greatknife (Melee weapon,  
                                                                Accurate), R35 pistol  
                                                                (sidearm, loading, limited) 

 Guard                     Martial Human                        Assault Rifle (Assault  
                                                                weapon) 

 Hacker                    Civilian                             Scavenged pistol (sidearm) 

 Low-tech (medieval        Martial Human                        Primitive melee (Melee  
 or tribal) warrior                                             weapon, primitive, 1  
                                                                damage) 

 Thug or Bandit            Untrained martial Human              Custom pistol (sidearm) 

                                                                                                          
\subsection{Squad}

                                                 SQUAD   

Squads come in two varieties: Squadrons and Infantry. A squadron represents a squad of mech- 
type enemies operating as a group, whereas an infantry squad represents a squad of  
approximately human-sized enemies operating together. They are treated like one entity.
 

All squads (squadrons and infantry) get the following features:
 
    -   Weak: Squads cannot have more than 1 structure or heat capacity. They take energy  
        damage when they take heat.  
    -   Exclusive templates: Squads cannot take the Grunt, Veteran, or Ultra templates (they  
        can still take Elite, but don’t gain structure)  
    -   Split HP: Squads have a large number of members operating together. Once a certain  
        amount of damage is done to the squad, one of the members is destroyed (indicated in  
        the profile). Once a squad is under half HP, it loses some of its attacks to represent this.  
    -   Strength in numbers: Squads have resistance to all damage that is not from line, blast,  
        or cone attacks. They are immune to grapple or ram and cannot grapple or ram.  
    -   Spread out: Squads occupy a square area equal to their size for purposes of targeting,  
        but each individual member is not represented. For the purposes of determining cover  
        and obstruction, use the size of each individual member, not the size of a squad as a  
        whole.  

       SQUADRON 

       Squad, Mech 

       Hull       Agility     Systems       Engineering 

       +1         +1          +1            +1 

       HP         Evasion     E-defense     Heat Cap. 

       16         6           8             - 

       Armor      Speed       Sensors       Size 

       1          5           10            6 (individual:  
                                            1) 

HP per member: 2
 
Number of members: 8
 

Base modules:
 
Primary squad weapon
 
Main Rifle
 
+1 vs evasion/tier
 

                                                                                                          


Range 10
 
3/4/5 kinetic, energy, or explosive damage (choose on creation)
 
This weapon can be fired three times when the squad attacks. If the squad is under 1/2 hp, it can  
only be fired once.
 

Heavy squad weapon
 
Heavy cannon
 
+0 vs evasion with 1 Accuracy/tier
 
Range 12 and blast 2, line 10, or cone 5 (choose on creation)
 
4/5/6 kinetic, energy, or explosive damage (choose on creation)
 

Tier II:
 
HP: +2 (+1 members)
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

          7        8      -       +2   +2    +2   +2       1           5        10 

Tier III:  
HP: +2(+1 members)
 

          Evade    E-D    Heat    H    A     S    E       Armor        Spd      Sense 

         8         8      -       +3   +3    +3   +3       1           5        10 

                                                                                                             

\subsection{Infantry}
                                               INFANTRY   

Infantry-type enemies represent a squad-level group of human or subaltern infantry: not a single  
chassis like the Grunt-type, but (generally) a group of five to ten armed and armored individual  
soldiers. Like the Grunt, an Infantry-type enemy alone might not present a threat to a chassis, but  
operating as a squad with the right gear and training, infantry groups are a formidable threat.    

       INFANTRY 

       Squad, Biological 

       GRIT +2/tier 

       HP         Evasion      E-defense     Heat Cap. 

       10         8            8             - 

       Armor      Speed       Sensors        Size 

       0          4            10            4 (individual:  
                                             1/2 ) 

HP per member: 1
 
Number of members: 10
 

Primary squad weapon
 
Main Rifle
 
+2 vs evasion/tier
 
Range 10
 
3/4/5 kinetic, energy, or explosive damage (choose on creation)
 
This weapon can be fired three times when the squad attacks. If the squad is under 1/2 HP, it can  
only be fired once.
 

Anti-mech squad weapon
 
Heavy cannon
 
AP
 
+2 vs evasion/tier
 
Range 20
 
4/tier kinetic, energy, or explosive damage (choose on creation)
 

Tier II:
 
HP: +5 (+5 members)
 

       Evade    E-D    Heat    Armor       Spd      Sense 

                                                                                                           


        8         10     -        0            4         10 

Tier III:  
HP: +5 (+5 members)
 

        Evade     E-D    Heat    Armor         Spd      Sense 

        8         10     -        1            5         10 

Optional modules for squads (both types): 
 
Armored  
Trait
 
The squad gains +1 armor
 

Ambushers  
Trait
 
The squad gains +2 Accuracy on all attacks and rolls on the first round of combat only, and gains  
+2 Accuracy to avoid being discovered while hiding
 

Go to ground  
Trait, reaction
 
Once per round as a reaction, the squad gains resistance to all the damage from an incoming  
attack, but cannot move or boost on their following turn. They must decide before the damage is  
rolled.
 

Rapid Insertion  
Trait
 
The squad can fly when it moves or boosts.
 

Technicals  
Trait
 
The squad can take the Invasion action (as per player rules). Disable this action if the squad is  
under 1/2 HP.
 

                                                                                                                    

\subsection{Swarm}
                                                   SWARM  

A swarm represents a large, motile group of very small or weak enemies, biological, human,  
nanorobotic, or otherwise.  

All swarms get the following features:
 
    -    Weak: Squads cannot have resilience or heat capacity. They take energy damage when  
         they take heat.  
    -    Exclusive templates: Swarms cannot take the Grunt, Veteran, or Ultra templates (they  
         can still take Elite, but don’t gain resilience)  
    -    Swarms can take the Biological tag if they represent biological creatures. Otherwise a  
         swarm represents a swarm of mechanical entities.  
    -    The Many: The only actions a swarm can take are to move and boost, or those specified  
         in its profile.  
    -    Strength in numbers: Swarms have resistance to all damage that is not from line, blast,  
         or cone attacks. They are immune to the grabbed condition.  
    -    Spread out: Swarms occupy a square area equal to their size for purposes of targeting,  
         but each individual member is not represented. For the purposes of determining cover  
         and obstruction, use the size of each individual member, not the size of a squad as a  
         whole.  
    -    Swarm: A swarm’s area counts as difficult terrain, even if a mech can normally move  
         through it  

       SWARM 

       Swarm 

       Hull       Agility      Systems       Engineering 

       +1         +1           +0            +0 

       HP         Evasion      E-defense     Heat Cap. 

       15         6            8             - 

       Armor      Speed        Sensors       Size 

       -          3            6             5 (individual:  
                                             1/2, 1/4, or  
                                             smaller) 

Base modules:
 
Swarm
 
Trait
 
Targets starting their turn in the swarm’s area or entering it for the first time take 3/5/7 AP kinetic  
damage.
 

                                                                                                            


Optional modules:  
Crawl over
 
Trait
 
When a target starts its turn inside the swarm or enters that area for the first time on its turn,  
members of the swarm cover and crawl over it, inflicting the impaired condition on it until the end  
of its next turn.
 

Drag down
 
Trait, Quick Action
 
1/round, the swarm chooses one target in its area. That target must pass a hull check with 1  
difficulty/tier or be knocked prone
 

Endless Swarm
 
Trait
 
The swarm heals 2 HP/tier at the end of its turn.
 

Split
 
Trait
 
At the end of any turn when the swarm is reduced past 1/2 HP, it splits into two swarms of size 2,  
each with half the swarm’s current HP. These swarms cannot split again.
 

Tear apart
 
Trait
 
The swarm’s Endless Swarm trait also causes 3/4/5 Burn
 

Tier II:
 
HP: +5
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          6         -       -       +2    +1    +0    +0       0            3         6 

Tier III:  
HP: +5
 

          Evade     E-D     Heat    H     A     S     E        Armor        Spd       Sense 

          6         -       -       +3    +1    +0    +0       0            3         6 

                                                                                                                     
\subsection{Monstrosity}
                                           MONSTROSITY  

Monstrosity-type enemies are massive or horrifying predatory wildlife. Generally wild, some kinds  
of monstrous enemies can be domesticated and trained for combat: these are in high demand in  
the distal and proximal reaches of the galaxy. 
 

       MONSTROSITY 

       Biological 

       Hull       Agility      Systems       Engineering 

       +2         +1           +0            +0 

       HP         Evasion      E-defense     Heat Cap. 

       15         10           10            - 

       Armor      Speed        Sensors       Size 

       1          6            10            1-3 

Base mutations:  
Claws
 
Main melee
 
+2 vs evasion/tier with 1 accuracy
 
6/8/12 kinetic damage
 

Optional mutations (choose 1 or more):
 

Acid Spittle  
AP  
+0 vs evasion with +1 accuracy/tier
 
Range 10
 
3/4/5 energy damage
 

Adhesive Extrusion  
Trait
 
The first target damaged by the monstrosity on a turn must pass an engineering check or  
become Slowed until it heals any amount of hit points or until the end of the current challenge.
 

Burrower  
Trait, Quick Action
 
The monstrosity can burrow into the ground as a quick action, as long as the ground beneath it  
is malleable enough. While burrowed, it counts as invisible, ignores all obstructions above  
ground, can take no other actions other than to move, boost, or emerge as a quick action. When  

                                                                                                           


it emerges, it must have a free space to emerge into. It loses these benefits and all adjacent  
mechs must pass a hull check or be knocked prone.
 

Charger  
Trait, Quick Action, Recharge (5+)
 
As a quick action, the monstrosity in a straight line as far as possible up to its speed, ignoring  
obstructions and not provoking reactions. Any targets it passes adjacent to or over must pass an  
agility check or take 4/6/8 kinetic damage.
 

Corrosive Bite  
Full Action, Recharge 5+
 
The monstrosity makes a melee attack at an adjacent target for +2 vs evasion/tier. On hit, the  
target takes 4/6/8 Burn. In addition, regardless of whether it succeeds this check, it is Shredded  
until it regains any amount of HP.
 

Grasping Claws  
Trait
 
The monstrosity gets +1 Accuracy to grapple, +1 Accuracy to attack targets it is grappling, and  
can boost and take reactions while grappling.
 

Natural Camouflage  
Trait
 
The monstrosity gains +1 Accuracy to checks made while hiding. If it’s in its natural terrain, it  
counts all terrain as being large enough to hide it (no matter the size difference).
 

Regenerator  
Trait
 
The monstrosity heals 2/3/4 HP at the end of its turn. This trait does not function if the  
monstrosity took energy damage at any point during the round.
 

Spined  
Trait
 
When the monstrosity takes damage from a melee weapon, it deals 1 AP kinetic damage to its  
attacker after the damage resolves.
 

Swift  
Trait
 
The monstrosity gains +2 speed
 

Tempered Hide  
Trait
 
The monstrosity has resistance to one of the following damage types: kinetic, energy, explosive  
damage.
 

                                                                                                                    


Winged  
Trait
 
The monstrosity can fly when it moves or boosts.
 

Increase at tier II :
 
HP +2
 
+1 optional mutation
 

         Evade    E-D     Heat    H   A   S    E   Armor     Spd       Sense 

         11       11      -       +   +   +    +   2         7         10 
                                  4   2   0    0 

Increase at tier III:  
HP +2
 
+1 optional mutation
 

         Evade    E-D     Heat    H   A   S    E   Armor     Spd       Sense 

         13       13      -       +   +   +    +   2         8         10 
                                  6   4   0    0 

All monstrosities get the following features:
 
    -    Unique Critical Chart: If the monstrosity has structure (such as an Elite or Ultra), it uses  
         the critical chart below instead of the regular one for mechs  
    -    Biological: The monstrosity has the biological tag  

                                          Monstrosity Critical Chart  

 ROLL       RESULT                   EFFECT 

 5-6         GLANCING BLOW           The monstrosity flinches in pain, giving it the impaired condition until  
                                     the end of its next turn 

 4           HEAVY BLOW              The blow knocks the monstrosity down. The attacker (or the GM)  
                                     chooses one of the following:
 
                                         -   The monstrosity is Slowed until the end of its next turn
 
                                         -   The monstrosity is knocked prone 

 3           HEAD TRAUMA             The monstrosity is stunned until the end of its next 

 2           DISMEMBERMENT           A limb or chunk is torn off the monstrosity, dealing +1d6 bonus damage  
                                     to it and permanently slowing it until it can potentially heal. 

 1           BRUTAL HIT              The monstrosity must pass a hull check or be destroyed. It gets +1  
                                     difficulty on this check per level of structure damage it has. 

                                                                                                                 


Two or     FATAL HIT              The monstrosity is destroyed and instantly killed 
more  
1s 

                                                                                                          


                                       TEMPLATES
 

These templates can be applied to any of the above enemy types to add more flavor or change  
the way they function in combat. In particular, the Ultra, Elite, Grunt, and Veteran templates can  
be used to make tougher or easier enemies. The Veteran template can be applied on top of the  
Ultra or Elite templates to make an especially tough enemy.
 
\subsection{Ultra}
                                                   ULTRA  

In Lancer, Ultra-type enemies are typically the most dangerous individual enemies a party can  
face.   

Ultra-type enemies are high-tier enemies that do not usually fill command roles. Ultras are  
champions, favored warriors, major domos: they might command a few units in a retinue or lead  
armies from the front, but they do not typically engage in grand strategy.    

Making an Ultra
 
All ultras get the following features added to their base NPC type:
 
    -    Bonus activations: The Ultra can be activated again (take another turn) each round. If  
        the Ultra is facing more than 4 players, it takes another activation (for a total of 3). It  
         regains spent reactions each time it takes a turn.  
    -    Deadly: The Ultra can Critical Hit, dealing an extra +2 bonus damage/tier on Critical Hits.
 
    -    Exclusive templates: The Ultra can’t take the Elite or Grunt templates.  
    -   Juggernaut (trait): At the start of its turn, the Ultra ends one condition affecting it. If it  
         rolls a ‘system destroyed’ result on a structure check, it is instead jammed until the end of  
         its next turn (it doesn’t lose the system or weapon).
 
    -    Legendary (trait): The Ultra can enter the CRITICAL state and is not destroyed when  
         reaching 0 HP.  
    -   Structure: The Ultra gains 4 Structure, or increases its structure up to 4 structure if it  
         already has structure
 
    -   Stress: The Ultra gains 4 reactor stress, or increases its stress up to 4 if it already has  
        stress.  
    -    Bonus module: The ultra should gain +1-2 more optional modules than normal.  
    -    Bonus HP: The Ultra gains +5 HP  
    -    Reflex (trait): The Ultra can make any number of overwatch attacks per round (instead of  
        just 1). It can only attack the same target 1/turn with overwatch.  

Then choose 1-3 Ultra Traits or modules.
 

ULTRA traits:
 

                                                                                                            


Berserker  
Trait  
The Ultra gains +1 Accuracy on all melee attacks. It can make 1 melee attack roll, grapple, or  
ram attack as a Free Action on its turn.
 

Devastator  
Trait
 
Once per turn, when the ultra hits with an attack, all targets visible to the ultra take 2 kinetic,  
explosive, or energy damage.
 

Evasive
 
Trait
 
The Ultra gains +4 evasion, up to a maximum of 20, but reduce its structure to 3.
 

Extra Deadly  
Trait  
The first Critical Hit the Ultra deals per turn does +1d6 bonus damage/tier
 

Fortress  
Trait
 
The Ultra gains the Fortress trait instead of its Hardened Target trait (lock on, invasion, and scans  
are made against it at +3 difficulty). To electronic systems, it doesn’t appear to even be there.
 

Legion  
Trait
 
The ultra gains +4 e-defense, up to a maximum of 20, can take the full tech action (like a player),  
and gains +2 accuracy to all tech actions
 

Limitless  
Trait
 
The Ultra can use overcharge.
 

Unstoppable  
Trait
 
The Ultra always cannot be knocked back, knocked prone, or moved involuntarily.
 

Sight  
Trait
 
Targets cannot hide while inside the Ultra’s sensor range and it ignores invisibility.
 

Superior Construction  
Trait
 
The ultra has resistance to one of the following damage types: kinetic, energy, explosive. It  
cannot gain resistance to more than 2 (from this trait or any other systems).
 

                                                                                                                        


Superior Frame  
Trait
 
The ultra is immune to the Slowed, Shredded, and immobilized conditions
 

Superior Reactor  
Trait
 
The ultra is immune to the stunned and shut down conditions.
 

Superior Targeting  
Trait
 
The ultra ignores light and heavy cover when making ranged attacks.
 

Supreme Maintenance  
Trait  
The ultra is immune to the Jammed condition and can reload one weapon with the loading  
property as a free action on its turn.
 

Supreme Parting Gift  
Trait  
The Ultra can use the Self Destruct action. When it takes this action, it emits an EMP pulse. All  
vulnerable targets (mechs, vehicles) in a burst 5 area around it must pass a system check or be  
shut down.
 

Supreme Skirmisher  
Trait
 
2/round the Ultra can take the boost action as a reaction to any enemy movement or action that  
it can see.
 

Ultra systems and weapons:  

ARGUS armor  
The ultra’s armor increases to 6. Each time it rolls a critical or overheating check, reduce its  
armor by 2, to a minimum of 0.
 

H.A. Siege Shield  
The ultra has resistance to all damage that originates further away than range 5
 

Hellfire Projector  
Heavy CQB
 
Cone 5
 
3 energy damage + 5 Burn/tier
 
This weapon can be fired twice with the attack action, but its areas cannot overlap.
 

                                                                                                                   


HORUS manticore repulsion field  
Hostile targets that start their turn adjacent to the Ultra or become adjacent to it for the first time  
on their turn take 2 energy damage, 2 heat, and must pass a systems check or become impaired  
until the end of their next turn.
 

Obliterator
 
Action, Ordnance, Recharge (6+)
 
Choose a direction, then draw a line 30 spaces long and 2 spaces wide in that direction. Each  
target inside that area must pass an agility skill check or take 1/2 of its current hit points in energy  
damage, or 1/4 on a successful check, rounded up. Any cover, objects, buildings, drones,  
deployables, or items smaller than size 5 in the area are completely annihilated.
 

Ravager Turret  
Heavy Cannon
 
Ultra
 
+1 vs evasion with 1 Accuracy/tier
 
Range 10
 
4/6/8 kinetic damage
 
The Ravager fires at every hostile mech in range when this weapon is fired with the attack action.
 

SSC Slivershielding  
System
 
The Ultra is permanently invisible. Reduce its structure to 2.
 

SSC Ex Hover propulsion  
System  
The Ultra can fly when it moves or boosts, and can hover (it can stop midair, doesn’t have to  
move in a straight line, and doesn’t need to land after moving).
 

Volley module
 
Full Action, System
 
The ultra goes into a stable stance. At the start of its next turn, it fires one weapon at each target  
that is in range and not in cover or prone as a Free Action. It can fire the same weapon multiple  
times for this special action, ignoring the loading tag during this attack.
 

WOLFHOUND missile  
Heavy Launcher
 
Recharge (6+)
 
Instead of firing this weapon normally, choose a target within range 30. The ultra fires a  
wolfhound missile at the target, which is size 1, moves speed 4, has evasion 10, 0 armor, and  
10/15/20 HP. The missile primes in an adjacent space when deployed, then moves 3 at the start  
of each the ultra’s turns. If its target suffers from the Locked On condition, its movement  
increases to 6. The missile can benefit from cover and can be targeted and shot by systems and  
weapons. It must move towards its target, but can maneuver skillfully around cover, fit through  

                                                                                                            


holes, etc. If the missile’s movement causes it to collide with a hostile mech or its target, it  
detonates for a blast 1 explosion. Mechs caught inside must pass an agility skill check or take  
15/20/30 energy damage, and half on a successful check.
 

The Ultra can have only one missile fired at a time. Only check for recharge if this missile has hit  
its target or been destroyed.
 
\subsection{Elite}
                                                   ELITE  

Making an Elite
 
All Elites get the following features added to their base NPC type:
 
    -   Structure: The Elite increases to 2 structure
 
    -   Stress: The Elite increases to 2 Reactor Stress
 
    -    Bonus Activation - The Elite can be activated twice a round  
    -    Exclusive templates: The Elite can’t take the Ultra or Grunt templates.  
    -    Bonus system: The Elite gains +1 more optional system than normal  
\subsection{Grunt}
                                                 GRUNT   

Grunt-type enemies in Lancer are the most common enemies faced en-mass by players. Grunts  
are a step above cannon fodder: cheap and trained to be disciplined fighters before deadly ones,  
grunts follow orders under threat of death, imprisonment, or some other kind of censure. Alone, a  
grunt-type enemy may not be a threat, but in a group, they can present an overwhelming mass of  
bodies and fire that threatens even the most powerful individual.   

Making a Grunt
 
All grunts get the following features added to their base NPC type:
 
    -   Weak: The Grunt’s maximum HP becomes 1, with 1 structure. It loses any heat capacity it  
         has (so it takes energy damage instead of heat). It cannot gain structure or heat capacity  
         in any way.  
    -   Surprisingly Hardy: Grunts don’t take damage from systems, talents, or weapons that  
        automatically deal damage (such as the reliable tag). When they would take half damage  
        on a successful save from a source of damage, they instead take 0.
 
    -   Still a mech: Grunts can only be killed by pilot weapons that have a total attack roll of  
        20+  
    -    Bonus activations: When a Grunt is activated, up to 2 other grunts can also be activated  
        at the same time and take their turns at once
 
    -    Max systems: The Grunt can’t have any more than 1 optional system  
    -    Exclusive templates: The Grunt can’t take the Veteran, Squad, Elite, or Ultra templates  
    -    Max attacks: The Grunt can’t attack with more than 1 weapon a turn.  
    -    Max damage: None of the grunt’s attacks can deal more than 4 damage, heat, or burn  
        total per attack at tier 1, or half if the attack is AOE or has more than one target. This  
         increases to 6 at tier II and 8 at tier III. Adjust as needed.  

                                                                                                           

\subsection{Veteran}
                                                   VETERAN  

Veteran-type enemies are hardened, experienced fighters that have survived direct engagement  
with their foes. Their encounter with your players is not their first rodeo: their ability to withstand  
morale shocks is far higher than an untested greenhorn.
 

Making a Veteran:
 
All Veterans get the following features added to their base NPC type:
 
     -   Bonus structure: The veteran gains +1 structure.
 
     -   Bonus stress: The Veteran gains +1 reactor stress  
     -   Veterancy: The Veteran gains +1 accuracy on all checks of one statistic: Hull, Agility,  
         Systems, Engineering (choose on creation)  

Then choose up to 1 Veteran trait per tier:  
AI co-pilot  
Trait  
The veteran’s mech or vehicle gains the AI tag. The veteran’s mech or vehicle is autonomous and  
can function even if the veteran is not piloting it (per the player rules). The AI can be unshackled,  
with the same effects as player AI.
 

Acrobat  
Trait  
When the veteran moves or boosts, it can fly 3 after the move or boost completes. This flight  
does not provoke reactions and ignores engagement.
 

Deadly  
Trait  
This mech can Critical Hit, dealing +2 bonus damage/tier to its attacks on crit.
 

EM-shielding  
Trait  
The veteran is resistant to heat
 

Engineer  
Trait, Quick Action  
The Veteran can take the repair quick action:
 
         Repair (limited 1): This mech heals 4 hit points per tier and ends one condition currently  
         affecting it (impaired, Slowed, immobilized, shut down, jammed)
 

Feign Death  
Trait  

                                                                                                                  


The first time in a challenge this enemy would be destroyed, though it appears destroyed, it is  
instead shut down, remaining at 1 hp. A successful scan or pilot notice check will reveal it is still  
active.
 

Hacker  
Trait  
The veteran’s invasion attacks deal +3 heat
 

Headshot  
Trait  
1/round when the veteran scores a Critical Hit, the target of its attack must pass an engineering  
check or be jammed until the start of the veteran’s next turn.
 

Hardened Target  
Trait  
Invasion, scan, and lock on attempts on this target are made with +1 difficulty
 

Legendary  
Trait  
The veteran can enter the CRITICAL state (like the player) instead of being destroyed when  
ticking off its last structure point.
 

Lesser Sight  
Trait
 
Within range 3 of the Veteran, targets cannot hide from it, and cannot benefit from invisibility  
against it while inside that area.
 

Limitless  
Trait
 
The veteran can use Overcharge
 

Lightning Reflexes  
Trait  
Reaction
 
The first time in a round the veteran is targeted by any weapon system of size heavy or larger, roll  
a d6. On a 5+, the weapon automatically misses this mech.
 

Parting Gift  
Trait  
The veteran can use the Self Destruct action.
 

Rodeo master  
Trait  

                                                                                                                     


The veteran can jockey (in a hard suit) and gains +1 Accuracy on jockeying attempts
 

Shock Armor  
Trait
 
The veteran has resistance to damage from main size weapons
 

Skirmisher  
Trait
 
1/round the veteran can move or boost as a reaction to any enemy movement or action that it  
can see.
 

Slippery
 
Trait
 
The veteran does not provoke reactions and ignores engagement with its move (its boost still  
provoke reactions) 
 

Steel Jaw  
Trait  
The most damage an auxiliary weapon can do to the veteran is 1.
 

Viper’s Speed  
Trait  
The veteran always takes its turn first, even over player characters. If there is a question of who  
acts first (in the story, or combat), it is always the veteran.
 
\subsection{Exotic}
                                                      EXOTIC   

Exotic-type enemies are, even for a galaxy of wonders, strange and dangerous enemies. Some  
feature unique technologies not yet available to the wider galaxy, others wield primitive weapon  
styles updated to the modern day, and others carry equipment or adopt tactics that are alien to  
Union doctrine.  
 
 
Making an Exotic NPC:
 
All Exotic NPCs get the following features added to their base NPC type:
 
     -   Xenotech: Scans reveal no information about exotic modules  
     -   Hardened Target: Hostile tech actions take +1 difficulty against exotic targets  
     -   Exotic systems: Any NPC with the exotic tag can choose one or two of the optional  
         exotic modules below  

Exotic modules
 
Bio-integrated  
Trait
 
You may only choose this trait for a mech. The mech gains the biological tag (it loses heat  
capacity and cannot take or be the target of tech actions except Lock On and scans).
 

                                                                                                                     


Blinkspace Carver  
System
 
When the NPC moves, it teleports.
 

Extrusion  
Trait
 
The NPC is only a partial extrusion of a higher-concept entity and only partially present in  
physical space. It gains resistance to all damage but all its weapons also deal half damage and it  
can be passed through as if it wasn’t there (it doesn’t provide obstruction).
 

Living Weaponry  
Trait
 
The NPC becomes immune to the Jammed condition. Its weapons have biotechnical and semi- 
organic components that spontaneously generate ammunition.
 

Paracausal Weapon  
Trait
 
Choose one of the NPC’s weapons. Damage from that weapon cannot be reduced in any way  
(by armor, resistance, or otherwise)
 

Ouroboros Brand  
System
 
1/round the NPC can force a re-roll by themselves or any allied or hostile target (but must choose  
the second result) by causing localized distortions in the flow of time.
 

Regenerator  
Trait
 
The NPC heals 2/3/4 HP at the end of its turn. This trait does not function if the NPC took energy  
damage at any point during the round.
 
\subsection{Drone}
                                                    DRONE   

Drone-type enemies are mechs or subaltern frames that are autonomous extensions of  
companion/concierge units or combat NHPs.  

Making an Drone
 
All Drones get the following features added to their base NPC type:
 
    -    Bonus HP: The Drone gets +5 HP to represent its lack of pilot. It can take damage that  
         would normally blow through a cockpit and kill a human.  
    -    No Pilot: The Drone permanently suffers from the Impaired condition. It cannot make  
         complex decisions or moral judgements. However, it is also immune to all systems and  
         actions that affect the pilot (it doesn’t have any).  

                                                                                                                


     -   Vulnerable to Tech: All hostile tech actions against the Drone can be made with +1  
         Accuracy  

\subsection{Mercenary}
                                                MERCENARY  

Mercenary-type enemies are foes that offer their services to the highest bidder. They may have  
attachments to a faith or flag, but when it comes to doing their business, they’re loyal only to  
gold.    
 
 
Making a Mercenary:
 
All Mercenaries get the following features added to their base NPC type:
 
     -   Opportunist: If an allied target is adjacent to the mercenary’s target, it gets +1 Accuracy  
         on all attack rolls against that target  
     -   Mercenary systems: A mercenary can choose from the list of mercenary systems and  
         traits below when choosing optional systems and modules  

Mercenary systems and traits:
 
Bounty Hunter
 
Trait
 
Before combat, choose a player character that there’s a bounty out for. The mercenary gains +1  
Accuracy on all attacks and checks against that character and their mech.
 

Efficient Killer
 
Trait
 
The mercenary gains +1 Accuracy on attacks and all its damage becomes AP against a target  
with 1 structure remaining.
 

Call in Favor
 
Action, Limited (1)
 
The Mercenary calls in a favor in the form of an orbital strike or artillery strike, targeting a blast 2  
area within range 30 of its position. All mechs caught in the area must pass an agility check or  
take 6/10/15 explosive damage, or half on a successful check.
 

Scout Drone
 
Action, Limited (1)
 
The Mercenary fires a scout drone to an empty space within its sensor range. The drone has  
evasion 10, 10 hp, and no armor. Within a burst 3 area centered on the drone, no target can turn  
invisible or hide from the mercenary, and the mercenary can attack targets in the area with +1  
accuracy. The mercenary can reposition the drone as a free action at the start of its turn.
 

Tactical Retreat
 
Reaction, Limited (1)
 
When the mercenary is taken below half health, this system automatically activates. All targets  
within a burst 2 area around the mercenary must pass a systems check or take 2 kinetic damage  

                                                                                                                   


and become jammed until the end of their next turns. The mercenary can then move its speed in  
any direction. This movement doesn't provoke reactions and ignores engagement.
 
\subsection{Commander}
                                              COMMANDER   

Commander-type enemies operate on a grand scale, controlling fleets and armies across worlds  
and in interstellar space. They might not be the best individual combatant, but they can bring out  
the best in the best of their forces.   

Making a Commander:
 
All Commanders get the following features added to their base NPC type:
 
    -    Bonus structure: The Commander gains +1 structure  
    -    Bonus stress: The Commander gains +1 reactor stress  
    -    Command: Once per round, the Commander can cause an allied target it can see to re- 
         roll any single attack roll or check as a reaction. The commander can’t use this reaction if  
         it is Jammed.  
    -    Commander Traits: The commander can choose one of the following commander traits.  
         These traits don’t function if the commander is Jammed.  

Commander Traits
 
Bolster network  
Trait  
While the commander is alive, all allies the commander can see gain the hardened target trait (+1  
difficulty on all hostile tech actions or attacks against them). The commander does not benefit  
from this trait.
 

Covering Fire  
Trait, Reaction
 
1/round, an ally the commander can see can attack with one weapon as a reaction against a  
target hostile to the commander that just made an attack against that ally or a different ally.
 

Press on!  
Trait, Free Action
 
1/round, the commander can pass a systems check as a free action to end the stunned or  
jammed conditions on a target it can see in its sensor range.
 

Reposition  
Trait, Free Action
 
1/round one ally that a commander can see can make the boost action as a reaction on the  
commander’s turn.
 

Rank and File  
Trait
 
Allied targets adjacent to the commander gain +1 Accuracy on all attacks and checks.
 

                                                                                                                
\subsection{Pirate}

                                                   PIRATE  

Pirate-type enemies live on the boundaries, in the forgotten bolt-holes of occupied space. They  
are far-ranging, operating around blink gates, interstellar shipping lanes, and near flagged but  
not-yet colonized worlds.   

Pirate-type groups are usually small, with their base of operations hidden a short-to-medium  
distance from the area that they are first encountered. Usually they are motivated by profit and  
materiel goods, not ideology or religion -- a good thing for a savvy negotiator.    

Pirate-type enemies commonly operate in mixed groups of fast, deadly subline ships, fighter/ 
bombers, and clutches of marines and mechanized chassis. They prefer hit-and-run style  
overwhelming ambush attacks, aim to capture rather than kill, and don’t like to engage in pitched  
battles  
 

Pirate-type enemies can be found across the galaxy wherever the law is spread thin, resources  
travel, and people are desperate.   

Making a Pirate
 
All pirates get the following features added to their base NPC type:
 
    -    Deadly (trait): The pirate can Critical Hit, dealing +2/3/4 bonus damage on a 20+ ranged  
         or melee attack roll  
    -    Pirate modules: The pirate can choose from the below modules when choosing optional  
         systems  

Gain the following options for optional systems/modules:
 

Boarding Clutch
 
Heavy Melee
 
+0 vs evasion with +1 Accuracy/tier
 
5/7/9 kinetic damage
 
This weapon can be used as an improvised grappling hook. It can be thrown at a target within  
range 5. The affected target must pass a hull or agility check or be pulled directly to the attacker  
and grappled.
 

Splinter Rounds  
System
 
Critical Hits from this mech deal an additional +3 bonus damage
 

Borer Missiles  
Main Launcher
 

                                                                                                              


Smart, Limited (1)
 
+1 vs e-defense with 1 Accuracy
 
Range 8
 
On hit, 1d3 miniature drones are attached to the target and begin boring into the mech’s interior.  
In 1d6+3 rounds, if there are any missiles still attached to the target, they bore inside the cockpit  
savage the pilot, reducing the pilot to 0 HP, causing them to make a Down and Out check. A  
single drone can be removed by making a successful systems or engineering skill check as a  
quick action. The drones can also be confused by shutting the affected mech down, which  
deactivates them. The pilot in the affected mech is aware of how much time they have before the  
drones bore through.
 

Prying Claws  
System, Full Action, Limited (1)
 
An adjacent target makes a hull check. On a failed check, the targeted pilot immediately exits  
their mech as if they had taken the dismount action (place them adjacent to their mech).
 

Slaver Signal  
System, Full Action
 
Recharge 5+
 
Range 10
 
This system affects one piloted vehicle or mech within range 10. The affected target must make  
a systems check with 1 difficulty/tier to shut out the signal or be affected. On failure, all the pilots  
in the target are affected by the signal, falling into an unresponsive stupor. While in this state,  
their mech is stunned. If the target takes damage, the pilots will be jolted awake, immediately  
ending this effect. Another adjacent actor can use an action on their turn to make a systems  
check to try and blot out the signal, waking the affected target up on success. If the source of  
the signal is destroyed, any targets affected will also wake up.
 
\subsection{Spacer}
                                                 SPACER  

Spacer-type enemies are born and bred in the hard vacuum of deep space. They are adept at  
maneuvering in and around the difficult, kinetic, low-gravity environments found only in space:  
blink stations, space stations, among asteroid fields, in low orbit over worlds, and between ships  
in military and commercial fleets.     

Making a Spacer:
 
All Veterans get the following features added to their base NPC type:
 
    -    Maneuverable: The Spacer does not suffer the impaired condition for operating in space,  
         underwater, or in zero-g environments and always counts as having an EVA module in  
        those environments.  
    -   Optional modules: The Spacer can choose from optional Spacer modules when  
        deciding additional modules  

Spacer modules
 
Concussion gun
 

                                                                                                           


Main Rifle
 
Cone 3
 
+1 vs evasion/tier with 1 Accuracy/tier
 
Mechs hit by this weapon are 3 spaces away from the direction of the zone.
 

Gravity Rifle
 
Main Rifle
 
Range 10
 
+1 vs evasion/tier with +1 Accuracy/tier
 
The target of this attack must pass a hull check with 1 difficulty/tier or be pulled in a straight line  
towards the wielder of this weapon up to 10 spaces, or as far as it can move. If this causes it to  
collide with an obstacle or another mech, it is additionally knocked prone.
 

Sealant Trap
 
Mine, Limited (1)
 
This self deploying trap can be placed in a vacant space. It counts as a mine and can be  
scanned to be detected and disabled with a successful systems check. Once any target walks  
over or adjacent to the trap, it explodes, creating a burst 2 area centered on it. All targets caught  
inside must pass an agility check or be covered in thick, fast-drying hull sealant and immobilized.  
The only way to break out of the sealant is to do enough damage to break it (evasion 5, 15 hp).
 

Thumper grenades
 
Grenade, Limited (1)
 
Thrown 5
 
Once thrown to an impact point as a quick action, these grenades explode outwards with a  
concussive pulse in a blast 1 area around the space where they are targeted. Targets caught in  
the area must pass an agility check or be knocked back 3 spaces directly away from the impact  
point. If this causes them to collide with an obstacle or another mech, they are additionally  
knocked prone.
 
\subsection{Outworlder}
                                            OUTWORLDER   

Outworlder-type enemies are found in the distal/proximal areas of the galaxy. They are, typically,  
more rugged and independent than other enemy types, able to operate on a shoestring -- or  
without one! -- for extended periods of time.  
 

Making an Outworlder
 

    -    Resourceful: The Outworlder gains +1 use to all (limited) use weapons, actions, and  
        deployables (including the repair action below - not yet included in the profile).  
    -   The outworlder gains the repair action:  
             -   Repair (limited 1): This mech heals 4/6/8 hit points and ends one condition  
                 currently affecting it (impaired, Slowed, immobilized, shut down, jammed)  

                                                                                                           

\subsection{Vehicle}
                                                VEHICLE   

Vehicle-type enemies are in-atmosphere military or civilian vehicles found throughout the galaxy. 
 

Making an Vehicle
 
You can use any of the mech classes and apply this template to convert that mech into a vehicle.  
They lose the mech tag and gain the vehicle tag. All vehicles get the following features added to  
their base NPC type:
 
    -    Limited Maneuverability: A vehicle must always move in a straight line (though it can  
         move and boost in separate directions). A vehicle cannot climb or swim. It gets +2  
        Accuracy on checks to avoid being knocked prone, but cannot right itself without  
        assistance.  
    -   Crew: A vehicle might be operated by more than one crew member (typically a minimum  
         number of crew equal to 1/2 of the vehicle’s size). As long at least half the crew is alive, the  
        vehicle can still function.  
    -    No manipulators: A vehicle cannot initiate a grapple, pick up, or manipulate items  
    -   Type: You can give a vehicle one or more of the following types:  
             -   Flier: A flying vehicle can fly when it moves or boosts  
             -   Transport: A transport vehicle can hold one squad or a number of entities whose  
                 total size (added together) is less than its size  
             -   Treads or Hover: A Treaded or Hover vehicle ignores difficult terrain  
\subsection{Ship}
                                                    SHIP   

Ship-type enemies are any military or civilian vehicles that are flight capable and operate primarily  
in space, outside the bounds of atmosphere (though many can operate in-atmos if need be).
 

Making a Ship
 
You can use any of the mech classes and apply this template to convert that mech into a ship.  
They lose the mech tag and gain the vehicle tag. All ships get the following features added to  
their base NPC type:
 
    -    Flier: A ship always counts as having an EVA module in space. In atmosphere, it can fly  
        with either normal flight or hover flight (depending on type). If a ship is grounded without  
         landing, it is immobilized. If it is immobilized, knocked prone, or stunned mid-air, it  
        crashes.  
    -    Massive size: A ship is typically much larger than a mech. If its size is less than 4,  
         increase its size to 4. This template describes ships that can be engaged on a ship-to- 
         mech level about up to size 6-8. Much larger ships (size 10/20+) are usually too heavily  
        armored for mech-mounted weapons to harm  
    -   Crew: A ship might be operated by more than one crew member (typically a minimum  
         number of crew equal to 1/2 of the vehicle’s size). As long at least half the crew is alive, the  
        ship can still function.
 
    -    Bonus HP: Increase the Ship’s HP by +5  
    -    No manipulators: A ship cannot initiate a grapple, pick up, or manipulate items  
    -    Limited melee attacks: A ship cannot make melee attacks other than Ram
 

                                                                                                            


-   Transport: A transport ship can hold one squad or a number of entities whose total size  
    (added together) is less than its size  

                                                                                                       
