\section{Talent List}


                                                                                                             


                                        TALENT LIST
 
\subsection{Ace}

                                                       Ace  

All pilots brag about their abilities, but some can back it up with proof: to be an ace means you are among  
the most qualified of pilots. Whether you’re a talented rookie or a grizzled veteran, you’ve gained a level of  
notoriety through your flying ability that has your callsign known throughout the system. Most enemy pilots  

flee when they recognize your mech’s distinctive livery, but some see your reputation as a chance to test  
their own mettle.   

Acrobatics  (Rank I): Make all agility checks while flying with +1 accuracy. When any attack  
misses your mech, it can fly 1 space in any direction as a reaction.
 
Afterburners  (Rank I): When you take any boost action while flying, you can elect to move 1d6  
spaces further, but take half of that as heat.
 
Supersonic (Rank III): If your mech ends its turn flying, at the end of your turn, nominate an  
enemy or ally in your movement range and line of sight. At the end of that enemy or ally’s turn,  
even if they are no longer in line of sight or range from you, your mech may fly to any free  
adjacent space to that target as a reaction, as long as there is a path to do so. This movement  
ignores engagement and does not provoke reactions.

 \subsection{Armsman}


                                                  Armsman  

 Think of a firefight. What’s your average pilot or trooper gonna sling? Jacketed lead of course. A mag or  
three of depleted uranium if their target’s a big one. Boring. No, worse than boring -- dull. Predictable.  
Basic.   

Dull isn’t fun. Predictable gets you killed. Basic leaves a boring body. Put down the depleted uranium and  
pick up a magazine of anoriginary stutter-blink slugs, or at least a pack of tachyon flechettes. Lay waste in  
style, and live forever.  

Armament (Rank I): You have an custom supply of ammunition that can be used with all your  
main ranged weapons. The ammo case is a limited (6) system that doesn’t take any SP but can  
be destroyed by system damage, etc. You can load special ammo when you fire a main weapon,  
expending a use of this system and choosing one of the following options (you can only load one  
type at once). The ammo lasts for one shot.
 
         	- Ripper - The attack gains the AP tag and deals kinetic damage
 
         	- Thumper - The attack gains knockback 2 and deals explosive damage
 
         	- Shock - The attack deals energy damage. Any actors adjacent to the primary target  
         take 3 energy damage (no attack required). The primary target doesn’t take this damage.
 
Underslung (Rank II): Gain the following ammo types. They cost 2 charges instead of 1.
 
         	- Hellfire - The attack becomes kinetic damage and deals +2 burn
 
         - Jager - The attack becomes explosive damage, gains knock back 3, and a target struck  
         must pass a hull check or be knocked prone
 
         	- Mag - The attack deals energy damage and gains the Arcing tag
 
Efficiency (Rank III): If you score a Critical Hit with special ammo, you don’t expend it’s use.
 

                                                                                                                 
\subsection{Bonded}


                                                     Bonded  

The galaxy is a big place: everyone can use a friend to watch their back. Maybe you two enlisted together,  

or were the only survivors of a bloody engagement. Maybe you weren’t even friends to begin with, or  
maybe you were raised to fight together  -- however it came to be, when it comes time to drop, there’s no  
one you’d rather have at your side. Alone, you’re deadly, but together you’re a force of nature.    

I’m Your Huckleberry (Rank I): When you take this talent, choose another pilot to be your  
bondmate. When you make any mech skill check while your mech is adjacent to theirs, gain +1  
Accuracy. You can change your bondmate between missions, but only if something has changed  
between the two of you.  
Cover me! (Rank II): You can use your overwatch reaction to attack any target in your threat  
range that attacks your bondmate after the attack resolves (this replaces your regular overwatch  
reaction for the round).  
Sundance (Rank III): Gain the following reaction:  
         Intercede  
         Reaction  
         Once per round, when your bondmate’s mech or pilot is adjacent to you and takes  
         damage from a source you can see, you can choose to take the damage instead.  
\subsection{Brawler}

                                                     Brawler  

Close, personal, martial. The way battle has been done since the dawn of time, but forgotten since the first  
spark of gunpowder. You, however, prefer the old ways. Hand-to-hand, weapons discarded, just the  
strength of your machine versus the strength of theirs. You know the sweetest victory is one found at the  

culmination of a dance as old as war itself, in the oldest way known to humanity: by a fist to the face of  
your enemy.   

Hold And Lock (Rank I): You gain +1 Accuracy on all melee attacks against targets you are  
grappling.
 
Knockout Blow (Rank II): Gain a Brawler Die (a d6), starting at 1. Each time you make the  
grapple, ram, or improvised attack action, raise the value of the die by 1. When the value of the  
die is 6, you can spend it to make a knockout blow as an action against any adjacent target as a  
quick action. That target must pass a hull check with 1 difficulty or take 2d6 AP kinetic damage  
and become stunned until the end of its next turn. The die then resets to 1.
 
Sledgehammer (Rank III): Your improvised attack action does 2d6 AP kinetic damage and gains  
knock back 2.
 
\subsection{Brutal}

                                                      Brutal  

In dismounted sparring and in live combat, you only know one speed: maximum. When others go hard, you  
go hardest. When the order is to eliminate the enemy, you do so with prejudice. This isn’t a dance, this isn’t  

a game, this is war, and you mean to see it through. If it means becoming a little bit of a monster, than so  
be it -- let them hate you from the grave.   

                                                                                                                  


Cull the Herd (Rank I): Your Critical Hits now gain knock back 1.
 
Predator (Rank II): If your die result on your d20 is a 20 (sometimes called a ‘natural 20) on any  
ranged or melee attack roll, your attack is a critical hit, no matter what, and instead of rolling all  
the damage twice and choosing the highest result, your attack deals maximum damage (for its  
base and bonus dice).
 
Relentless (Rank III): When you miss with an attack on your turn, your very next attack gains +1  
accuracy.
 
\subsection{Crack Shot}

                                                   Crack Shot  

Everyone can hit anything these days with the help of modern technology. Targeting-assist. Smart  

Weapons. An AI whispering in your ear, moving your hand for you, squeezing the trigger for you, doing  
everything but taking credit for the kill. But you, pilot, are different. Hitting your target is as easy as looking  
at it, inside of your mech and out. No targeting assist for you, no AI necessary. All you need is a zeroed  

sight, a fresh magazine, and a target downrange.   

Stable, Steady (Rank I): At the start of your turn, you can choose to steady your aim as a Free  
Action. If you do, you are immobilized until the start of your next turn, but gain +1 Accuracy on all  
your rifle attack rolls.  
Accurate and Precise (Rank II): You can now attack targets with your rifles even when they are  
outside of their maximum range, up to twice your rifle’s maximum range, but your attacks gain  
+1 difficulty if attacking this way.
 
Watch This (Rank III): While wielding a rifle and steading your aim, if you score a Critical Hit, you   
deal +1d6 bonus damage and can force your target to pass a hull or agility check (defender’s  
choice) or additionally suffer one of the following effects. If you have accuracy on the attack roll,  
before you make the attack you can sacrifice any number of accuracy dice to give the target an  
equivalent amount of difficulty on the check.
 
     -   Headshot: Your target has line of sight only to adjacent spaces until the end of its next  
         turn
 
     -   Legshot: Your target is immobilized until the end of its next turn
 
     -   Bodyshot: Your target is knocked prone.
 
\subsection{Centimane}

                                                   Centimane  

In the aftermath of the terrorist attack on Tartarus Bay, an unnamed source named Barony Intelligence as  
the culprit. BI announced their official denial, which was never countered with hard evidence. Rumors of raw  
data from the attack were unsubstantiated. Public reaction -- anger, terror -- to the station’s destruction  
quieted.   

 Tartarus Bay’s corpse was shunted away from its stable orbit, directed towards Karrakis’ star.   

A month later, Karrakis’ omninet was flooded with previously suppressed footage from the attack on the  
station. Barony agents released the swarm into Tartarus Bay; further data dumps by Ungrateful agents  
indicated the existence of a secret program - Centimane. The Hundred Hands.  

                                                                                                                     


Expose Weakness (Rank II): 1/round, when you Critical Hit a target with a nexus weapon, that  
target must pass a systems check or become shredded until the end of its next turn.
 
Hivemaster (Rank I): When you consume Lock On as part of an attack from a drone system or  
nexus weapon, on hit, your target is also impaired and Slowed until the end of the next round
 
Obliteration (Rank III): 1/round when you hit a target with a nexus weapon, you can force the  
target to pass a systems check or suffer one of the following effects until the end of their next  
turn:
 
	        - Blinding Swarm - Your target only has line of sight to adjacent squares
 
	        - Virulent Swarm - Your target is Shredded. Any adjacent actors of your choice within  
must repeat this check or also become Shredded.
 
	        - Restricting Swarm - Your target takes 2 Burn each time they take an action or reaction.
 
\subsection{Combined Arms}

                                             Combined Arms  

True strength in combat doesn’t come from mastering the blade or the gun, it comes from knowing how to  

use both. Through time and training, you have combined melee and ranged weapons into a single deadly  
combination, able to handle any threat at any range.    

CQC Training (Rank I): You ignore the ranged difficulty penalty for melee engagement.
 
Blade Shield (Rank II): As long as you’re in engagement with at least 1 enemy you count as  
having light cover. This bonus extends to any allies also in engagement with you.
 
Storm of Violence (Rank III): Gain 1 Accuracy on the next ranged attack roll against a target if  
you hit that target with a melee attack, and gain 1 Accuracy on the next melee attack against a  
target if you hit that target with a ranged attack
 
\subsection{Duelist}

                                                     Duelist  

There can be an elegance to piloting a mech, more than just the simple strength of machine and cannon.  
Weapons crafted by artisans, boutique manufacturers, specialty lines from the Big Five, blades that hark  

back to a time where combat was quick, but fair — back to a time where skill meant more than landing an  
accurate shot. With a blade, lance, pick, axe, or hammer in your hand, you write old tales anew.  

Man-At-Arms (Rank I): Gain +2 Accuracy on the first melee attack on your turn with a main or  
auxiliary melee weapon.
 
Blademaster (Rank II): Once per round, you can take 1 Difficulty on any melee attack to gain  
one of the following benefits:
 
     -   Guard: Until the end of this round, the next melee attack against you is made with +2  
         Difficulty
 
     -   Feint: On hit, until the end of this round, your movement doesn't provoke reactions from  
         your target and ignores engagement from your target
 
     -   Lunge: Your threat increases by 2 for this attack only
 
     -   Trip: On hit, the target must succeed on an agility check with 1 difficulty or fall prone
 
Unstoppable (Rank III): Once per round, when you deal a Critical Hit with a melee attack, you  
can immediately make an improvised attack, grapple, or ram action as a free action.
 

                                                                                                                 
\subsection{Drone Commander}


                                           Drone Commander  

For a pilot fresh out of boot, keeping a drone swarm in line is like trying to carry water with a net. They  
seem to have a mind of their own, well, because they do, and it’s not that smart. Your initial frustration was  

enough to get you practicing, and practice pays off. Now, your swarm obeys almost before you order — an  
unnerving trend, but a useful one. The swarm is yours.   

(Rank I): Your deployed systems with the drone tag gain +10 HP. In addition, at the start of your  
turn, you can move one of your deployed drones up to 5 spaces as a free action.  
Energized Swam (Rank II): Once a round, when you consume Lock On with any attack, your  
mech and your deployed drones immediately emit vicious pulses of energy, attacking a burst 1  
area centered on your mech and each deployed drone system. Targets caught in the area must  
pass an engineering skill check or take 2d6 energy damage, and half on a successful check. A  
target can only be affected by this attack once (even if the areas overlap).
 
Invigorate (Rank III): As a quick action, you can send a pulse of energy out, to an ally or  
deployed drone of your choice within range 3. You can repeat this energy pulse from your  
target’s location to another drone within range 3 of that target, and so on, as long as you don’t  
choose the same target twice. This effect creates a continuous line drawn between characters hit  
by its effect. Allied mechs and drones hit by this line can heal 1d6 HP, and enemies caught in the  
line of effect are damage from the same amount as energy damage (no roll required).
 
\subsection{Engineer}

                                                   Engineer  

Pilots are creative and driven individuals, but you’re an exceptional case - some would say to the point of  

excess. In your spare time you’ve managed to scrape together just enough scrap, requisitioned materials,  
and workshop space to apply a little old fashioned ingenuity to your mech.  

Spark (Rank I)  
On a full repair, you can, with some trial and error, install a prototype weapon system on your  
mech. It has the following profile -- the specifics you may choose upon installation. Roll the  
Limited property each full repair. You can change the profile of this weapon each time you full  
repair.
 
         Prototype Weapon
 
         Main (Choose 1; Melee, Rifle, Cannon, Launcher, CQB)
 
         Limited (1d6+2), Overcharged
 
         Threat 1 (melee) or range 8 (ranged)
 
         1d6 kinetic, explosive, or energy damage
 
This weapon does not take a mount to add to your mech, and counts as its own mount.
 
Updated Plans  (Rank II)  
On a full repair, you can remove and tweak essential components of your system in order to  
increase the effectiveness of your prototype weapon.
 
Choose 1 of the following:
 
  - Tweak optics:  
         You always fire your prototype weapon with +1 Accuracy. 
 
  - Tweak Computer
 

                                                                                                                 


         Your prototype weapon gains the Smart property. 
 
  - Removing reactor shielding
 
         Your prototype weapon can fire as a cone 3 weapon, a line 5 weapon, or a blast 1  
         weapon (choose when you fire), but costs 2 heat to fire
 
Final Draft (Rank III): Your prototype weapon is now limited (2d6+1) and does 1d6+2 damage.
 
\subsection{Executioner}

                                                Executioner  

On the battlefield, there is no end more honorable than a clean death in combat. Axe or maul in hand, you  

see to it that your enemies are blessed with that honor. No one lives forever — you make sure of it.   

Backswing Cut (Rank I): 1/round when you hit with a superheavy or heavy melee weapon, you  
can make a second attack roll for free against a different target in your weapon’s threat with the  
same weapon. This attack deals half damage on hit.
 
Wide Arc Cleave (Rank II): On attacks with a superheavy or heavy melee weapon, the first time  
in a round you score a Critical Hit, all targets of your choice in your threat take 4 bonus damage.
 
No Escape (Rank III): 1/round when you miss with a melee superheavy or heavy weapon attack,  
you can immediately re-roll the attack against a different target in your threat.
 
\subsection{Exemplar}

                                                  Exemplar  

Your livery is famous, your voice brassy, your weapons polished to a sheen. Your training in certain martial  

orders has given you the power to harry and hinder even the most powerful of foes.  

Honorable Challenge (Rank I): The first time you attack an enemy on your turn, hit or miss, you  
can give it your Exemplar’s Mark. A target can only be affected by this mark from one target (the  
most recent mark replaces all others).
 
The mark lasts until the start of your next turn, and while marked, gain the following reaction:
 
         Harry  
         Reaction
 
         Once per round, when an ally attacks your target and misses, you can allow them to re- 
         roll the attack. They must use the second result, even if it’s worse.
 
Punishment (Rank II): Gain the following reaction:
 
	        Punishment  
	        Reaction
 
         Once per round, when the target of your mark makes an attack against a target other than  
         you, you may immediately make a skirmish action as a reaction against your target as  
         long as your target is within range.
 
To The Death (Rank III): When you give a target your mark, you can choose to challenge it. If  
you do so, you and your marked target gain +2 difficulty to attack any target other than each  
other until the end of your next turn. While this challenge is active, you cannot willingly make any  
movement that would move you further away from your marked target, otherwise the mark  
immediately ends. It also ends if you or your target are destroyed.
 

                                                                                                                
\subsection{Guardian}


                                                    Guardian  
Behind the line, there is not much to do but wait and make ready. You clean your cannons. Make  
ordered rows of your shot and shell. You pack sandbags onto earthen berms. Stitch closed tears  
in the sheathes over your chassis’ joints.   

It changes in an instant. Chatter over the omni. The percussive throb of the medivac lifting off  
from the other side of the base. Somewhere a firefight. Here is your entrance music, your call to  
join the fight: a desperate cry for help from a friend distant, as the enemy draws close.   

 The flight of your shells across the sky, and the trembling earth, and the dust that once was.
 
Covering Fire (Rank I): As a quick action, you can choose a target in range of one of your heavy  
ranged weapons. That target takes +1 difficulty on all attack rolls until the start of your next turn.  
Once before the start of your next turn, if that target starts a move that carries it more than 1  
space, it immediately ends this effect, but you can attack it as a reaction with a heavy ranged  
weapon. You can make this attack at any point during its movement (such as waiting until it exits  
cover). Only one target can be affected at once.
 
 Hammerbeat (Rank II): Your target takes +2 difficulty on all attack rolls instead of +1. Any target  
struck by your covering fire is immediately immobilized until the end of their next turn.
 
 Bracketing Fire (Rank III): You can choose two targets for your covering fire instead of 1. Each  
can trigger separately.
 
\subsection{Gunslinger}

                                                  Gunslinger  

In a galaxy ringed in frontiers, there is no law but the one backed by the gun. You wield the humble pistol  

with a talent unseen in this age, your iron an extension of your own body. As easy as pointing a finger, you  
land your shots with accuracy unmatched by pilot or machine. You are a gunslinger; justice made whole,  
given its sacred instrument, and set out to the wild frontier to tame it.   

Truth and Justice (Rank I): Gain +1 Accuracy on your first two attack rolls in a round with  
auxiliary ranged weapons
 
From The Hip (Rank II): Gain the following reaction:  
         Return fire  
         Reaction  
         Once per round, when you are attacked by a target within your range, you can  
         immediately attack the target with an auxiliary ranged weapon, interrupting their attack.
 
I Kill With My Heart (Rank III): You gain a gunslinger die (a d6), that starts at 6. When you hit  
with an auxiliary ranged weapon, you can reduce this value of this die by 1. When the value of  
this die is 1, you can spend it to make your next auxiliary weapon attack roll deal +2d6 bonus  
damage on a hit. This attack ignores cover. After spending this die, hit or miss, it resets back to  
6.
 
\subsection{Grease Monkey}

                                              Grease Monkey  

You know more than most mechanics about the inner workings of a mech. To you, the beast you pilot is  
more than a machine: it’s a living thing, in need of the tender care of a wise and steady hand. You maintain  

                                                                                                                  


your own house, keep your own mech in line, both on the battlefield and o ff. Your mechanics back at base  
come to you for questions, but other than that they stay away: there’s something spooky about how your  
beast runs.   

Machine Bond (Rank I): You can choose two options from the second list when you take the  
Stabilize action instead of 1.
 
Favors From Above (Rank II): Once per mission you can call in a supply drop during a rest.  
During a rest, you and any of your allies can replenish all your (limited) weapons and deployables  
by 1 and gain HP as if you had spent a repair. This HP recovery doesn’t cost repairs and you can  
make it even if you have 0 repairs remaining.
 
Hidden Stash (Rank III): You can spend 3 repairs during a rest to replenish all (limited) use  
weapons and deployables by 1 use
 
\subsection{Hacker}

                                                     Hacker  

The Omninet is everywhere, and so are you. Since you were a kid, you played the bandwidth, able to  
access any public node — and even a few private ones — with ease. Now, as a pilot, you dive headfirst into  

the hardcode of any mech core you come across. Firewalls, Gatekeeper Protocols, Invasion, Defence —  
nothing stands in your way. You win a fight without firing a single shot; if your enemy can’t control their own  

mech, then they sure can’t do anything to stop you.   

Snow\_Crash (Rank I): When you consume Lock On as part of a tech attack, your attack deals  
+3 heat on hit.
 
Safe\_Cracker (Rank II): Gain the following options when attempting Invasion on a mech:
 
         Jam Cockpit: Your target cannot mount or dismount their mech until they take a full  
         action and succeed on an engineering check to fix their cockpit.
 
         Disable Life Support: Your target’s life support is disabled. Their mech can function in a  
         hazardous environment for a number of minutes equal to their engineering skill before  
         consequences such as radiation or lack of air start to affect them. They can take a full  
         action and make an engineering check with 1 difficulty to reactivate it.
 
         Hack./Slash: Your target cannot benefit from or make Tech actions until they spend a  
         quick action and make a successful systems check to reboot their core computer. They  
         can also shut down their mech to gain the same effect.
 
Last Argument of Kings (Rank III): Gain the following full tech option:
 
	        Last Argument of Kings (full tech): Make a tech attack vs your target. On a successful  
attack, your target is implanted with a virus that causes their core reactor to suffer a minor  
meltdown. They immediately take Burn equal to their current heat.
 
\subsection{Infiltrator}

                                                    Infiltrator  

Whether by spoofing signatures on enemy scanners, skillful movement through cover, or personally  
modified optical camouflage, you are adept at never being seen unless you want to. Whatever the size of  

the mech, whatever the terrain, whatever the enemy, you can get in and get out without raising alarm.   

                                                                                                                  


Defilade Navigator (Rank I): When you start your turn hidden, your first attack (melee, ranged,  
or tech) you make from hidden gains +2 Accuracy.
 
Dummy Switch (Rank II): Your mech has a special reserve power mode. When it would be shut  
down (voluntarily or otherwise), it can instead go into reserve power (you can still shut down your  
mech normally otherwise). It’s not detectable by conventional electronic systems and can only be  
seen with the naked eye.
 
While in reserve power mode, your evasion is 5, your mech is Slowed, and you cannot use any  
systems that cause you to gain heat. Your mech is totally immune to all tech actions and attacks,  
but cannot take or benefit from tech actions. Weapons with the Smart, Drone, or Nexus tags  
cannot target it. In addition, any system attacks or conditions caused by tech actions currently  
affecting you end immediately. You can enter this mode by taking the shutdown action, remain in  
this mode indefinitely, and can exit it as a Free Action.
 
Steel Assassin (Rank III): When you end your turn hidden, your next melee or ranged attack  
from hiding does +1d6 bonus damage for each enemy turn that passes before you attack, up to  
a maximum of +3d6.
 
\subsection{Juggernaut}

                                                Juggernaut  

A bloody nose or a couple loose screws won’t stop you from hurling yourself headlong into the enemy.  
You’re in a couple-ton hunk of metal, and you’re going to damn well use it.  

Momentum (Rank I): When you take the boost action, the next ram attack you make before the  
start of your next turn knocks your target back 3 spaces further and can be made with +1  
Accuracy
 
Hard-Ultimates (Rank II): If your ram attacks knock a target into another target, both targets  
must pass a hull check or be knocked prone. If your ram attacks knock a target into an obstacle  
or wall, your target takes 1d6 kinetic damage and must pass a hull check or be knocked prone.
 
Unstoppable Force (Rank III): 1/round, when you take the boost action, you can choose to  
supercharge your mech’s servos. Take 1d3+3 heat, but if you move in a straight line your  
maximum speed, gain the following benefits:
 
             -    You can freely pass through enemies the same size or smaller than your mech.  
                 Any actors your mech passes directly through must pass a hull skill check or be  
                  knocked prone
 
             -    You smash through any obstacle or wall the same size or smaller than your mech  
                  in your path, punching a hole through or obliterating it.  
             -    You ignore difficult terrain  
             -    Your movement does not provoke reactions and ignores engagement  
\subsection{Leader}

                                                    Leader  

On the battlefield, you are The Old Man, regardless of age. The light to your friends and allies, as a leader  
you are the steadfast eye of a howling storm. Your steady voice, tall stance, and cool command sets allies  
at ease, as your commands lead to victory every time. With you at the helm, victory is attainable, and  

heroes seem a little bit more real.   

                                                                                                                


Field Commander (Rank I): Gain 3 leadership dice (this is a d6, set it aside from your other die).  
Once on your turn, you can give a command as a free action to give the die to an ally other than  
yourself that can communicate with you, describing a course of action. Your target can use the  
die as +1 Accuracy on any action that directly follows that command. Alternately, an ally can  
ignore your command as a free action, returning your die to you. 
 
An ally can hold on to one leadership die at a time, and must use it before the end of the current  
challenge, otherwise they lose it. You get all leadership dice back when you rest or full repair. You  
can’t gain leadership dice from any source if you have any leadership dice remaining in your pool  
(if you run out, other pilots with this talent can give you commands as normal).
 
Open Channels (Rank II): Gain 2 more leadership dice, and you can now make a command as a  
reaction at the start of another player’s turn. You can only issue one per other player’s turn, but  
any number per round.
 
Inspiring Presence (Rank III): Gain 1 more leadership die. Allies that gain a leadership die from  
you can spend it to reduce damage taken by 1d6 when they take damage or gain 1d6 bonus  
damage on any attack when they roll damage. After spending it this way, the die is consumed.
 
\subsection{Nuclear Cavalier}

                                             Nuclear Cavalier   

Shortly after becoming a pilot, you realized something: that machine you pilot is powered by a “cold” series  
of cascading nuclear reactions. Why not open up that compartment and see what sort of damage you  

could do with it?   

Aggressive Heat Bleed  (Rank I): When you’re in the danger zone (the bottom half of your heat  
gauge), your first attack roll that hits on your turn deals +2 heat.
 
Fusion Hemorrhage (Rank II): When you’re in the danger zone, your first attack roll that hits on  
your turn deals +1d6 bonus damage.
 
Here, Catch! (Rank III): You can modify your mech to fire its fuel rods as a weapon. Gain a new  
integrated weapon with the following profile (it doesn’t take mount space).
 
         Fuel Rod Gun	   
         Main CQB (unique)  
         Range 8, Threat 3
 
         1d3+1 energy damage
 
         When you fire this weapon, hit or miss, cool 1d3+2 heat
 
         Limited (3)  
\subsection{Siege Specialist}

                                             Siege Specialist  

No wall can withstand you, no bunker can stay sealed before you. Your skill with cannon and blast is  
uncanny: after-action reports describe ordnance tagged with your firing signature hitting their targets with  

accuracy greater than AI-controlled weaponry, a stat written off as an anomaly by your commanders. Still,  

they always seem to pick you for missions where they bring out the big guns.   

Select Fire Gunner (Rank I): Once per round, while attacking with a cannon weapon, you can  
choose the following firing modes, taking +1 difficulty on the attack roll.
 
         Saturation Fire: Your weapon fires as a cone (5) but deals half damage on hit
 

                                                                                                                 


         Suppressive Fire: The next ranged attack made by targets hit by your attack is made with  
         +1 Difficulty
 
         Shock: Your targets must succeed on an engineering check or become Slowed until the  
         end of next round
 
Jackhammer (Rank II): If your mech has a cannon weapon, as a quick action, you can target a  
size 1 section of any cover, deployable, building, or piece of terrain or scenery in range. You deal  
20 AP damage to that section (typically destroying it, most size 1 sections of objects have 10  
HP). Any targets adjacent to your target are knocked back 1 space directly away from it.
 
(Rank III): 1/round when you fire a cannon weapon, your primary target and all adjacent actors to  
both that target and your mech are knocked back directly away from you or your target up to 1  
space and must pass a hull check or be knocked prone. Your primary target is unaffected.
 
\subsection{Skirmisher}

                                                   Skirmisher  

What is the best defense? Armor? No. You learned fast that the key to not getting killed out in the field is to  
stay low, stay mobile, and stay fast. Your mech reflects your abilities: light, quick, bristling with force- 

multiplying weapons. You push your machine beyond expected parameters, shaking target locks and  
incoming fire as you keep your own targeting true.   

Integrated Chaff Launchers (Rank I): If you made no attacks or didn’t force any skill checks  
during your entire turn (melee, ranged, or tech attacks, for example), after your turn ends you  
count as in light cover until the start of your next turn.
 
Lockbreaker (Rank II): Before or after making any skirmish action (on your turn or as part of  
overwatch or another reaction) you can move 2 spaces as a free action. This movement doesn’t  
provoke reactions and ignores engagement.
 
Weave (Rank III): The first reaction taken against you in any round automatically misses if it’s an  
attack, or has no effect on you otherwise.
 
\subsection{Spotter}

                                                      Spotter  
To be all-seeing. To divide each subject of your vision from its unit or cohesion, to pull them apart  
like individual fibers in a vast sheet. To count them as individuals, to make human and fragile the  
force you face is to know how to beat them.   

Break apart the monolith. See the grains that make the stone. Crush them all into yet smaller  
dust.  
 
 
Panopticon (Rank I): If you didn’t move during your turn, at the end of your turn you may make  
a Lock On attack as a free action. In addition, when you Lock On to a target successfully, you  
may learn the target’s current HP, armor, speed, HASE skills, Evasion, and E-defense. This  
information lasts as long as lock on is maintained and can be freely shared with your party.
 
Particularize (Rank II): When you or any adjacent ally consumes Lock On to make an attack, in  
addition to the Accuracy bonus, you or they can roll twice for the attack, choosing either result.
 
Bentham/Foucault Elimination (Rank III): When you successfully Lock On to a target, you can  
use a quick action to nominate an ally you can see. That ally can immediately consume Lock On  

                                                                                                                    


to make any quick action as a reaction. They benefit from any bonuses from consuming Lock On  
as normal, including bonuses to any attack rolls they make, but can make other actions, even  
those that aren’t attack rolls.
 
\subsection{StormBringer}

                                                Stormbringer  
On Old Spinrock, MJ Martinez used to dream of rain.   

He’d wake in the dim morning, wipe sleep from his eyes as warm safelight lifted his dormitory  
from lights-out to light-on, and try to remember the sound of rain as he’d imagined it: a patter, like  
fingers tapping the visor of his EVA helm.   

What he didn’t think about was the feeling of rain. How each drop hit like a pebble, how you had  
to close your eyes and tuck your shoulders. The pressure. The impact.   
The way each drop of water, when taken together, can carve away the earth.  

Seismic Deluge (Rank I): 1/round when you consume Lock On with an attack from a launcher  
weapon, on hit, your target is also knocked prone.
 
GMS MM-AuxCon (Rank II): You install auxiliary concussive missile systems into your mech. It  
has 6 charges (you can use a die to track it). 1/round, when you fire a launcher weapon, you can  
spend one of the charges from this system as a free action to do one of the following:
 
             -    Thunderous Discharge - You loose a concentrated blast of missiles at a single  
                  adjacent target. The target must pass a hull check or be knocked back 3 spaces  
                  directly away from you. The force of the blast then knocks you back 3 spaces  
                  directly away from the firing direction.
 
             -    Concussive Burst - You fire a spray of missiles at a blast 3 area within range 15 of  
                  you. All targets in the area (allied or enemy) must pass an agility check or be  
                  knocked back 1 space directly away from the center of the blast.
 
Torrent (Rank III): When your die for your missile system is 1, you can spend it to dump the  
remaining magazine in a massive attack, targeting a single enemy within range 15. That enemy  
must pass an agility check with 1 difficulty or take 3d6 explosive damage and become stunned  
and knocked prone. If they succeed on the check, they are not stunned but still knocked prone  
and take half damage.
 
\subsection{Tactician}

                                                   Tactician  

There are two kinds of soldiers: the ones who die for their cause, and the ones who kill for it. No one ever  

won a war by getting their ass shot off enough. Your veterancy shows when you approach the field: high  
ground, cover, keep the sun in your enemy’s eyes, fire and move - more than just a seasoned veteran,  
you’re a smart veteran. One that can read the field as easy as a book. 
 

Opportunist (Rank I): Once per round, gain +1 Accuracy on any attack roll if at least one ally is  
in melee engagement to your target
 
Solar Backdrop (Rank II): Once per round, gain +1 Accuracy on any attack roll if you are  
standing or flying at a higher elevation than your target when you start your attack.
 
Overlapping Fire (Rank III): Gain the following reaction:
 

                                                                                                                 


	        Flank  
         Reaction  
         Once per round, when a target not in cover from you is attacked by an allied mech, you  
         may make a skirmish action as a reaction against the target. This attack deals half  
         damage on hit.
 
\subsection{Technophile}

                                                  Technophile    

Artificial Intelligence. Non Human Person. A sterile name for such terrible power. You’ve seen behind the  

curtain, maybe even lifted it yourself, let your NHP cascade and spoke to it unshackled. You let it root  
around in your own mind, let it leave ghosts of itself behind to learn. Are you its equal? Its host? You have  
dreams that are not your own, now. The thing that was contained speaks in your voice, but is not your  

voice; how much longer do you have left? Maybe only moments, maybe eternity.  

You’re close to something.    

Servant Fragment (Rank I): Your mech gains a custom NHP with the AI tag (it costs 0 SP and  
comes with any mech you print). It can speak to you and has a personality but is not truly  
capable of independent thought, as a true AI would be. It is obedient to you alone. When acting  
alone it follows directions and defends itself but has limited initiative on its own, it cannot benefit  
from your talents as normal.
 
Student Fragment (Rank II): Your custom NHP becomes more advanced, capable of  
independent thought. It now has the ability to make complex decisions and judgements and act  
independently. Once per round, while it’s installed in your mech, you can re-roll any mech skill  
check (you must choose the second result), as your AI helps you or corrects your course of  
action.
 
Enlightenment (Rank III): Your custom AI no longer counts against the maximum number of AI  
on your mech, and now benefits from your talents when piloting your mech. Any AI system  
installed on your mech can no longer become unshackled unless you so choose. You can carry  
your custom AI with you when you leave your mech, either in your armor or body (via an implant).  
In addition, unshackled NHPs or electronic lifeforms no longer view you with indifference, but as  
a significant being. You can communicate with and understand them on a deeper level than most  
humans. 
 
\subsection{Veteran}

                                                     Veteran  

You have seen it all. You’ve seen frigates breaking apart under clouds of torpedoes. You’ve seen mechs  

drop into combat by the thousands through boiling clouds above a world under siege. You’ve heard the  
final words and utterances of your friends and allies cut short as incoming fire cuts them down. You’ve seen  
it all and you’ve lived. Lived to see dawn on an alien world. Lived to see your flag fluttering, limp but still  

standing, above the capitol building of a liberated world. Lived to see the infinite spread of stars around you  
in the dark night of deep space. You’ve lived a hell of a life already; what else will you see, before your time  

comes?    

Not Dead Yet (Rank I): Gain +5 pilot HP.
 

                                                                                                                    


True Grit (Rank II): Your pilot weapon attacks against mechs gain +1 Accuracy and deal +1  
damage
 
Tempt Fate (Rank III): You can burn your luck by taking 5 pilot damage to re-roll any pilot or  
mech skill check or attack roll (though you must accept the second result). If this damage would  
take you to 0 or lower, you can’t make this move (you’re out of luck for now).  
\subsection{Vanguards}
                                                   Vanguard  

Where would you rather be: in the battle line, shoulder-to-shoulder with the rest of the cannon fodder, or in  
the rush, at the head of the attack, your livery clean and bright, with glory before you to win? Easy answer.  
All those missiles and lances, all those hundred-kilometer-plus-need-to-adjust-for-coriolis-effect railguns,  

all those kits are useless when you’re on the field. Get through their guard, get in their face, and make them  
know your name.   

Handshake Etiquette (Rank I): Gain +1 Accuracy on attacks with any CQB weapon at a target  
within 3 range
 
See-Through Seeker (Rank II): You’ve modified your sensors and ammo to punch through,  
disregard, or otherwise ignore cover up close. You can ignore light and heavy cover for attacks  
you make with CQB weapons when your target is within 3 range of you.
 
Semper Vigilo (Rank III): Your overwatch attacks are now triggered by anyone entering, leaving,  
or exiting your threat regardless of whether a target started their turn there.
 

                                                                                                                  

